### 2020-02-11 reports/Progress-2-10-20.tex
prop covert signalers vs. receptivity/homophily prelim done

% Author: Matthew Turner

\documentclass[11pt,letterpaper]{article}
% \documentclass[11pt]{report}
% \documentclass{report}
% \documentclass{book}
\usepackage[bookmarks]{hyperref}
\usepackage{amssymb,amsmath}
% \usepackage{fullpage}
\usepackage{tabulary}
\usepackage{tabularx}

% \usepackage[margin=1.00in]{geometry}
\usepackage[margin=0.90in]{geometry}
\usepackage{float}

\usepackage{caption}
\usepackage{booktabs}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{wrapfig}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage{setspace}
\doublespace
% \usepackage{url}
\usepackage{bigfoot}
\usepackage[export]{adjustbox}
\setlength\intextsep{0pt}

\usepackage{graphicx}

\title{Identity signaling model progress}

\author{{Matthew A.~Turner}}

\begin{document}
\maketitle

\section*{Preliminary results}

For these preliminary results I focus on the evolution of signaling strategies,
and set receiving strategies to be randomly assigned with probability 0.5 to
each agent at model initialization. I set $R=0.5$, $s=0.25$, $d=\delta=0.25$,
and $N=100$. After signaling, agents go through 10 rounds of assortment/interaction,
followed by evolution after the 10 rounds of interaction. The model has been
run out to 100 timesteps where timeseries are nearly stable, though we will
want more timesteps for our final study, or perhaps adjust the number of 
assortment/interaction rounds up or down per timestep, to guarantee full 
stability (see Figure~\ref{fig:exampleSeries}).

\subsection*{Density of covert signalers vs. $r/R$ and homophily, $w$}

Based on results from ``Evolution of covert signaling'' (``ECS''), I designed
the first agent-based model experiment to determine the dependence of the
density of covert signalers in the population ($\rho_C$) on
the receptiveness of the population to covert signals ($r$) and the
importance of homophily ($w$) to assortment.

I systematically varied $r/R$ by setting $R=0.5$ and varied 
$r \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$ to get $r/R \in \{0.0, 0.1, \ldots, 0.9\}$.
I varied homophily similartly to $r$, $w \in \{0.0, 0.5, \ldots, 0.45\}$. Note
that both $r$ and $w$ are bounded above by 0.5.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/exampleMidrangeSeries.pdf}
  \caption{Timeseries of nine combinations of $r/R$ and $w$.}
  \label{fig:exampleSeries}
\end{figure}

\begin{figure}[H]
  \centering
\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsReceptivityHomophily.pdf}
  \caption{Density of covert signalers at $t=100$, final timestep recorded
    in this preliminary experiment.}
  \label{fig:}
\end{figure}

\section*{Discussion}

These preliminary experiments and results are based on one major finding from
ECS that covert signaling is maintained when overt signalers do not have
too large an advantage in the free choice context. ``This requires that
assortment with liked individuals not be too accurate,'' which corresponds to
small $w$ in this ABM version. ``The accuracy of assortment is influenced
by the reception probabilities of both signal types, $R$ and $r$'' (see p.
4 in ECS). Our preliminary results find the same trend with our ABM.

% \bibliographystyle{apacite}

% \setlength{\bibleftmargin}{.125in}
% \setlength{\bibindent}{-\bibleftmargin}

% \bibliography{/Users/mt/workspace/papers/library.bib}

\end{document}

### 2020-02-13 reports/Progress-2-14-20.tex
disliking experiment ready for cluster

--- 2020-02-11 reports/Progress-2-10-20.tex
@@
 
-\author{{Matthew A.~Turner}}
+\author{} %{Matthew A.~Turner}}
 
@@
   \caption{Timeseries of nine combinations of $r/R$ and $w$.}
-  \label{fig:exampleSeries}
+  \label{fig:receptivityHomophilySeries}
 \end{figure}
@@
     in this preliminary experiment.}
-  \label{fig:}
+  \label{fig:receptivityHomophilyHeatmap}
+\end{figure}
+
+\subsection*{Density of covert signalers vs. disliking penalty $d=\delta$ and homophily, $w$}
+
+Here we co-vary the disliking penalties, which we set equal ($d=\delta$), and
+homophily, $w$. The bonus payoff for two interacting agents where at least one
+likes the other is set to $s=0.25$. The payoff structure is as follows
+
+\begin{table}[h]
+  \centering
+  \begin{tabular}{rl}
+   Attitude combo. & Payoff \\
+   \toprule
+    Like/like & $1 + s$ \\
+    Like/neutral & $1 + s$ \\
+    Neutral/neutral & 1 \\
+    Like/dislike & $1 + s - d$ \\
+    Dislike/neutral & $1 - d$ \\
+    Dislike/dislike & $1 - d - \delta$
+  \end{tabular}
+\end{table}
+
+Specifically, we vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}
+As in the above experiment, we set $w \in \{0.0, 0.5, \ldots, 0.45\}$.
+In this experiment we ran the simulations to 200 timesteps 
+(Figure~\ref{fig:dislikingHomophilySeries}).
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\textwidth]{Figures/exampleMidrangeSeries.pdf}
+  \caption{Timeseries of nine combinations of $d=\delta$ and $w$.}
+  \label{fig:dislikingHomophilySeries}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsReceptivityHomophily.pdf}
+  \caption{Density of covert signalers at $t=100$, final timestep recorded
+    in this preliminary experiment.}
+  \label{fig:dislikingHomophilyHeatmap}
 \end{figure}

### 2020-02-13 id_signaling/experiment.py

@@ -83,11 +83,41 @@ def trials_receptivity_homophily(receptivity, homophily, n_trials=10,
     )
 
 
+def trials_dislikepen_homophily(dislike_penalty, homophily, n_trials=10,
+                                n_iter=100, R=0.5):
+
+    results = np.zeros((n_trials, n_iter + 1))
+    seeds = np.random.randint(2**32 - 1, size=(n_trials,))
+
+    with mp.Pool(processes=mp.cpu_count()) as pool:
+        trial_func = partial(_one_trial, n_iter=n_iter,
+                             covert_rec_prob=0.25,
+                             one_dislike_penalty=dislike_penalty,
+                             two_dislike_penalty=dislike_penalty,
+                             R=R, homophily=homophily)
+        results = np.array(
+            list(pool.map(trial_func, seeds))
+        )
+
+    return pd.DataFrame(
+        {
+            "timestep": list(range(n_iter + 1)) * n_trials,
+
+            "trial_idx": [idx
+                          for _ in range(n_iter + 1)
+                          for idx in range(n_trials)],
+
+            "dislike_penalty": [dislike_penalty] * n_trials * (n_iter + 1),
+
+            "homophily": [homophily] * n_trials * (n_iter + 1),
+
+            "prop_covert": results.flatten()
+        }
+    )
+
+
 def _one_trial(seed, n_iter, covert_rec_prob, R, **model_kwargs):
 
-    # seed = int(round(trial_index * time.time()))
-
-    # print(f'running trial with random seed {seed}')
     with open('log.txt', 'a+') as f:
         f.write(f'running trial with random seed {seed}\n')
 
@@ -102,7 +132,6 @@ def _one_trial(seed, n_iter, covert_rec_prob, R, **model_kwargs):
 
     # Models have an attribute representing proportion of covert signalers.
     return model.prop_covert_series
-    # output.put(model.prop_covert_series)
 
 
 def analyze_covert_receiving_prob(results):

### 2020-02-13 run_disliking_homophily.py

@@ -1,0 +1,22 @@
+from id_signaling.experiment import trials_dislikepen_homophily
+
+import os
+
+data_dir = 'output_data'
+
+disliking_penalties = [0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45]
+homophilies = receptivities
+
+df_full = None
+
+for d in disliking_penalties:
+    for w in homophilies:
+
+        df = trials_dislikepen_homophily(r, w, n_iter=200, n_trials=100)
+
+        if df_full is None:
+            df_full = df
+        else:
+            df_full = df_full.append(df)
+
+df_full.to_csv(os.path.join(data_dir, 'test.csv'), index=False)

### 2020-02-14 reports/Progress-2-14-20.tex
disliking-homoph conf exp done; on to co-evo of sig/rec strat

@@
 
-\title{Identity signaling model progress}
+\title{\vspace{-1in}Identity signaling model progress}
 
@@
 
-\section*{Preliminary results}
+\section*{Evolution in signaling strategy}
 
@@
 and set receiving strategies to be randomly assigned with probability 0.5 to
-each agent at model initialization. I set $R=0.5$, $s=0.25$, $d=\delta=0.25$,
-and $N=100$. After signaling, agents go through 10 rounds of assortment/interaction,
-followed by evolution after the 10 rounds of interaction. The model has been
-run out to 100 timesteps where timeseries are nearly stable, though we will
-want more timesteps for our final study, or perhaps adjust the number of 
-assortment/interaction rounds up or down per timestep, to guarantee full 
-stability (see Figure~\ref{fig:exampleSeries}).
+each agent at model initialization. The output measure in these experiments
+is density of covert signalers. There are confirmatory results for two
+computational experiments in which I: (1) varied relative covert receptivity $r/R$ and 
+homophily, $w$; and (2) varied the disliking penalties set equal, $d=\delta$,
+and homophily, $w$.
 
@@
 importance of homophily ($w$) to assortment.
+
+Here I set $R=0.5$, $s=0.25$, $d=\delta=0.25$,
+and $N=100$. After signaling, agents go through 10 rounds of assortment/interaction,
+followed by evolution after the 10 rounds of interaction. The model has been
+run out to 100 timesteps where timeseries are nearly stable, though we will
+want more timesteps for our final study, or perhaps adjust the number of 
+assortment/interaction rounds up or down per timestep, to guarantee full 
+stability.
 
@@
 Here we co-vary the disliking penalties, which we set equal ($d=\delta$), and
-homophily, $w$. The bonus payoff for two interacting agents where at least one
-likes the other is set to $s=0.25$. The payoff structure is as follows
+homophily, $w$. I ran the model to 200 timesteps this time, which did allow
+the series to settle more, but perhaps not to a significant degree 
+(Figure~\ref{fig:dislikingHomophilySeries}). The bonus payoff for two 
+interacting agents where at least one
+likes the other is set fixed to $s=0.25$. The payoff structure is as follows
 
-\begin{table}[h]
+\begin{table}[H]
   \centering
@@
 
-Specifically, we vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}
+Specifically, we vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$
 As in the above experiment, we set $w \in \{0.0, 0.5, \ldots, 0.45\}$.
-In this experiment we ran the simulations to 200 timesteps 
-(Figure~\ref{fig:dislikingHomophilySeries}).
 
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{Figures/exampleMidrangeSeries.pdf}
+  \includegraphics[width=0.8\textwidth]{Figures/dislikingHomophilySeries.pdf}
   \caption{Timeseries of nine combinations of $d=\delta$ and $w$.}
@@
   \centering
-\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsReceptivityHomophily.pdf}
+\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsDislikingHomophily.pdf}
   \caption{Density of covert signalers at $t=100$, final timestep recorded

### 2020-02-18 id_signaling/experiment.py
updated model and experiments to have receiving strategy evolve

@@ -86,7 +86,8 @@ def trials_receptivity_homophily(receptivity, homophily, n_trials=10,
 def trials_dislikepen_homophily(dislike_penalty, homophily, n_trials=10,
                                 n_iter=100, R=0.5):
 
-    results = np.zeros((n_trials, n_iter + 1))
+    results_covert = np.zeros((n_trials, n_iter + 1))
+    results_churlish = np.zeros((n_trials, n_iter + 1))
     seeds = np.random.randint(2**32 - 1, size=(n_trials,))
 
     with mp.Pool(processes=mp.cpu_count()) as pool:
@@ -95,9 +96,13 @@ def trials_dislikepen_homophily(dislike_penalty, homophily, n_trials=10,
                              one_dislike_penalty=dislike_penalty,
                              two_dislike_penalty=dislike_penalty,
                              R=R, homophily=homophily)
-        results = np.array(
-            list(pool.map(trial_func, seeds))
-        )
+        # results = np.array(
+        #     list(pool.map(trial_func, seeds))
+        # )
+        results = list(pool.map(trial_func, seeds))
+        results_covert = np.array([el[0] for el in results])
+        results_churlish = np.array([el[1] for el in results])
+
 
     return pd.DataFrame(
         {
@@ -111,7 +116,9 @@ def trials_dislikepen_homophily(dislike_penalty, homophily, n_trials=10,
 
             "homophily": [homophily] * n_trials * (n_iter + 1),
 
-            "prop_covert": results.flatten()
+            "prop_covert": results_covert.flatten(),
+
+            "prop_churlish": results_churlish.flatten()
         }
     )
 
@@ -131,7 +138,7 @@ def _one_trial(seed, n_iter, covert_rec_prob, R, **model_kwargs):
     model.run(n_iter)
 
     # Models have an attribute representing proportion of covert signalers.
-    return model.prop_covert_series
+    return (model.prop_covert_series, model.prop_churlish_series)
 
 
 def analyze_covert_receiving_prob(results):

### 2020-02-18 id_signaling/model.py

@@ -67,6 +67,7 @@ class Model:
 
         # This is the series of proportion of covert signalers.
         self.prop_covert_series = np.array([_proportion_covert(self)])
+        self.prop_churlish_series = np.array([_proportion_churlish(self)])
 
 
     def run(self, n_iter):
@@ -90,6 +91,11 @@ class Model:
             self.prop_covert_series= np.append(
                 self.prop_covert_series, _proportion_covert(self)
             )
+            self.prop_churlish_series= np.append(
+                self.prop_churlish_series, _proportion_churlish(self)
+            )
+
+            self._reset_attitudes()
 
     def _signal_and_receive(self):
 
@@ -220,8 +226,23 @@ class Model:
                 )
                 # Switch specified teacher strategy for learner's in-place.
                 # XXX setting strategy type explicitly for now.
-                strategy_type = "Signaling"
-                self._switch_strategy(learner, teacher, strategy_type)
+                # strategy_type = "Signaling"
+                # print(strategy_type)
+                if strategy_type == "Signaling":
+                    learner.signaling_strategy = teacher.signaling_strategy
+                else:
+                    learner.receiving_strategy = teacher.receiving_strategy
+
+    def _reset_attitudes(self):
+        '''
+        This resets attitudes, which occurs after evolution happens.
+        '''
+        for agent in self.agents:
+            if agent.receiving_strategy == "Generous":
+                self.attitudes = np.zeros((self.N,), dtype=int)
+            else:
+                self.attitudes = -1 * np.ones((self.N,), dtype=int)
+
 
     def _calculate_payoff(self, a1, a2):
         '''
@@ -263,62 +284,6 @@ class Model:
             raise RuntimeError(
                 "The attitude sum was not bounded between -2 and 2"
             )
-
-    def _switch_strategy(self, learner, teacher, strategy_type):
-        '''
-        Switch learner's strategy for teacher's strategy. Switches even if they
-        are the same since it's no more expensive to just do that.
-
-        Arguments:
-            learner (Agent): Learner agent who will adopt teacher's strategy
-                for the given type.
-            teacher (Agent): learner learns from teacher.
-            strategy_type: Either "Signaling" or "Receiving" to indicate which
-                of the two strategy elements is being updated.
-        Returns:
-            None, operates in-place to update learner's strategy.
-        '''
-        # If signaling is being updated, only have to update
-        # that instance attribute.
-        if strategy_type == "Signaling":
-            learner.signaling_strategy = teacher.signaling_strategy
-
[…]

### 2020-02-19 id_signaling/experiment.py
running with 100 nodes on cluster for churlish and covert co-evo

@@ -128,8 +128,10 @@ def trials_dislikepen_homophily(dislike_penalty, homophily, n_trials=10,
 
 def _one_trial(seed, n_iter, covert_rec_prob, R, **model_kwargs):
 
-    with open('log.txt', 'a+') as f:
-        f.write(f'running trial with random seed {seed}\n')
+    print(f'running trial with random seed {seed}')
+
+    # with open('log.txt', 'a+') as f:
+    #     f.write(f'running trial with random seed {seed}\n')
 
     # Initialize model for trial.
     model = Model(prob_overt_receiving=R,

### 2020-02-19 reports/Progress-2-19.tex
finished coevolution experiment, analysis, and writeup

--- 2020-02-14 reports/Progress-2-14-20.tex
@@
 $r \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$ to get $r/R \in \{0.0, 0.1, \ldots, 0.9\}$.
-I varied homophily similartly to $r$, $w \in \{0.0, 0.5, \ldots, 0.45\}$. Note
+I varied homophily identically to $r$, $w \in \{0.0, 0.5, \ldots, 0.45\}$. Note
 that both $r$ and $w$ are bounded above by 0.5.
@@
 \begin{figure}[H]
+
   \centering
-  \includegraphics[width=0.8\textwidth]{Figures/exampleMidrangeSeries.pdf}
-  \caption{Timeseries of nine combinations of $r/R$ and $w$.}
-  \label{fig:receptivityHomophilySeries}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/receptivityHomophilyCovertSeries.pdf}
+    \caption{Density of covert signalers.}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/receptivityHomophilyChurlishSeries.pdf}
+    \caption{Density of churlish receivers.}
+  \end{subfigure}
+
+  \caption{Timeseries of density of covert signalers and churlish receivers
+    for nine combinations of $r$ and $w$. Receptivity of
+    overt signals is $R=0.5$.}
+  \label{fig:dislikingHomophilySeries}
 \end{figure}
@@
   \centering
-\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsReceptivityHomophily.pdf}
-  \caption{Density of covert signalers at $t=100$, final timestep recorded
-    in this preliminary experiment.}
-  \label{fig:receptivityHomophilyHeatmap}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/covertDensityVsReceptivityHomophilyCoevo.pdf}
+    \caption{Density of covert signalers.}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/churlishDensityVsReceptivityHomophilyCoevo.pdf}
+    \caption{Density of churlish receivers.}
+  \end{subfigure}
+
+  \caption{Density of covert signalers and churlish receivers at $t=200$, 
+    final timestep recorded in this preliminary experiment. Receptivity of
+    overt signals is $R=0.5$.}
+  \label{fig:dislikingHomophilyHeatmap}
 \end{figure}
@@
 \begin{figure}[H]
+
   \centering
-  \includegraphics[width=0.8\textwidth]{Figures/dislikingHomophilySeries.pdf}
-  \caption{Timeseries of nine combinations of $d=\delta$ and $w$.}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/dislikingHomophilyCovertSeries.pdf}
+    \caption{Density of covert signalers.}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/dislikingHomophilyChurlishSeries.pdf}
+    \caption{Density of churlish receivers.}
+  \end{subfigure}
+
+  \caption{Timeseries of density of covert signalers and churlish receivers
+    for nine combinations of $d=\delta$ and $w$.}
   \label{fig:dislikingHomophilySeries}
@@
   \centering
-\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsDislikingHomophily.pdf}
-  \caption{Density of covert signalers at $t=100$, final timestep recorded
-    in this preliminary experiment.}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/covertDensityVsDislikingHomophilyCoevo.pdf}
+    \caption{Density of covert signalers.}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/churlishDensityVsDislikingHomophilyCoevo.pdf}
+    \caption{Density of churlish receivers.}
+  \end{subfigure}
+
+  \caption{Density of covert signalers and churlish receivers at $t=200$, 
+    final timestep recorded in this preliminary experiment.}
   \label{fig:dislikingHomophilyHeatmap}

### 2020-02-25 id_signaling/experiment.py
automated figures and demos

@@ -85,6 +85,30 @@ def trials_receptivity_homophily(receptivity, homophily, n_trials=10,
         }
     )
 
+def demo(parameter_vals, experiment='receptivity',
+         n_trials=4, n_iter=50, R=0.5):
+
+    if experiment == 'receptivity':
+        func = trials_receptivity_homophily
+    elif experiment == 'disliking':
+        func = trials_dislikepen_homophily
+    else:
+        raise RuntimeError(f'{experiment} not recognized')
+
+    # Run experiment trials for each parameter setting and append to returned
+    # dataframe with all trial data.
+    df_full = None
+
+    for val in parameter_vals:
+
+        df = func(val, val, n_iter=n_iter, n_trials=n_trials, R=R)
+
+        if df_full is None:
+            df_full = df
+        else:
+            df_full = df_full.append(df)
+
+    return df_full
 
 def trials_dislikepen_homophily(dislike_penalty, homophily, n_trials=10,
                                 n_iter=100, R=0.5):

### 2020-02-25 id_signaling/figures.py

@@ -1,0 +1,90 @@
+
+
+import matplotlib.pyplot as plt
+
+
+def plot_evolution(df, experiment='receptivity',
+                   strategy='signaling', parameter_vals=[0.1, 0.25, 0.4],
+                   savefig_path=None,
+                   **plot_kwargs):
+    '''
+    Arguments:
+        df (pandas.DataFrame):
+        experiment (str): Either 'receptivity' or 'disliking' for now,
+            indicating whether receptivity and homophily, or disliking and
+            homophily, were co-varied in the experiment.
+        strategy (str): Either 'signaling' or 'receiving', specifying which
+            output variable to use. If 'signaling', the proportion of
+            covert signalers is plotted. If 'receiving', the proportion of
+            churlish receivers is plotted.
+        parameter_vals (list): Values of the homophily and disliking/receiving
+            parameters to plot, used for subsetting input data frame.
+        plot_kwargs (dict): Additional arguments for passing to plotting
+            functions, e.g., `lw=3` to set line width.
+    '''
+
+    # Set up plot annotations depending on which kind of experiment
+    # and strategy is plotted.
+    if experiment == 'disliking':
+        exp_inset = '$(d=\delta,~w)$'
+        exp_col = 'dislike_penalty'
+    elif experiment == 'receptivity':
+        exp_inset = '$(r/R,~w)$'
+        exp_col = 'receptivity'
+    else:
+        raise RuntimeError(f'{experiment} not recognized')
+
+    if strategy == 'signaling':
+        strategy_inset = 'Covert signalers'
+        data_col = 'prop_covert'
+    elif strategy == 'receiving':
+        strategy_inset = 'Churlish receivers'
+        data_col = 'prop_churlish'
+    else:
+        raise RuntimeError(f'{strategy} not recognized')
+
+    # Build title from `inset`s above.
+    title = f'{strategy_inset} over time for various {exp_inset} pairs'
+
+    # Limit data to specified parameter values.
+    df = df[
+        df['homophily'].isin(parameter_vals) &
+        df[exp_col].isin(parameter_vals)
+    ]
+
+    # Some lines I hacked together to take mean over trials and get something
+    # easy to plot.
+    gb_mean = df.groupby([exp_col, 'homophily', 'timestep'])[data_col].mean()
[…]

### 2020-02-26 id_signaling/experiment.py
developed initial minorities experiment

@@ -85,10 +85,89 @@ def trials_receptivity_homophily(receptivity, homophily, n_trials=10,
         }
     )
 
-def demo(parameter_vals, experiment='receptivity',
-         n_trials=4, n_iter=50, R=0.5):
 
-    if experiment == 'receptivity':
+def trials_minority(exp_param, homophily, minority_trait_frac=0.1,
+                    experiment='disliking',
+                    n_trials=10, n_iter=100, R=0.5):
+
+    ###  XXX XXX XXX  ###
+    # Start here in AM. #
+    #####################
+
+    results_covert = np.zeros((n_trials, n_iter + 1))
+    results_churlish = np.zeros((n_trials, n_iter + 1))
+    seeds = np.random.randint(2**32 - 1, size=(n_trials,))
+
+    with mp.Pool(processes=mp.cpu_count()) as pool:
+
+        if experiment == 'receptivity':
+            trial_func = partial(_one_minority_trial, n_iter=n_iter,
+                                 covert_rec_prob=exp_param,
+                                 minority_trait_frac=minority_trait_frac,
+                                 R=R, homophily=homophily)
+
+        elif experiment == 'disliking':
+            trial_func = partial(_one_minority_trial, n_iter=n_iter,
+                                 covert_rec_prob=0.25,
+                                 one_dislike_penalty=exp_param,
+                                 two_dislike_penalty=exp_param,
+                                 minority_trait_frac=minority_trait_frac,
+                                 R=R, homophily=homophily)
+        else:
+            raise RuntimeError(f'{experiment} not recognized')
+
+        results = list(pool.map(trial_func, seeds))
+
+        r0 = results[0]
+        results_dict = {k: [] for k in r0.keys()}
+        for result in results:
+            for k, v in result.items():
+                results_dict[k].append(v)
+
+        ret_series_data = {k: np.array(v).flatten()
+                           for k, v in results_dict.items()}
+            # results_dict.update({
+            #     k: results_dict[k].append(v) for k, v in result.items()
+            # })
+
+    ret_dict = {
+        'timestep': list(range(n_iter + 1)) * n_trials,
+
+        'trial_idx': [idx
+                      for _ in range(n_iter + 1)
+                      for idx in range(n_trials)],
+
+        'homophily': [homophily] * n_trials * (n_iter + 1),
+
+        # XXX this suggests changing column to 'disliking' for that
+        # experiment.
[…]

### 2020-02-26 id_signaling/figures.py

@@ -4,7 +4,10 @@ import matplotlib.pyplot as plt
 
 
 def plot_evolution(df, experiment='receptivity',
-                   strategy='signaling', parameter_vals=[0.1, 0.25, 0.4],
+                   strategy='signaling',
+                   exp_param_vals=[0.1, 0.25, 0.4],
+                   homophily_vals=[0.1, 0.25, 0.4],
+                   minority_subset=None,
                    savefig_path=None,
                    **plot_kwargs):
     '''
@@ -17,6 +20,9 @@ def plot_evolution(df, experiment='receptivity',
             output variable to use. If 'signaling', the proportion of
             covert signalers is plotted. If 'receiving', the proportion of
             churlish receivers is plotted.
+        minority_subset (str or None): If given, should be 'minority' or
+            'majority' to plot either minority or majority evolution of
+            signaling or receiving strategy.
         parameter_vals (list): Values of the homophily and disliking/receiving
             parameters to plot, used for subsetting input data frame.
         plot_kwargs (dict): Additional arguments for passing to plotting
@@ -27,13 +33,14 @@ def plot_evolution(df, experiment='receptivity',
     # and strategy is plotted.
     if experiment == 'disliking':
         exp_inset = '$(d=\delta,~w)$'
-        exp_col = 'dislike_penalty'
+        exp_col = 'disliking'
     elif experiment == 'receptivity':
         exp_inset = '$(r/R,~w)$'
         exp_col = 'receptivity'
     else:
         raise RuntimeError(f'{experiment} not recognized')
 
+    # Plot non-minority/majority subsetted data.
     if strategy == 'signaling':
         strategy_inset = 'Covert signalers'
         data_col = 'prop_covert'
@@ -43,32 +50,33 @@ def plot_evolution(df, experiment='receptivity',
     else:
         raise RuntimeError(f'{strategy} not recognized')
 
+    # Modify title/ylabel inset and data column of interest if subsetting.
+    if minority_subset == 'minority':
+        strategy_inset += ' minority'
+        data_col += '_minority'
+    elif minority_subset == 'majority':
+        strategy_inset += ' majority'
+        data_col += '_majority'
+
     # Build title from `inset`s above.
     title = f'{strategy_inset} over time for various {exp_inset} pairs'
 
[…]

### 2020-02-26 id_signaling/model.py

@@ -2,10 +2,11 @@
 Model of the evolution of identity covert signaling
 
 Author: Matthew A. Turner
-Date: 2020-01-23
+Date: 2020-02-25
 '''
 import numpy as np
 
+from copy import deepcopy
 from numpy.random import choice, uniform
 from scipy.special import expit
 
@@ -20,6 +21,7 @@ class Model:
                  prob_covert_receiving=0.25, similarity_benefit=0.25,
                  one_dislike_penalty=0.25, two_dislike_penalty=0.25,
                  homophily=0.25, random_seed=None, similarity_threshold=1,
+                 minority_trait_frac=None,
                  evo_logistic_loc=1.25, evo_logistic_scale=12):
         '''
         Arguments:
@@ -40,6 +42,10 @@ class Model:
             similarity_threshold (int): the minimum difference between the
                 number of traits agents have in common and number of
                 opposing traits
+            minority_trait_frac (float): number between 0 and 1 indicating
+                what fraction of agents should be ``minority'' agents with
+                first trait +1, and set first trait of majority to -1. If
+                None, do not set minority agents.
             evo_logistic_loc (float): location where logistic function = 0.5
                 probability of switching strategies depending on relative
                 payoff. I.e. default is set so that 50% chance of switching
@@ -70,6 +76,46 @@ class Model:
 
         self.agents = [Agent(idx, K=K, N=N) for idx in range(N)]
 
+        # Have a marker for the run() method if it should track majority/
+        # minority agents over time so we can later recover their
+        # proportional strategies.
+        self.minority_test = False
+        if minority_trait_frac is not None:
+
+            # Set minority_trait_frac of agents to have first trait +1
+            # and set the rest to have -1. The +1 will be the minorities
+            # along the first trait dimension.
+            self.minority_test = True
+
+            # Select minority agents.
+            self.minority_agents = list(choice(self.agents,
+                                         size=int(N*minority_trait_frac),
+                                         replace=False))
+
+            # Majority agents are the ones unselected for minority.
+            self.majority_agents = list(
+                set(self.agents) - set(self.minority_agents)
+            )
+
+
+            # Initialize a series of agents over time. See below.
+            # self.minority_agents_series = []
+            # self.majority_agents_series = []
+
+            self.prop_covert_series_minority = np.array(
+                [_proportion_covert(self, subset='minority')]
+            )
[…]

### 2020-02-26 run_minority_experiment.py

@@ -1,0 +1,22 @@
+from id_signaling.experiment import run_experiments
+
+import sys
+import os
+
+# XXX Change this to change the minority fraction.
+minority_trait_frac = 0.1
+
+data_dir = 'output_data'
+
+disliking_penalties = [0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45]
+homophilies = disliking_penalties[2:] + [0.49, 0.5]
+
+df = run_experiments(disliking_penalties, homophilies,
+    minority_trait_frac=minority_trait_frac,
+    experiment='disliking',
+    n_iter=200,
+    n_trials=100
+)
+
+df.to_csv(os.path.join(data_dir, f'minorities_{minority_trait_frac}.csv'),
+          index=False)

### 2020-02-26 id_signaling/model.py
now setting traits; wasn't actually before, just splitting minority and majority into groups with random first traits

@@ -97,10 +97,11 @@ class Model:
                 set(self.agents) - set(self.minority_agents)
             )
 
-
-            # Initialize a series of agents over time. See below.
-            # self.minority_agents_series = []
-            # self.majority_agents_series = []
+            # Set traits.
+            for agent in self.minority_agents:
+                agent.traits[0] = 1
+            for agent in self.majority_agents:
+                agent.traits[0] = -1
 
             self.prop_covert_series_minority = np.array(
                 [_proportion_covert(self, subset='minority')]

### 2020-02-26 id_signaling/model.py
restricting teachers to in-groups for minority/majority experiments

@@ -268,18 +268,26 @@ class Model:
 
             # Calculate interaction probability for every possible teacher,
             # setting self-teaching probability to zero.
+            if self.minority_test:
+                if learner in self.minority_agents:
+                    maybe_teachers = self.minority_agents
+                else:
+                    maybe_teachers = self.majority_agents
+            else:
+                maybe_teachers = self.agents
+
             probs = np.array(
                 [
                     self._dyadic_interaction_prob(learner, maybe_teacher)
                     if maybe_teacher != learner else 0.0
 
-                    for maybe_teacher in self.agents
+                    for maybe_teacher in maybe_teachers
                 ]
             )
             # Normalize probabilities.
             probs = probs / probs.sum()
             # Weight random teacher selection by calculated probabilities.
-            teacher = choice(self.agents, p=probs)
+            teacher = choice(maybe_teachers, p=probs)
 
             # Learner payoff sometimes is zero at the beginning of the model...
             if learner.payoff > 0:

### 2020-02-26 id_signaling/experiment.py
minorities experiment working, have results for 0.1 frac

@@ -142,7 +142,7 @@ def trials_minority(exp_param, homophily, minority_trait_frac=0.1,
         # XXX this suggests changing column to 'disliking' for that
         # experiment.
         experiment: [exp_param] * n_trials * (n_iter + 1)
-        }
+    }
 
     ret_dict.update(ret_series_data)
 

### 2020-02-26 id_signaling/figures.py

@@ -1,6 +1,6 @@
-
-
 import matplotlib.pyplot as plt
+import numpy as np
+import seaborn as sns
 
 
 def plot_evolution(df, experiment='receptivity',
@@ -52,14 +52,14 @@ def plot_evolution(df, experiment='receptivity',
 
     # Modify title/ylabel inset and data column of interest if subsetting.
     if minority_subset == 'minority':
-        strategy_inset += ' minority'
+        strategy_inset += ' in minority'
         data_col += '_minority'
     elif minority_subset == 'majority':
-        strategy_inset += ' majority'
+        strategy_inset += ' in majority'
         data_col += '_majority'
 
     # Build title from `inset`s above.
-    title = f'{strategy_inset} over time for various {exp_inset} pairs'
+    title = f'{strategy_inset}\nover time for various {exp_inset} pairs'
 
     # Limit data to specified parameter values.
     df = df[
@@ -76,11 +76,11 @@ def plot_evolution(df, experiment='receptivity',
 
     # Put legend outside of plot with label determined by experiment type.
     plt.legend(bbox_to_anchor=(1.01, 0.9), loc='upper left', ncol=1, title=exp_inset,
-               borderaxespad=0, frameon=False, prop={'size': 12})
+               borderaxespad=0, frameon=False, prop={'size': 12}, title_fontsize=14)
 
     plt.xticks(size=12)
     plt.yticks(size=12)
-    plt.ylabel(f'Proportion of {strategy_inset.lower()}', size=16)
+    plt.ylabel(f'Proportion of\n{strategy_inset.lower()}', size=16)
     plt.xlabel('Timestep', size=16)
     plt.title(title, size=14)
 
@@ -88,11 +88,167 @@ def plot_evolution(df, experiment='receptivity',
         plt.savefig(savefig_path)
 
 
-def heatmap(df, strategy='signal'):
-    pass
+def heatmap(df, experiment='disliking', strategy='signaling',
+            figsize=(6, 4.75), minority_subset=None, savefig_path=None):
+
+    if experiment == 'disliking':
+        exp_inset = '$(d=\delta,~w)$'
+        exp_col = 'disliking'
+    elif experiment == 'receptivity':
+        exp_inset = '$(r/R,~w)$'
+        exp_col = 'receptivity'
+    else:
+        raise RuntimeError(f'{experiment} not recognized')
+
+    # Plot non-minority/majority subsetted data.
[…]

### 2020-02-26 reports/Progress-2-25.tex
complete prototype of minorities experiment

--- 2020-02-19 reports/Progress-2-19.tex
@@
 
-\section*{Evolution in signaling strategy}
+\section{Evolution in signaling and receiving strategies}
 
 For these preliminary results I focus on the evolution of signaling strategies,
-and set receiving strategies to be randomly assigned with probability 0.5 to
-each agent at model initialization. The output measure in these experiments
-is density of covert signalers. There are confirmatory results for two
-computational experiments in which I: (1) varied relative covert receptivity $r/R$ and 
+each agent at model initialization. There are two output measures in these experiments:
+density of covert signalers and density of churlish receivers. 
+There are confirmatory results for two computational experiments in which I: 
+(1) varied relative covert receptivity $r/R$ and 
 homophily, $w$; and (2) varied the disliking penalties set equal, $d=\delta$,
@@
 
-\subsection*{Density of covert signalers vs. $r/R$ and homophily, $w$}
+The bonus payoff for two 
+interacting agents where at least one
+likes the other is set fixed to $s=0.25$. The payoff structure is as follows
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{rcc}
+    Attitude combo. & Payoff (similar) & Payoff (dissim.) \\
+   \toprule
+    Like/like & $1 + s$                    & NA \\
+    Like/neutral & $1 + s$                 & NA \\
+    Like/dislike & $1 + s - d$             & NA \\
+    Neutral/neutral & 1 + s                & 1  \\
+    Dislike/neutral & $1 + s - d$          & $1-d$\\
+    Dislike/dislike & $1 + s - d - \delta$ & $1 - d - \delta$
+  \end{tabular}
+\end{table}
+
+Agents only interact with one another with probability given by their attitudes
+towards one another. If two agents are assorted together to potentially 
+interact, these are the probabilities the agents do interact.
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{rc}
+    Attitudes & Pr(paired agents interact) \\
+    \toprule
+    Like/like & $0.5 + w$ \\
+    Like/neutral & $0.5 + \frac{w}{2}$ \\
+    Like/dislike & $0.5$ \\
+    Neutral/neutral & $0.5$ \\
+    Dislike/neutral & $0.5 - \frac{w}{2}$ \\
+    Dislike/dislike & $0.5 - w$ 
+  \end{tabular}
+\end{table}
+
+\subsection{Density of covert signalers vs. $r/R$ and homophily, $w$}
 
@@
 
-\subsection*{Density of covert signalers vs. disliking penalty $d=\delta$ and homophily, $w$}
+\subsection{Density of covert signalers vs. disliking penalty $d=\delta$ and homophily, $w$}
 
-Here we co-vary the disliking penalties, which we set equal ($d=\delta$), and
-homophily, $w$. I ran the model to 200 timesteps this time, which did allow
-the series to settle more, but perhaps not to a significant degree 
-(Figure~\ref{fig:dislikingHomophilySeries}). The bonus payoff for two 
-interacting agents where at least one
-likes the other is set fixed to $s=0.25$. The payoff structure is as follows
+Here I co-vary the disliking penalties, which I set equal ($d=\delta$), and
+homophily, $w$. Here, $r=0.25$ and $R=0.5$.
 
-\begin{table}[H]
-  \centering
-  \begin{tabular}{rl}
-   Attitude combo. & Payoff \\
-   \toprule
-    Like/like & $1 + s$ \\
-    Like/neutral & $1 + s$ \\
-    Neutral/neutral & 1 \\
-    Like/dislike & $1 + s - d$ \\
-    Dislike/neutral & $1 - d$ \\
-    Dislike/dislike & $1 - d - \delta$
-  \end{tabular}
-\end{table}
-
-Specifically, we vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$
-As in the above experiment, we set $w \in \{0.0, 0.5, \ldots, 0.45\}$.
+Specifically, I vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$
+As in the above experiment, I set $w \in \{0.0, 0.5, \ldots, 0.45\}$.
 
@@
 
-\section*{Discussion}
+\subsection{Correlations between proportion of covert signalers and of churlish receivers}
 
-These preliminary experiments and results are based on one major finding from
-ECS that covert signaling is maintained when overt signalers do not have
-too large an advantage in the free choice context. ``This requires that
-assortment with liked individuals not be too accurate,'' which corresponds to
-small $w$ in this ABM version. ``The accuracy of assortment is influenced
-by the reception probabilities of both signal types, $R$ and $r$'' (see p.
-4 in ECS). Our preliminary results find the same trend with our ABM.
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/receptivity_allcombos_reg.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/disliking_allcombos_reg.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Correlation between proportion of covert signalers and proportion of
+    churlish receivers for all tested parameter combinations in both 
+    receptivity (a) and disliking (b) experiments.}
+  \label{fig:regressions}
+\end{figure}
+
+\section{Minority populations}
+
+So far in these results I tested the case where a 10\% of all agents have
+the minority trait, $+1$ in the first trait vector position. 
+The other 90\% have the majority trait, $-1$ in the first trait vector position.
+
+$r=0.25$, $R=0.5$.
+
+\subsection{Covert signaling}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/covert_series_majority.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/covert_series_minority.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Mean timeseries of the evolution of covert signaling in the
+    majority (a) and minority (b) populations.}
+  \label{fig:regressions}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/majority_signalers.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/minority_signalers.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Proprtion of covert signalers for different parameter settings in the
+    majority (a) and minority (b) populations.}
+  \label{fig:regressions}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.6\textwidth]{Figures/covert_signalers_diff.pdf}
+  \caption{Difference between proportion of covert signalers in the minority 
+    and majority populations. When cost of disliking is high and homophily is 
+    low, more minority agents are covert signalers than majority agents,
+    proportionally. An increase in homophily enables minority agents to 
+    find one another more easily, so overt signaling, which reaches more of
+    the population, is advantageous.
+  }
+  \label{fig:}
+\end{figure}
+
+\subsection{Churlish receiving}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/churlish_series_majority.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/churlish_series_minority.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Mean timeseries of the evolution of churlish receiving in the
+    majority (a) and minority (b) populations.}
+  \label{fig:regressions}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/majority_receivers.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/minority_receivers.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Proprtion of churlish receivers for different parameter settings in the
+    majority (a) and minority (b) populations.}
+  \label{fig:regressions}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.6\textwidth]{Figures/churlish_receivers_diff.pdf}
+  \caption{Difference between proportion of churlish receivers in the minority 
+    and majority populations. Here the dependence is primarily on homophily.
+    If homophily is too low, the minority population cannot interact often
+    enough with their in-group, and so must adopt a non-churlish stance towards
+    others in order to not suffer cost of disliking penalties. Once the minority
+    can reliably find its in-group members (increasing homophily) the minority
+    can afford to assume they dislike others, since by and large they dislike
+    the majority.
+  }
+  \label{fig:}
+\end{figure}
+
+% \section{Discussion}
+
+% These preliminary experiments and results are based on one major finding from
+% ECS that covert signaling is maintained when overt signalers do not have
+% too large an advantage in the free choice context. ``This requires that
+% assortment with liked individuals not be too accurate,'' which corresponds to
+% small $w$ in this ABM version. ``The accuracy of assortment is influenced
+% by the reception probabilities of both signal types, $R$ and $r$'' (see p.
+% 4 in ECS). Our preliminary results find the same trend with our ABM.
 

### 2020-02-26 id_signaling/figures.py

@@ -185,7 +185,7 @@ def minority_diff_heatmap(df, strategy='signaling', savefig_path=None,
     plt.figure(figsize=figsize)
     ax = sns.heatmap(
         diff.stack(), square=True, vmin=vmin, vmax=vmax,
-        cmap=sns.diverging_palette(10, 220, sep=80, n=7),
+        cmap=sns.diverging_palette(10, 220, sep=80, n=10), #, center='dark'),
         cbar_kws={
             'label':
                 f'Difference in density\n'
@@ -215,7 +215,8 @@ def minority_diff_heatmap(df, strategy='signaling', savefig_path=None,
 
 def covert_churlish_regression(df, # exp_param_vals, homophily_vals,
                                experiment='receptivity',
-                               minority_subset=None, **kwargs):
+                               minority_subset=None, savefig_path=None,
+                               **kwargs):
     # Get pairs of final (prop_covert, prop_churlish) for each trial and
     # perform/plot regression of prop_covert vs. prop_churlish.
 # Set up plot annotations depending on which kind of experiment
@@ -243,12 +244,17 @@ def covert_churlish_regression(df, # exp_param_vals, homophily_vals,
 
     x = df[xcol]
     y = df[ycol]
-    from scipy import stats
-    sns.regplot(x, y, line_kws=dict(color='r'))
-    pearson_coef, p_value = stats.pearsonr(x, y) #define the columns to perform calculations on
-    plt.title(f'{experiment.title()}, all parameter combinations\nPearson correlation coefficient: {pearson_coef:.2f}\nP-value: {p_value:.2e}')
-            # sns.jointplot(x, y, kind='reg', # label=f'{(exp_param_val, homophily_val)}',
-            #   annot_kws=dict(stat='r', template='{stat} = {val:.2g}; p = {p:.1e}', frameon=False))
 
-    # plt.legend(bbox_to_anchor=(1.01, 0.9), loc='upper left', ncol=1, title=exp_inset,
-    #            borderaxespad=0, frameon=False, prop={'size': 12})
+    from scipy import stats
+
+    sns.regplot(x, y, line_kws=dict(color='r'),
+                scatter_kws=dict(lw=0, s=45, alpha=0.125))
+    plt.ylabel('Covert signaler proportion', size=16)
+    plt.xlabel('Churlish receiver proportion', size=16)
+
+    pearson_coef, p_value = stats.pearsonr(x, y) #define the columns to perform calculations on
+
[…]

### 2020-02-26 reports/Progress-2-26.tex
report and NB updated with min. frac. 0.25

--- 2020-02-26 reports/Progress-2-25.tex
@@
 \setlength\intextsep{0pt}
+\hypersetup{linktocpage}
 
@@
 \maketitle
+\tableofcontents
 
@@
 
-So far in these results I tested the case where a 10\% of all agents have
+So far in these results I tested the case where a 10\% or 25\% of all agents have
 the minority trait, $+1$ in the first trait vector position. 
-The other 90\% have the majority trait, $-1$ in the first trait vector position.
+The other 90\% or 75\% have the majority trait, $-1$ in the first trait vector position.
 
@@
 
+\subsubsection{Fraction of minorities = 0.10}
 \begin{figure}[H]
@@
     majority (a) and minority (b) populations.}
-  \label{fig:regressions}
+  \label{fig:}
 \end{figure}
@@
 
+\subsubsection{Fraction of minorities = 0.25}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/covert_series_majority_025.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/covert_series_minority_025.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Mean timeseries of the evolution of covert signaling in the
+    majority (a) and minority (b) populations.}
+  \label{fig:regressions}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/majority_signalers_025.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/minority_signalers_025.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Proprtion of covert signalers for different parameter settings in the
+    majority (a) and minority (b) populations.}
+  \label{fig:regressions}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.6\textwidth]{Figures/covert_signalers_diff_025.pdf}
+  \caption{Difference between proportion of covert signalers in the minority 
+    and majority populations. When cost of disliking is high and homophily is 
+    low, more minority agents are covert signalers than majority agents,
+    proportionally. An increase in homophily enables minority agents to 
+    find one another more easily, so overt signaling, which reaches more of
+    the population, is advantageous.
+  }
+  \label{fig:}
+\end{figure}
+
 \subsection{Churlish receiving}
+
+\subsubsection{Fraction of minorities = 0.10}
 
@@
 
+\subsubsection{Fraction of minorities = 0.25}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/churlish_series_majority_025.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/churlish_series_minority_025.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Mean timeseries of the evolution of churlish receiving in the
+    majority (a) and minority (b) populations.}
+  \label{fig:regressions}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/majority_receivers_025.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/minority_receivers_025.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Proprtion of churlish receivers for different parameter settings in the
+    majority (a) and minority (b) populations.}
+  \label{fig:regressions}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.6\textwidth]{Figures/churlish_receivers_diff_025.pdf}
+  \caption{Difference between proportion of churlish receivers in the minority 
+    and majority populations. Here the dependence is primarily on homophily.
+    If homophily is too low, the minority population cannot interact often
+    enough with their in-group, and so must adopt a non-churlish stance towards
+    others in order to not suffer cost of disliking penalties. Once the minority
+    can reliably find its in-group members (increasing homophily) the minority
+    can afford to assume they dislike others, since by and large they dislike
+    the majority.
+  }
+  \label{fig:}
+\end{figure}
+
 % \section{Discussion}

### 2020-02-26 id_signaling/figures.py
changed y-axis on heatmaps for homophily to include .49 and .5

@@ -151,7 +151,7 @@ def heatmap(df, experiment='disliking', strategy='signaling',
         relative_receptivity.sort()
         ax.set_xticklabels(relative_receptivity)
 
-    ax.set_yticklabels([f'{y:.2f}' for y in np.arange(0, 0.46, 0.05)]);
+    ax.set_yticklabels([f'{y:.2f}' for y in np.arange(0.1, 0.46, 0.05)] + ['0.49', '0.50']);
 
     if savefig_path is not None:
         plt.savefig(savefig_path)
@@ -208,7 +208,8 @@ def minority_diff_heatmap(df, strategy='signaling', savefig_path=None,
     ax.invert_yaxis()
     # ax.set_yticklabels(['0.1', '0.25', '0.4'])
     ax.set_ylabel('Homophily, $w$', size=15)
-    ax.set_yticklabels([f'{y:.2f}' for y in np.arange(0, 0.46, 0.05)]);
+    # ax.set_yticklabels([f'{y:.2f}' for y in np.arange(0, 0.46, 0.05)]);
+    ax.set_yticklabels([f'{y:.2f}' for y in np.arange(0.1, 0.46, 0.05)] + ['0.49', '0.50']);
 
     if savefig_path is not None:
         plt.savefig(savefig_path)

### 2020-03-11 reports/Progress.tex
finished preliminary minority experiments
beginning refactor with writing README documenting how to run experiments

--- 2020-02-26 reports/Progress-2-26.tex
@@
 
+\subsubsection{Fraction of minorities = 0.05}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/covert_series_majority_005.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/covert_series_minority_005.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Mean timeseries of the evolution of covert signaling in the
+    majority (a) and minority (b) populations.}
+  \label{fig:regressions}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/majority_signalers_005.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/minority_signalers_005.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Proprtion of covert signalers for different parameter settings in the
+    majority (a) and minority (b) populations.}
+  \label{fig:regressions}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.6\textwidth]{Figures/covert_signalers_diff_005.pdf}
+  \caption{Difference between proportion of covert signalers in the minority 
+    and majority populations. When cost of disliking is high and homophily is 
+    low, more minority agents are covert signalers than majority agents,
+    proportionally. An increase in homophily enables minority agents to 
+    find one another more easily, so overt signaling, which reaches more of
+    the population, is advantageous.
+  }
+  \label{fig:}
+\end{figure}
+
 \subsection{Churlish receiving}
@@
 
+\subsubsection{Fraction of minorities = 0.05}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/churlish_series_majority_005.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/churlish_series_minority_005.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Mean timeseries of the evolution of churlish receiving in the
+    majority (a) and minority (b) populations.}
+  \label{fig:regressions}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/majority_receivers_005.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/minority_receivers_005.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Proprtion of churlish receivers for different parameter settings in the
+    majority (a) and minority (b) populations.}
+  \label{fig:regressions}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.6\textwidth]{Figures/churlish_receivers_diff_005.pdf}
+  \caption{Difference between proportion of churlish receivers in the minority 
+    and majority populations. Here the dependence is primarily on homophily.
+    If homophily is too low, the minority population cannot interact often
+    enough with their in-group, and so must adopt a non-churlish stance towards
+    others in order to not suffer cost of disliking penalties. Once the minority
+    can reliably find its in-group members (increasing homophily) the minority
+    can afford to assume they dislike others, since by and large they dislike
+    the majority.
+  }
+  \label{fig:}
+\end{figure}
+
 % \section{Discussion}

### 2020-03-11 id_signaling/experiment.py

@@ -186,15 +186,16 @@ def run_experiments(exp_param_vals, homophily_vals, experiment='receptivity',
                           experiment=experiment, n_trials=n_trials,
                           n_iter=n_iter, R=R)
             else:
-                df = func(val, val, n_iter=n_iter, n_trials=n_trials, R=R)
+                df = func(exp_param_val, homophily,
+                          n_iter=n_iter, n_trials=n_trials, R=R)
 
             if df_full is None:
                 df_full = df
             else:
                 df_full = df_full.append(df)
 
-
     return df_full
+
 
 def trials_dislikepen_homophily(dislike_penalty, homophily, n_trials=10,
                                 n_iter=100, R=0.5):

### 2020-03-30 id_signaling/experiment.py
invasion experiment first pass; need to inspect small output sample

@@ -80,6 +80,8 @@ def _one_trial(trial_tup, experiment, n_iter, **model_kwargs):
     ret = dict(
         timestep=np.arange(0, n_tstep, dtype=int),
         trial_idx=[seed]*n_tstep,
+        initial_prop_covert=[model.initial_prop_covert]*n_tstep,
+        initial_prop_churlish=[model.initial_prop_churlish]*n_tstep,
         prop_covert=model.prop_covert_series,
         prop_churlish=model.prop_churlish_series,
         homophily=[homophily] * n_tstep
@@ -130,14 +132,3 @@ def _one_minority_trial(seed, n_iter, minority_trait_frac,
         'prop_churlish_majority': model.prop_churlish_series_majority,
     }
 
-# def analyze_covert_receiving_prob(results):
-
-#     # Calculate mean series for each covert receiving probability.
-#     mean_series = {
-#         covert_rec_prob: results_array.mean(axis=0)
-#         for covert_rec_prob, results_array in results.items()
-#     }
-
-#     # Plot them.
-#     for covert_rec_prob, series in mean_series.items():
-#         plt.plot(series, label=f"r/R = {covert_rec_prob / 0.5}")

### 2020-03-30 id_signaling/model.py

@@ -22,6 +22,7 @@ class Model:
                  one_dislike_penalty=0.25, two_dislike_penalty=0.25,
                  homophily=0.25, random_seed=None, similarity_threshold=1,
                  minority_trait_frac=None,
+                 initial_prop_covert=0.5, initial_prop_churlish=0.5,
                  evo_logistic_loc=1.25, evo_logistic_scale=12):
         '''
         Arguments:
@@ -69,12 +70,29 @@ class Model:
         self.evo_logistic_loc = evo_logistic_loc
         self.evo_logistic_scale = evo_logistic_scale
 
+        self.initial_prop_covert = initial_prop_covert
+        self.initial_prop_churlish = initial_prop_churlish
+
         assert (homophily >= 0.0) and (homophily <= 0.5)
 
         if random_seed is not None:
             np.random.seed(random_seed)
 
-        self.agents = [Agent(idx, K=K, N=N) for idx in range(N)]
+        choose_rec = lambda : \
+            choice(['Churlish', 'Generous'],
+                   p=[initial_prop_churlish, 1 - initial_prop_churlish])
+
+        choose_sig = lambda : \
+            choice(['Covert', 'Overt'],
+                   p=[initial_prop_covert, 1 - initial_prop_covert])
+
+        self.agents = [
+            Agent(idx, K=K, N=N,
+                  receiving_strategy=choose_rec(),
+                  signaling_strategy=choose_sig()
+                 )
+            for idx in range(N)
+        ]
 
         # Have a marker for the run() method if it should track majority/
         # minority agents over time so we can later recover their

### 2020-03-30 id_signaling/scripts/runner.py

@@ -33,19 +33,24 @@ def basic_decorator():
                      type=float, default=0.5),
         click.option('--minority_trait_frac', '-m',
                      type=float, default=None),
+        click.option('--initial_prop_covert', type=float, default=0.5),
+        click.option('--initial_prop_churlish', type=float, default=0.5),
    )
 
 ## RUNEXP ##
 @basic_decorator()
 def run(experiment, param_vals, homophily_vals, n_trials, n_iter,
-        output_file, prob_overt_receiving, minority_trait_frac):
+        output_file, prob_overt_receiving, minority_trait_frac,
+        initial_prop_covert, initial_prop_churlish):
 
     param_vals = np.arange(*[float(val) for val in param_vals.split(':')])
     homophily_vals = np.arange(*[float(val) for val in homophily_vals.split(':')])
     # XXX This is where to go to edit parallelization. See note in run_experiments XXX
     out_df = run_experiments(param_vals, homophily_vals, experiment, n_trials,
                              n_iter, prob_overt_receiving=prob_overt_receiving,
-                             minority_trait_frac=minority_trait_frac)
+                             minority_trait_frac=minority_trait_frac,
+                             initial_prop_covert=initial_prop_covert,
+                             initial_prop_churlish=initial_prop_churlish)
 
     out_df.to_csv(output_file, index=False)
 
@@ -55,19 +60,22 @@ def run(experiment, param_vals, homophily_vals, n_trials, n_iter,
 @click.option('--ncpu', '-n', type=int, default=100)
 @click.option('--wall_time', '-t', type=str, default='04:00:00')
 @click.option('--dry_run', '-d', is_flag=True)
+@click.option('--job_name', '-j', default=None)
 def sub(
-        experiment, param_vals, homophily_vals, n_trials, n_iter,
-        output_file, overt_receptivity, minority_trait_frac,
-        queue, ncpu, wall_time, dry_run
+        experiment, param_vals, homophily_vals, n_iter, n_trials,
+        output_file, prob_overt_receiving, minority_trait_frac,
+        initial_prop_covert, initial_prop_churlish,
+        queue, ncpu, wall_time, dry_run, job_name
     ):
     """
     Submit experiment trials to the cluster using slurm .sub template.
     """
 
-    if minority_trait_frac is not None:
-        job_name = f'minority_{minority_trait_frac}'
-    else:
-        job_name = experiment
[…]

### 2020-03-30 run_all_experiments.sh

@@ -1,0 +1,34 @@
+# run_all_experiments.sh
+# 2020-03-29
+
+# An executable bit of documentation of how to run all the experiments used
+# for the computational modeling publication.
+
+# runexp disliking 0.0:0.51:0.25 0.0:0.51:0.25 40 4 invasion-part-`uuidgen`.csv -R0.5  \
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.05 --initial_prop_churlish=0.95
+
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.95
+
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.5 --initial_prop_churlish=0.95
+
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.5
+
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.5 --initial_prop_churlish=0.95
+
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.5
+
+# Get header from last filename
+head -n1 $fname > invasion-full.csv
+tail invasion-part-*.csv >> invasion-full.csv

### 2020-03-30 run_invasion_experiments_sample.sh

@@ -1,0 +1,54 @@
+# run_all_experiments.sh
+# 2020-03-29
+
+# An executable bit of documentation of how to run all the experiments used
+# for the computational modeling publication.
+
+printf "\nRunning .95, .95\n"
+fname=invasion-part-`uuidgen`
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.95
+
+printf "\nRunning .5, .95\n"
+fname=invasion-part-`uuidgen`
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.5 --initial_prop_churlish=0.95
+
+printf "\nRunning .05, .95\n"
+fname=invasion-part-`uuidgen`
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.05 --initial_prop_churlish=0.95
+
+printf "\nRunning .95, .5\n"
+fname=invasion-part-`uuidgen`
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.5
+
+printf "\nRunning .5, .5\n"
+fname="invasion-part-`uuidgen`"
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.5 --initial_prop_churlish=0.5
+
+printf "\nRunning .05, .95\n"
+fname=invasion-part-`uuidgen`
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.05 --initial_prop_churlish=0.5
+
+printf "\nRunning .95, .05\n"
+fname=invasion-part-`uuidgen`
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.05
+
+printf "\nRunning .5, .05\n"
+fname=invasion-part-`uuidgen`
[…]

### 2020-03-30 sub_invasion_experiments_sample.sh

@@ -1,0 +1,72 @@
+# run_all_experiments.sh
+# 2020-03-29
+
+# An executable bit of documentation of how to run all the experiments used
+# for the computational modeling publication.
+
+printf "\nRunning .95, .95\n"
+fname=invasion-part-`uuidgen`
+subexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.95 \
+    -d -qfast.q -j$fname -n10 -t"00:10:00"
+
+
+printf "\nRunning .5, .95\n"
+fname=invasion-part-`uuidgen`
+subexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.5 --initial_prop_churlish=0.95 \
+    -d -qfast.q -j$fname -n10 -t"00:10:00"
+
+
+printf "\nRunning .05, .95\n"
+fname=invasion-part-`uuidgen`
+subexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.05 --initial_prop_churlish=0.95 \
+    -d -qfast.q -j$fname -n10 -t"00:10:00"
+
+
+printf "\nRunning .95, .5\n"
+fname=invasion-part-`uuidgen`
+subexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.5 \
+    -d -qfast.q -j$fname -n10 -t"00:10:00"
+
+
+printf "\nRunning .5, .5\n"
+fname=invasion-part-`uuidgen`
+subexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.5 --initial_prop_churlish=0.5 \
+    -d -qfast.q -j$fname -n10 -t"00:10:00"
+
+
+printf "\nRunning .05, .95\n"
+fname=invasion-part-`uuidgen`
+subexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname.csv -R0.5  \
+    --initial_prop_covert=0.05 --initial_prop_churlish=0.5 \
[…]

### 2020-03-31 reports/Progress.tex
created runners for invasion experiment, on to test this on cluster

@@
 \end{figure}
+
+\section{Invasion experiments}
+
+Here we run identical experiments, but vary the initial proportion of 
+churlish receivers and covert receivers over $\{0.05, 0.5, 0.95\}$ for a total
+of nine parameter combinations. One of these is a repeat of the previous
+experiments, where both parameters are set to 0.5. Below are two figures.
+The first is nine parameter settings where the density of covert signalers
+is plotted in a heatmap (Figure~\ref{fig:invasion-signaling}). The second has 
+heatmaps of the density of churlish receivers (Figure~\ref{fig:invasion-receiving}).
+
+\input{invasion-figures.tex}
 

### 2020-03-31 id_signaling/figures.py

@@ -89,7 +89,8 @@ def plot_evolution(df, experiment='receptivity',
 
 
 def heatmap(df, experiment='disliking', strategy='signaling',
-            figsize=(6, 4.75), minority_subset=None, savefig_path=None):
+            figsize=(6, 4.75), minority_subset=None, savefig_path=None,
+            title=None, vmin=None, vmax=None):
 
     if experiment == 'disliking':
         exp_inset = '$(d=\delta,~w)$'
@@ -127,7 +128,8 @@ def heatmap(df, experiment='disliking', strategy='signaling',
 
     plt.figure(figsize=figsize)
     ax = sns.heatmap(final_means.stack(), cmap='YlGnBu_r', square=True,
-                    cbar_kws={'label': f'Density of {strategy_inset.lower()}'},
+                     cbar_kws={'label': f'Density of {strategy_inset.lower()}'},
+                     vmin=vmin, vmax=vmax
                     )
 
     # Set size of colorbar title.
@@ -153,6 +155,8 @@ def heatmap(df, experiment='disliking', strategy='signaling',
 
     ax.set_yticklabels([f'{y:.2f}' for y in np.arange(0.1, 0.46, 0.05)] + ['0.49', '0.50']);
 
+    if title is not None:
+        ax.set_title(title, size=14)
     if savefig_path is not None:
         plt.savefig(savefig_path)
 

### 2020-03-31 run_invasion_experiments.sh

@@ -1,0 +1,47 @@
+# run_all_experiments.sh
+# 2020-03-29
+
+# An executable bit of documentation of how to run all the experiments used
+# for the computational modeling publication.
+
+# runexp disliking 0.0:0.51:0.25 0.0:0.51:0.25 40 4 invasion-part-`uuidgen`.csv -R0.5  \
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.95
+
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.5 --initial_prop_churlish=0.95
+
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.05 --initial_prop_churlish=0.95
+
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.5
+
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.5 --initial_prop_churlish=0.5
+
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.05 --initial_prop_churlish=0.5
+
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.05
+
+
+fname=invasion-part-${uuidgen}
+runexp disliking 0.0:0.50:0.25 0.0:0.50:0.25 40 4 $fname -R0.5  \
+    --initial_prop_covert=0.5 --initial_prop_churlish=0.05
+
+fname=invasion-part-${uuidgen}
[…]

### 2020-03-31 run_invasion_experiments_prelimresults.sh

@@ -6,47 +6,47 @@
 
 printf "\nRunning .95, .95\n"
 fname=data/scratch/invasion-part-`uuidgen`
-runexp disliking 0.0:0.51:0.25 0.0:0.51:0.25 40 4 $fname.csv -R0.5  \
+runexp disliking 0.0:0.51:0.25 0.0:0.51:0.25 100 10 $fname.csv -R0.5  \
     --initial_prop_covert=0.95 --initial_prop_churlish=0.95 > $fname.log
 
 printf "\nRunning .5, .95\n"
 fname=data/scratch/invasion-part-`uuidgen`
-runexp disliking 0.0:0.51:0.25 0.0:0.51:0.25 40 4 $fname.csv -R0.5  \
+runexp disliking 0.0:0.51:0.25 0.0:0.51:0.25 100 10 $fname.csv -R0.5  \
     --initial_prop_covert=0.5 --initial_prop_churlish=0.95 > $fname.log
 
 printf "\nRunning .05, .95\n"
 fname=data/scratch/invasion-part-`uuidgen`
-runexp disliking 0.0:0.51:0.25 0.0:0.51:0.25 40 4 $fname.csv -R0.5  \
+runexp disliking 0.0:0.51:0.25 0.0:0.51:0.25 100 10 $fname.csv -R0.5  \
     --initial_prop_covert=0.05 --initial_prop_churlish=0.95 > $fname.log
 
 printf "\nRunning .95, .5\n"
 fname=data/scratch/invasion-part-`uuidgen`
-runexp disliking 0.0:0.51:0.25 0.0:0.51:0.25 40 4 $fname.csv -R0.5  \
+runexp disliking 0.0:0.51:0.25 0.0:0.51:0.25 100 10 $fname.csv -R0.5  \
     --initial_prop_covert=0.95 --initial_prop_churlish=0.5 > $fname.log
 
 printf "\nRunning .5, .5\n"
 fname="data/scratch/invasion-part-`uuidgen`"
-runexp disliking 0.0:0.51:0.25 0.0:0.51:0.25 40 4 $fname.csv -R0.5  \
+runexp disliking 0.0:0.51:0.25 0.0:0.51:0.25 100 10 $fname.csv -R0.5  \
     --initial_prop_covert=0.5 --initial_prop_churlish=0.5 > $fname.log
 
 printf "\nRunning .05, .95\n"
 fname=data/scratch/invasion-part-`uuidgen`
[…]

### 2020-03-31 id_signaling/scripts/runner.py
added sbatch run in runner

@@ -1,5 +1,6 @@
 import click
 import numpy as np
+import subprocess
 
 from id_signaling.experiment import run_experiments
 
@@ -98,4 +99,4 @@ printf "******************\\nFinished at `uptime`"
         print(subscript)
 
     else:
-        pass  # TODO submit the subscript using squeue
+        subprocess.run(['sbatch'], stdin=subscript)

### 2020-03-31 id_signaling/experiment.py
running on cluster

@@ -3,6 +3,7 @@ Computational experiments investigating behavior of the identity
 signalling model over different parameter settings and other experimental
 treatments.
 '''
+import click
 import matplotlib.pyplot as plt
 import multiprocessing as mp
 import numpy as np
@@ -56,7 +57,8 @@ def _one_trial(trial_tup, experiment, n_iter, **model_kwargs):
     exp_param = trial_tup[1]
     homophily = trial_tup[2]
 
-    print(f'running trial with random seed {seed}')
+    # print(f'running trial with random seed {seed}')
+    click.echo(f'running trial with random seed {seed}')
 
     # Initialize model for trial.
     if experiment == 'disliking':

### 2020-03-31 id_signaling/scripts/runner.py

@@ -2,6 +2,8 @@ import click
 import numpy as np
 import subprocess
 
+from subprocess import PIPE
+
 from id_signaling.experiment import run_experiments
 
 
@@ -32,21 +34,29 @@ def basic_decorator():
         click.argument('output_file'),
         click.option('--prob_overt_receiving', '-R',
                      type=float, default=0.5),
-        click.option('--minority_trait_frac', '-m',
-                     type=float, default=None),
+        click.option('--minority_trait_frac', '-m'),
         click.option('--initial_prop_covert', type=float, default=0.5),
         click.option('--initial_prop_churlish', type=float, default=0.5),
    )
 
 ## RUNEXP ##
 @basic_decorator()
-def run(experiment, param_vals, homophily_vals, n_trials, n_iter,
+def run(experiment, param_vals, homophily_vals, n_iter, n_trials,
         output_file, prob_overt_receiving, minority_trait_frac,
         initial_prop_covert, initial_prop_churlish):
 
+    # XXX Hack to deal with subexp throwing error I don't understand that
+    # minority_trait_frac can't be None (the default) because it's not a
+    # float. This doesn't seem to happen just with runexp.
+    print(minority_trait_frac)
+    if minority_trait_frac == 'None':
+        minority_trait_frac = None
+    if minority_trait_frac is not None:
+        minority_trait_frac = float(minority_trait_frac)
+
     param_vals = np.arange(*[float(val) for val in param_vals.split(':')])
     homophily_vals = np.arange(*[float(val) for val in homophily_vals.split(':')])
-    # XXX This is where to go to edit parallelization. See note in run_experiments XXX
+
     out_df = run_experiments(param_vals, homophily_vals, experiment, n_trials,
                              n_iter, prob_overt_receiving=prob_overt_receiving,
                              minority_trait_frac=minority_trait_frac,
@@ -89,7 +99,7 @@ f'''#! /bin/bash
 
 printf "******************\\nStarting {job_name} at `uptime`\\n"
 
-runexp {experiment} {param_vals} {homophily_vals} {n_trials} {n_iter} \\
+runexp {experiment} {param_vals} {homophily_vals} {n_iter} {n_trials} \\
     {output_file} -R{prob_overt_receiving} -m{minority_trait_frac}
 
 printf "******************\\nFinished at `uptime`"
@@ -99,4 +109,4 @@ printf "******************\\nFinished at `uptime`"
[…]

### 2020-03-31 sub_invasion_experiments_cluster.sh

@@ -1,0 +1,139 @@
+# An executable bit of documentation of how to run all the experiments used
+# for the computational modeling publication.
+
+# printf "\nRunning .95, .95\n"
+# fname=output_data/invasion/disliking/part-`uuidgen`
+# subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 50 20 $fname.csv -R0.5  \
+#     --initial_prop_covert=0.95 --initial_prop_churlish=0.95 \
+#     -qfast.q -j$fname -n200 -t"01:00:00"
+
+printf "\nRunning .95, .95\n"
+fname=output_data/invasion/disliking/part-`uuidgen`
+subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.95 \
+    -qfast.q -j$fname -n200 -t"04:00:00"
+    # -qfast.q -j$fname -n200 -t"04:00:00"
+
+
+printf "\nRunning .5, .95\n"
+fname=output_data/invasion/disliking/part-`uuidgen`
+subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
+    --initial_prop_covert=0.5 --initial_prop_churlish=0.95 \
+    -qfast.q -j$fname -n200 -t"04:00:00"
+
+
+printf "\nRunning .05, .95\n"
+fname=output_data/invasion/disliking/part-`uuidgen`
+subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
+    --initial_prop_covert=0.05 --initial_prop_churlish=0.95 \
+    -qfast.q -j$fname -n200 -t"04:00:00"
+
+
+printf "\nRunning .95, .5\n"
+fname=output_data/invasion/disliking/part-`uuidgen`
+subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.5 \
+    -qfast.q -j$fname -n200 -t"04:00:00"
+
+
+printf "\nRunning .5, .5\n"
+fname=output_data/invasion/disliking/part-`uuidgen`
[…]

### 2020-04-01 id_signaling/scripts/runner.py
fixed nodes vs cores mistake

@@ -94,7 +94,8 @@ f'''#! /bin/bash
 #SBATCH -J {job_name}
 #SBATCH -o {job_name}.out
 #SBATCH -e {job_name}.err
-#SBATCH -n {ncpu}
+#SBATCH -n 1
+#SBATCH -c {ncpu}
 #SBATCH -t {wall_time}
 
 printf "******************\\nStarting {job_name} at `uptime`\\n"

### 2020-04-01 run_minority_experiment.py

@@ -4,7 +4,7 @@ import sys
 import os
 
 # XXX Change this to change the minority fraction.
-minority_trait_frac = 0.1
+minority_trait_frac = 0.05
 
 data_dir = 'output_data'
 

### 2020-04-01 sub_invasion_experiments_cluster.sh

@@ -7,68 +7,68 @@
 #     --initial_prop_covert=0.95 --initial_prop_churlish=0.95 \
 #     -qfast.q -j$fname -n200 -t"01:00:00"
 
-printf "\nRunning .95, .95\n"
-fname=output_data/invasion/disliking/part-`uuidgen`
-subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
-    --initial_prop_covert=0.95 --initial_prop_churlish=0.95 \
-    -qfast.q -j$fname -n200 -t"04:00:00"
-    # -qfast.q -j$fname -n200 -t"04:00:00"
+# printf "\nRunning .95, .95\n"
+# fname=output_data/invasion/disliking/part-`uuidgen`
+# subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
+#     --initial_prop_covert=0.95 --initial_prop_churlish=0.95 \
+#     -qfast.q -j$fname -n200 -t"04:00:00"
+#     # -qfast.q -j$fname -n200 -t"04:00:00"
 
 
-printf "\nRunning .5, .95\n"
-fname=output_data/invasion/disliking/part-`uuidgen`
-subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
-    --initial_prop_covert=0.5 --initial_prop_churlish=0.95 \
-    -qfast.q -j$fname -n200 -t"04:00:00"
+# printf "\nRunning .5, .95\n"
+# fname=output_data/invasion/disliking/part-`uuidgen`
+# subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
+#     --initial_prop_covert=0.5 --initial_prop_churlish=0.95 \
+#     -qfast.q -j$fname -n200 -t"04:00:00"
 
 
-printf "\nRunning .05, .95\n"
-fname=output_data/invasion/disliking/part-`uuidgen`
-subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
-    --initial_prop_covert=0.05 --initial_prop_churlish=0.95 \
-    -qfast.q -j$fname -n200 -t"04:00:00"
+# printf "\nRunning .05, .95\n"
[…]

### 2020-04-09 id_signaling/figures.py
closing in on finalizing basic, minority, and invasion experiment analyses

@@ -1,5 +1,7 @@
 import matplotlib.pyplot as plt
 import numpy as np
+import os
+import pandas as pd
 import seaborn as sns
 
 
@@ -9,6 +11,7 @@ def plot_evolution(df, experiment='receptivity',
                    homophily_vals=[0.1, 0.25, 0.4],
                    minority_subset=None,
                    savefig_path=None,
+                   ax=None,
                    **plot_kwargs):
     '''
     Arguments:
@@ -72,7 +75,7 @@ def plot_evolution(df, experiment='receptivity',
     gb_mean = df.groupby([exp_col, 'homophily', 'timestep'])[data_col].mean()
     means = gb_mean.unstack(level=(0, 1))
 
-    means.plot(lw=4, alpha=0.75, **plot_kwargs)
+    ax = means.plot(lw=4, alpha=0.75, ax=ax, **plot_kwargs)
 
     # Put legend outside of plot with label determined by experiment type.
     plt.legend(bbox_to_anchor=(1.01, 0.9), loc='upper left', ncol=1, title=exp_inset,
@@ -87,10 +90,57 @@ def plot_evolution(df, experiment='receptivity',
     if savefig_path is not None:
         plt.savefig(savefig_path)
 
+    return ax
+
+
+def plot_coevolution(df, experiment, exp_param_vals, homophily_vals,
+                     colors=['black', 'mediumorchid', 'dodgerblue'],
+                     savefig_path=None, ax=None,
+                     figsize=(7.5, 4), **plot_kwargs):
+
+    # Plot N lines for given exp_param_vals and homophily_vals
+    # representing evolution of signaling strategy in terms of
+    # density of covert signalers.
+    ax = plot_evolution(df, experiment=experiment,
+                        exp_param_vals=exp_param_vals,
+                        homophily_vals=homophily_vals,
+                        figsize=figsize, color=colors, ax=ax)
+
+    # Plot N lines for given exp_param_vals and homophily_vals
+    # representing evolution of receiving strategy in terms of
+    # density of covert signalers.
+    plot_evolution(df, experiment=experiment,
+                   exp_param_vals=exp_param_vals,
+                   strategy='receiving',
+                   homophily_vals=homophily_vals, ls='--',
+                   figsize=figsize, color=colors, ax=ax)
+
+    plt.title('Coevolution of sending\nand receiving strategies')
+
[…]

### 2020-04-11 id_signaling/figures.py
first rough draft/outline of pub-ready results

@@ -337,20 +337,24 @@ def load_minority_dfs(directory='data/minority',
     ]
 
 
-def covert_vs_minority_frac(minority_dfs, dislikings, homophily, ax=None):
+def covert_vs_minority_frac(minority_dfs, dislikings, homophily,
+                            ax=None, savefig_path=None):
 
     if ax is None:
         fig, ax = plt.subplots(figsize=(5, 4))
-
+    minority_dfs = minority_dfs[1:]  # Excluding 0.05 case.
     minority_frac_strs = [el[0] for el in minority_dfs]
 
-    print(minority_frac_strs)
-
-    styles = ['-', '--', ':']
+    line_styles = ['-', '--', ':']
+    marker_styles = ['^', 'o', 's']
 
     for d_idx, disliking in enumerate(dislikings):
 
         means_over_minority_frac = []
+        means_over_majority_frac = []
+        minmaj_covert_mean_diff = []
+        minmaj_covert_std_diff = []
+
         std_over_minority_frac = []
 
         for minority_frac_str, df in minority_dfs:
@@ -361,36 +365,71 @@ def covert_vs_minority_frac(minority_dfs, dislikings, homophily, ax=None):
                 (df.homophily == homophily)
             ]
 
-            # print(len(pre))
+            pre['min_maj_cov_diff'] = \
+               pre.prop_covert_minority - pre.prop_covert_majority
+            # print(pre['min_maj_cov_ratio'])
+            # print(pre.min_maj_cov_ratio.mean())
+            minmaj_covert_mean_diff.append(pre.min_maj_cov_diff.mean())
 
-            mean_final_cov_prop = pre.prop_covert_minority.mean()
-            std_final_cov_prop = pre.prop_covert_minority.std()
+            std_final_cov_prop = pre.min_maj_cov_diff.std()
+            minmaj_covert_std_diff.append(std_final_cov_prop)
 
-            means_over_minority_frac.append(mean_final_cov_prop)
-            std_over_minority_frac.append(std_final_cov_prop)
+            # minmaj_covert_std_diff = pre.prop_covert_minority.std()
 
+            # means_over_minority_frac.append(mean_min_cov_prop)
+            # means_over_majority_frac.append(mean_maj_cov_prop)
+            # std_over_minority_frac.append(std_final_cov_prop)
+
+        # majmin_covert_ratio = [min_ / maj_ for min_, maj_ in
+        #                        zip(means_over_minority_frac, means_over_majority_frac)]
[…]

### 2020-04-13 id_signaling/scripts/runner.py
including submission scripts

@@ -101,7 +101,9 @@ f'''#! /bin/bash
 printf "******************\\nStarting {job_name} at `uptime`\\n"
 
 runexp {experiment} {param_vals} {homophily_vals} {n_iter} {n_trials} \\
-    {output_file} -R{prob_overt_receiving} -m{minority_trait_frac}
+    {output_file} -R{prob_overt_receiving} -m{minority_trait_frac} \\
+    --initial_prop_covert={initial_prop_covert} \\
+    --initial_prop_churlish={initial_prop_churlish}
 
 printf "******************\\nFinished at `uptime`"
 '''

### 2020-04-13 sub_invasion_experiments_cluster.sh

@@ -1,138 +1,131 @@
 # An executable bit of documentation of how to run all the experiments used
 # for the computational modeling publication.
 
-# printf "\nRunning .95, .95\n"
-# fname=output_data/invasion/disliking/part-`uuidgen`
-# subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 50 20 $fname.csv -R0.5  \
-#     --initial_prop_covert=0.95 --initial_prop_churlish=0.95 \
-#     -qfast.q -j$fname -n200 -t"01:00:00"
-
-# printf "\nRunning .95, .95\n"
-# fname=output_data/invasion/disliking/part-`uuidgen`
-# subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
-#     --initial_prop_covert=0.95 --initial_prop_churlish=0.95 \
-#     -qfast.q -j$fname -n200 -t"04:00:00"
-#     # -qfast.q -j$fname -n200 -t"04:00:00"
+printf "\nRunning .95, .95\n"
+fname=output_data/invasion/disliking/part-`uuidgen`
+subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
+    --initial_prop_covert=0.95 --initial_prop_churlish=0.95 \
+    -qfast.q -j$fname -n24 -t"02:00:00"
 
 
-# printf "\nRunning .5, .95\n"
-# fname=output_data/invasion/disliking/part-`uuidgen`
-# subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
-#     --initial_prop_covert=0.5 --initial_prop_churlish=0.95 \
-#     -qfast.q -j$fname -n200 -t"04:00:00"
+printf "\nRunning .5, .95\n"
+fname=output_data/invasion/disliking/part-`uuidgen`
+subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
+    --initial_prop_covert=0.5 --initial_prop_churlish=0.95 \
+    -qfast.q -j$fname -n24 -t"02:00:00"
 
 
-# printf "\nRunning .05, .95\n"
-# fname=output_data/invasion/disliking/part-`uuidgen`
[…]

### 2020-04-13 id_signaling/figures.py
final draft of figures roll before developing pub-ready

@@ -177,13 +177,14 @@ def heatmap(df, experiment='disliking', strategy='signaling',
     final_means = means[means.index == means.index[-1]]
     # final_means = means[means.timestep == means.timestep.max()]
     # print(final_means.stack().max())
-    print(final_means.stack())
-    print(final_means.head())
+    # print(final_means.stack())
+    # print(final_means.head())
 
 
     plt.figure(figsize=figsize)
 
     ax = sns.heatmap(final_means.stack(), cmap=cmap, square=True,
+                     vmin=0.0, vmax=1.0,
                      # cbar_kws={'label': f'Density of {strategy_inset.lower()}'},
                      **heatmap_kwargs
                     )
@@ -206,14 +207,14 @@ def heatmap(df, experiment='disliking', strategy='signaling',
 
     if experiment == 'receptivity':
         relative_receptivity = np.sort(df.receptivity.unique() / 0.5)
-        ax.set_xticklabels([f'{x:.1f}' for x in relative_receptivity], rotation=0)
+        ax.set_xticklabels([f'{x:.1f}' for x in relative_receptivity], rotation=30)
     else:
-        ax.set_xticklabels([f'{x:.1f}'
+        ax.set_xticklabels([f'{x:.2f}'
                             for x in np.sort(df.disliking.unique())], rotation=30)
 
     # ax.set_yticklabels([f'{y:.2f}' for y in np.arange(0.1, 0.46, 0.05)] + ['0.49', '0.50']);
 
-    ax.set_yticklabels([f'{y:.1f}' for y in np.sort(df['homophily'].unique())])
+    ax.set_yticklabels([f'{y:.2f}' for y in np.sort(df['homophily'].unique())])
 
     if title is not None:
         ax.set_title(title, size=14)
@@ -338,11 +339,15 @@ def load_minority_dfs(directory='data/minority',
 
 
 def covert_vs_minority_frac(minority_dfs, dislikings, homophily,
+                            exclude_p05=True,  # Exclude data point by default.
                             ax=None, savefig_path=None):
+
+    if exclude_p05:
+        minority_dfs = minority_dfs[1:]  # For excluding 0.05 case.
 
     if ax is None:
         fig, ax = plt.subplots(figsize=(5, 4))
-    minority_dfs = minority_dfs[1:]  # Excluding 0.05 case.
+
     minority_frac_strs = [el[0] for el in minority_dfs]
 
     line_styles = ['-', '--', ':']

### 2020-04-16 id_signaling/figures.py
fixed number of invading agents issue to not be random, but exact if N*init_prop is integer

@@ -447,7 +447,6 @@ def invasion_heatmaps(disliking_df, recept_df,
                       base_filename='reports/Figures/invasion',
                       figsize=(8, 5),
                       save_path=None):
-        #, center='dark'),
     '''
     Plot 3x2 heatmaps in subplots. 3-element rows are each for one of the
     two experiments, with disliking penalty or covert receptivity on the
@@ -462,6 +461,7 @@ def invasion_heatmaps(disliking_df, recept_df,
     fig, axes = plt.subplots(2, 3, sharex=True, figsize=figsize)
 
     # Step 1: do this for covert invading and generalize from there.
+    rate_dfs = []
     if invading in ('overt', 'covert'):
 
         if invading == 'covert':
@@ -473,8 +473,11 @@ def invasion_heatmaps(disliking_df, recept_df,
 
         # final_dis = disliking_df[disliking_df.timestep == timesteps]
         # final_rec = recept_df[recept_df.timestep == timesteps]
-        for exp_idx, name_df in enumerate([("Disliking penalty", disliking_df),
-                                            ("Relative\ncovert receptivity", recept_df)]):
+        for exp_idx, name_df in enumerate(
+                            [("Disliking penalty", disliking_df),
+                             ("Relative\ncovert receptivity", recept_df)]
+                        ):
+
             for chur_idx, init_chur in enumerate(init_churs):
 
                 name = name_df[0]
@@ -484,9 +487,10 @@ def invasion_heatmaps(disliking_df, recept_df,
                 df_lim = df[(df.initial_prop_covert == init_cov) &
                             (df.initial_prop_churlish == init_chur)]
 
-                _one_invasion_heatmap(axes, name, df_lim, invading, init_cov,
-                                      init_chur, exp_idx, chur_idx, timesteps,
-                                      cmap)
+                rate_df = _one_invasion_heatmap(
+                    axes, name, df_lim, invading, init_cov, init_chur, exp_idx,
+                    chur_idx, timesteps, cmap)
+                rate_dfs.append(rate_df)
 
     elif invading in ('churlish', 'generous'):
 
@@ -497,8 +501,11 @@ def invasion_heatmaps(disliking_df, recept_df,
 
         init_covs = [0.05, 0.5, 0.95]
 
-        for exp_idx, name_df in enumerate([("Disliking penalty", disliking_df),
[…]

### 2020-04-16 id_signaling/model.py

@@ -56,7 +56,6 @@ class Model:
                 so that probability of switching is ~1/50 when
                 relative payoff is 0.9 and ~3/50 when relative payoff is 1.0.
         '''
-
         self.N = N
         self.n_rounds = n_rounds
         self.K = K
@@ -78,19 +77,29 @@ class Model:
         if random_seed is not None:
             np.random.seed(random_seed)
 
-        choose_rec = lambda : \
-            choice(['Churlish', 'Generous'],
-                   p=[initial_prop_churlish, 1 - initial_prop_churlish])
+        n_initial_churlish = int(N * initial_prop_churlish)
+        n_initial_generous = N - n_initial_churlish
+        n_initial_covert = int(N * initial_prop_covert)
+        n_initial_overt = N - n_initial_covert
 
-        choose_sig = lambda : \
-            choice(['Covert', 'Overt'],
-                   p=[initial_prop_covert, 1 - initial_prop_covert])
+        rec_strategies = (
+            ['Churlish'] * n_initial_churlish +
+            ['Generous'] * n_initial_generous
+        )
+        np.random.shuffle(rec_strategies)
+
+        sig_strategies = (
+            ['Covert'] * n_initial_covert +
+            ['Overt'] * n_initial_overt
+        )
+        np.random.shuffle(sig_strategies)
 
         self.agents = [
+
             Agent(idx, K=K, N=N,
-                  receiving_strategy=choose_rec(),
-                  signaling_strategy=choose_sig()
-                 )
+                  receiving_strategy=rec_strategies[idx],
+                  signaling_strategy=sig_strategies[idx])
+
             for idx in range(N)
         ]
 
@@ -107,8 +116,8 @@ class Model:
 
             # Select minority agents.
             self.minority_agents = list(choice(self.agents,
-                                         size=int(N*minority_trait_frac),
-                                         replace=False))
+                                        size=int(N*minority_trait_frac),
+                                        replace=False))
 
             # Majority agents are the ones unselected for minority.
             self.majority_agents = list(

### 2020-04-23 id_signaling/figures.py
updated similarity threshold for general use and the number of traits that minority/majority share out of K

@@ -355,23 +355,23 @@ def covert_vs_minority_frac(minority_dfs, dislikings, homophily,
 
     for d_idx, disliking in enumerate(dislikings):
 
-        means_over_minority_frac = []
-        means_over_majority_frac = []
+        # means_over_minority_frac = []
+        # means_over_majority_frac = []
         minmaj_covert_mean_diff = []
         minmaj_covert_std_diff = []
 
-        std_over_minority_frac = []
+        # std_over_minority_frac = []
 
         for minority_frac_str, df in minority_dfs:
             # First extract all N_trials final covert signaling proportions.
-            pre = mean_final_cov_prop = df[
+            pre = df[
                 (df.timestep == 500) &
                 (df.disliking == disliking) &
                 (df.homophily == homophily)
             ]
 
             pre['min_maj_cov_diff'] = \
-               pre.prop_covert_minority - pre.prop_covert_majority
+                pre.prop_covert_minority - pre.prop_covert_majority
             # print(pre['min_maj_cov_ratio'])
             # print(pre.min_maj_cov_ratio.mean())
             minmaj_covert_mean_diff.append(pre.min_maj_cov_diff.mean())
@@ -398,7 +398,6 @@ def covert_vs_minority_frac(minority_dfs, dislikings, homophily,
         #         label=f'$d=\\delta={disliking:.2f}$')
         # ax.plot(minmaj_covert_mean_ratio, color='black', ls=line_styles[d_idx],
         #         label=f'$d=\\delta={disliking:.2f}$')
-
 
         ax.plot(minmaj_covert_mean_diff, color='black', ls=line_styles[d_idx],
                 marker=marker_styles[d_idx], mfc='white', mec='black', mew=1,

### 2020-04-23 id_signaling/model.py

@@ -6,9 +6,9 @@ Date: 2020-02-25
 '''
 import numpy as np
 
-from copy import deepcopy
 from numpy.random import choice, uniform
 from scipy.special import expit
+from scipy.spatial.distance import hamming
 
 
 RECEIVING_STRATEGIES = ["Generous", "Churlish"]
@@ -20,9 +20,10 @@ class Model:
     def __init__(self, N=100, n_rounds=10, K=3, prob_overt_receiving=0.75,
                  prob_covert_receiving=0.25, similarity_benefit=0.25,
                  one_dislike_penalty=0.25, two_dislike_penalty=0.25,
-                 homophily=0.25, random_seed=None, similarity_threshold=1,
+                 homophily=0.25, random_seed=None, similarity_threshold=0.5,
                  minority_trait_frac=None,
                  initial_prop_covert=0.5, initial_prop_churlish=0.5,
+                 n_minmaj_traits=1,  # only used if minority_trait_frac ! None
                  evo_logistic_loc=1.25, evo_logistic_scale=12):
         '''
         Arguments:
@@ -126,9 +127,9 @@ class Model:
 
             # Set traits.
             for agent in self.minority_agents:
-                agent.traits[0] = 1
+                agent.traits[0:n_minmaj_traits] = 1
             for agent in self.majority_agents:
-                agent.traits[0] = -1
+                agent.traits[0:n_minmaj_traits] = -1
 
             self.prop_covert_series_minority = np.array(
                 [_proportion_covert(self, subset='minority')]
@@ -360,7 +361,11 @@ class Model:
 
         att_sum = a1.attitudes[a2.index] + a2.attitudes[a1.index]
 
-        similar = (np.sum(a1.traits * a2.traits) >= self.similarity_threshold)
+        # XXX OLD
+        # similar = (np.sum(a1.traits * a2.traits) >= self.similarity_threshold)
+
+        similarity = 1 - hamming(a1.traits, a2.traits)
+        similar = similarity >= self.similarity_threshold
 
         # Like/like.
         if att_sum == 2:
@@ -480,6 +485,7 @@ def _proportion_churlish(model, subset=None):
         )
     else:
         print(f'{subset} not recognized')
+
 
 class Agent:
 

### 2020-04-23 id_signaling/scripts/runner.py

@@ -7,12 +7,6 @@ from subprocess import PIPE
 from id_signaling.experiment import run_experiments
 
 
-# @click.group()
-# @click.pass_context
-# def run(ctx):
-#     "Run a series of given experiment trials"
-#     ctx.obj = dict()
-
 def composed(*decs):
     """Compose a series of decorators, which will be handy here."""
     def deco(f):
@@ -25,25 +19,31 @@ def composed(*decs):
 def basic_decorator():
 
     return composed(
-        click.command(),
-        click.argument('experiment', type=str),
-        click.argument('param_vals', type=str),
-        click.argument('homophily_vals', type=str),
-        click.argument('n_iter', type=int),
-        click.argument('n_trials', type=int),
-        click.argument('output_file'),
-        click.option('--prob_overt_receiving', '-R',
-                     type=float, default=0.5),
-        click.option('--minority_trait_frac', '-m'),
-        click.option('--initial_prop_covert', type=float, default=0.5),
-        click.option('--initial_prop_churlish', type=float, default=0.5),
-   )
+            click.command(),
+            click.argument('experiment', type=str),
+            click.argument('param_vals', type=str),
+            click.argument('homophily_vals', type=str),
+            click.argument('n_iter', type=int),
+            click.argument('n_trials', type=int),
+            click.argument('output_file'),
+            click.option('--prob_overt_receiving', '-R',
+                         type=float, default=0.5),
+            click.option('--minority_trait_frac', '-m'),
+            click.option('--initial_prop_covert', type=float, default=0.5),
+            click.option('--initial_prop_churlish', type=float, default=0.5),
+            click.option('--num_traits', '-K', type=float, default=3),
+            click.option('--similarity_threshold', '-S', type=float,
+                         default=0.5),
+            click.option('--n_minmaj_traits', type=float, default=1)
+       )
+
 
 ## RUNEXP ##
 @basic_decorator()
 def run(experiment, param_vals, homophily_vals, n_iter, n_trials,
         output_file, prob_overt_receiving, minority_trait_frac,
-        initial_prop_covert, initial_prop_churlish):
+        initial_prop_covert, initial_prop_churlish, num_traits,
+        similarity_threshold, n_minmaj_traits):
 
     # XXX Hack to deal with subexp throwing error I don't understand that
     # minority_trait_frac can't be None (the default) because it's not a
[…]

### 2020-04-23 sub_similarity_experiments.sh

@@ -1,0 +1,26 @@
+# * Set up simulations where agents are characterized by 10 
+#     binary traits (instead of 3). 
+# * Run simulations where "similarity" is defined as having at least X traits 
+#     in common, where X = {1, 2, 3, 4, ..., 10}. We should find here 
+#     that when X increases, we get more covert signaling. 
+# * Run new majority-minority dynamics using a threshold of 50% similar. Set 
+#     minority to be 10% of the population, where the first 4 traits are set to 
+#     zero, and one for the majority (so that minority individuals really need 
+#     to find each other). This will be a good confirmation of the trend we see 
+#     with 3 traits. 
+# * You can run all these with just one value of r/R and maybe 3 values of d.
+
+
+# Experiment 1: 
+
+for similarity_threshold in 0.{1..9} 1.0; do
+
+    fname=output_data/minority-similarity/$similarity_threshold/part-`uuidgen`
+    echo subexp disliking 0.05:0.46:0.2 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
+        -qfast.q -j$fname -n24 -t"04:00:00" -S$similarity_threshold -K10
+
+done
+
+
+echo subexp disliking 0.05:0.46:0.2 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
+    -qfast.q -j$fname -n24 -t"04:00:00" --n_minmaj_traits=4 -K10

### 2020-04-25 id_signaling/figures.py
starting analysis and bugfixes for similarity experiment

@@ -436,6 +436,38 @@ def covert_vs_minority_frac(minority_dfs, dislikings, homophily,
             plt.savefig(savefig_path)
 
 
+def similarity_threshold(dfs, thresholds=np.arange(0.1, 1.1, 0.1),
+                         dislikings=[0.05, 0.25, 0.45], homophily=0.2,
+                         ax=None, savefig_path=None):
+
+    if ax is None:
+        fig, ax = plt.subplots(figsize=(5, 4))
+
+    line_styles = ['-', '--', ':']
+    marker_styles = ['^', 'o', 's']
+
+    for d_idx, disliking in enumerate(dislikings):
+
+        mean_covert_prevalence = []
+
+        for df_idx, df in enumerate(dfs):
+
+            mean_covert_prevalence.append(
+                df[
+                    (df.timestep == 500) &
+                    (df.disliking == disliking) &
+                    (df.homophily == homophily)
+                ].prop_covert.mean()
+            )
+
+        ax.plot(mean_covert_prevalence, color='black', ls=line_styles[d_idx],
+                marker=marker_styles[d_idx], mfc='white', mec='black', mew=1,
+                label=f'$d=\\delta={disliking:.2f}$')
+
+    ax.legend()
+    ax.set_title(f'$w={homophily:.1f}$')
+
+
 def invasion_heatmaps(disliking_df, recept_df,
                       cmap=sns.cubehelix_palette(
                           50, hue=0.05, rot=0, light=0.0,

### 2020-04-25 id_signaling/scripts/runner.py

@@ -107,8 +107,10 @@ printf "******************\\nStarting {job_name} at `uptime`\\n"
 
 runexp {experiment} {param_vals} {homophily_vals} {n_iter} {n_trials} \\
     {output_file} -R{prob_overt_receiving} -m{minority_trait_frac} \\
+    -K{num_traits} -S{similarity_threshold} \\
     --initial_prop_covert={initial_prop_covert} \\
     --initial_prop_churlish={initial_prop_churlish}
+
 
 printf "******************\\nFinished at `uptime`"
 '''
@@ -117,4 +119,5 @@ printf "******************\\nFinished at `uptime`"
         print(subscript)
 
     else:
-        subprocess.run(['sbatch'], stdout=PIPE, input=bytearray(subscript, 'utf-8'))
+        subprocess.run(['sbatch'], stdout=PIPE,
+                       input=bytearray(subscript, 'utf-8'))

### 2020-04-25 id_signaling/figures.py
cov sig versus similarity first pass

@@ -438,7 +438,8 @@ def covert_vs_minority_frac(minority_dfs, dislikings, homophily,
 
 def similarity_threshold(dfs, thresholds=np.arange(0.1, 1.1, 0.1),
                          dislikings=[0.05, 0.25, 0.45], homophily=0.2,
-                         ax=None, savefig_path=None):
+                         ax=None, savefig_path=None, ylow=0.2, yhigh=1.0,
+                         legend=False, xlabel=True, ylabel=True):
 
     if ax is None:
         fig, ax = plt.subplots(figsize=(5, 4))
@@ -456,7 +457,7 @@ def similarity_threshold(dfs, thresholds=np.arange(0.1, 1.1, 0.1),
                 df[
                     (df.timestep == 500) &
                     (df.disliking == disliking) &
-                    (df.homophily == homophily)
+                    (np.isclose(df.homophily, homophily))
                 ].prop_covert.mean()
             )
 
@@ -464,8 +465,22 @@ def similarity_threshold(dfs, thresholds=np.arange(0.1, 1.1, 0.1),
                 marker=marker_styles[d_idx], mfc='white', mec='black', mew=1,
                 label=f'$d=\\delta={disliking:.2f}$')
 
-    ax.legend()
+    if legend:
+        ax.legend()
+
     ax.set_title(f'$w={homophily:.1f}$')
+
+    ax.set_ylim(ylow, yhigh)
+    ax.grid(axis='y')
+
+    if xlabel:
+        ax.set_xlabel('Similarity threshold, $S$', size=14)
+    if ylabel:
+        ax.set_ylabel('Covert prev., $\\rho_{cov,t=T}$', size=14)
+
+    ax.set_xticks(range(1, 10, 2))
+    ax.set_xticklabels([f'{threshold:1.1f}' for threshold in thresholds[1::2]])
+    # ax.set_yticks(np.arange(0.2, 1.1, 0.1))
 
 
 def invasion_heatmaps(disliking_df, recept_df,

### 2020-04-28 reports/minority-supplement-figures.tex
made minority diff heatmap for K=10, M=4; added to results.tex

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.315\textwidth}
    \includegraphics[width=\textwidth]{Figures/full-minority-homophily=0p00.pdf}
  \end{subfigure}
  \begin{subfigure}{0.315\textwidth}
    \includegraphics[width=\textwidth]{Figures/full-minority-homophily=0p05.pdf}
  \end{subfigure}
  \begin{subfigure}{0.315\textwidth}
    \includegraphics[width=\textwidth]{Figures/full-minority-homophily=0p10.pdf}
  \end{subfigure} \\
  \begin{subfigure}{0.315\textwidth}
    \includegraphics[width=\textwidth]{Figures/full-minority-homophily=0p15.pdf}
  \end{subfigure}
  \begin{subfigure}{0.315\textwidth}
    \includegraphics[width=\textwidth]{Figures/full-minority-homophily=0p20.pdf}
  \end{subfigure}
  \begin{subfigure}{0.315\textwidth}
    \includegraphics[width=\textwidth]{Figures/full-minority-homophily=0p25.pdf}
  \end{subfigure}
  \\
  \begin{subfigure}{0.315\textwidth}
    \includegraphics[width=\textwidth]{Figures/full-minority-homophily=0p30.pdf}
  \end{subfigure}
  \begin{subfigure}{0.315\textwidth}
    \includegraphics[width=\textwidth]{Figures/full-minority-homophily=0p35.pdf}
  \end{subfigure}
  \begin{subfigure}{0.315\textwidth}
    \includegraphics[width=\textwidth]{Figures/full-minority-homophily=0p40.pdf}
  \end{subfigure} \\
  \begin{subfigure}{0.49\textwidth}
    \includegraphics[width=0.7\textwidth]{Figures/full-minority-homophily=0p45.pdf}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \includegraphics[width=0.7\textwidth]{Figures/full-minority-homophily=0p50.pdf}
  \end{subfigure}
  \caption{}
  \label{fig:}
\end{figure}

### 2020-04-28 id_signaling/figures.py

@@ -222,7 +222,8 @@ def heatmap(df, experiment='disliking', strategy='signaling',
         plt.savefig(savefig_path)
 
 def minority_diff_heatmap(df, strategy='signaling', savefig_path=None,
-                          figsize=(6.35, 4.75), vmin=None, vmax=None):
+                          figsize=(6.35, 4.75), vmin=None, vmax=None,
+                          title=None):
 
     if strategy == 'signaling':
         strategy_inset = 'Covert signalers'
@@ -236,10 +237,12 @@ def minority_diff_heatmap(df, strategy='signaling', savefig_path=None,
     data_col_min = data_col + '_minority'
     data_col_maj = data_col + '_majority'
 
-    gb_minority_mean = df.groupby(['disliking', 'homophily', 'timestep'])[data_col_min].mean()
+    pre = df[df.timestep == df.timestep.max()]
+
+    gb_minority_mean = pre.groupby(['disliking', 'homophily', 'timestep'])[data_col_min].mean()
     minority_means = gb_minority_mean.unstack(level=(0, 1))
 
-    gb_majority_mean = df.groupby(['disliking', 'homophily', 'timestep'])[data_col_maj].mean()
+    gb_majority_mean = pre.groupby(['disliking', 'homophily', 'timestep'])[data_col_maj].mean()
     majority_means = gb_majority_mean.unstack(level=(0, 1))
 
     final_min_means = minority_means[minority_means.index == minority_means.index[-1]]
@@ -253,13 +256,15 @@ def minority_diff_heatmap(df, strategy='signaling', savefig_path=None,
         cmap=sns.diverging_palette(10, 220, sep=80, n=10), #, center='dark'),
         cbar_kws={
             'label':
-                f'Difference in density\n'
-                f'of {strategy_inset.lower()}\n'
-                f'Minority - Majority',
-            'ticks':
-                np.arange(-0.2, 0.31, 0.1),
+                f'Difference in {strategy_inset.lower()}\n'
+                f'prevalence (minority - majority)\n'
+                # f'Minority - Majority',
+            # 'ticks':
+            #     np.arange(-0.2, 0.31, 0.1),
         }
     )
+
+    ax.set_title(title)
 
     # Set size of colorbar title.
[…]

### 2020-05-22 paper/ms.tex
start of model and results writing for paper; new red tests for minority, invasion, similarity threshold

\documentclass[11pt,letterpaper]{article}
% \documentclass[11pt]{report}
% \documentclass{report}
% \documentclass{book}
\usepackage[bookmarks]{hyperref}
\usepackage{amssymb,amsmath}
% \usepackage{fullpage}
\usepackage{tabulary}
\usepackage{tabularx}
\usepackage{float}
% \usepackage[margin=1.00in]{geometry}
\usepackage[margin=0.90in]{geometry}

\usepackage{caption}
\usepackage{booktabs}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{wrapfig}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage{setspace}
\doublespace
% \usepackage{url}
\usepackage{bigfoot}
\usepackage[export]{adjustbox}
\setlength\intextsep{0pt}

\usepackage{graphicx}

\title{Model and results for identity signaling project}

\author{{Paul E.~Smaldino and Matthew A.~Turner}}

\begin{document}
\maketitle

\section{Introduction}

When we interact with others it is often to mutually benefit from the
exchange. For instance, we shop at a store to buy things we want from one or
a group of people who want to do the hard work of shopkeeping. When we are
dissimilar from those with whom we interact, the benefit can be lessened.
For instance, you might be wearing a shirt with a political slogan and 
the shopkeeper has posted signs boasting their political affiliation. Perhaps
the shopkeeper decides to charge you more, or perhaps you feel a sense of 
resentment for giving money to someone with whom you disagree politically;
maybe the shopkeeper's signage distracted you from making all the purchases 
you needed to make. Shopping is rather inconsequential, but illustrates the issue. 
A much more critical situation is the interaction of political partisans, who
must mutually benefit one another for democracy to work.

In response to the fact that
interpersonal disliking often lowers payoffs from interaction, humans have
developed \emph{covert signaling} strategies so that, e.g.,
customer and shopkeeper can signal their political affiliations so that like-minded
people will know they are similar, but dissimilar others will be unaware
of political or identity signaling at all. Different social settings present
different signaling pressures. Sometimes it is possible to choose who we assort
with for interaction, which means the practice of homophily---selectively
interacting with similar others---is widespread. In that case, there is little
reason to signal covertly because we can preferentially 
interact with similar others, avoiding penalties for interaction with 
dissimilar others. Sometimes the penalties for
disliking one another are very high, which pressures individuals to choose
covert signaling more often in order to not be disliked. While there are
interaction costs for dislike there are benefits for the case where two, which are
also included in the model.

Here we present a model of identity signaling, social interaction,
and social learning to identify mechanisms for the evolution of the covert 
signaling strategy, as opposed to an overt signaling strategy. The precise 
definitions of overt and covert signaling are given in the Model section.
Our results are thus predictions of when covert signaling will or
will not evolve. This depends on a number of model parameters and the 
co-evolution of the \emph{receiving} strategy, which may be either \emph{generous}
or \emph{churlish}. Generous individuals do not dislike
others with whom they have not previously interacted. Churlish individuals 
dislike others with whom they have not previously interacted.

The model predicts that covert signaling evolves when homophily is low (agents
do not efficiently assort) and the costs of disliking are high. The model also 
predicts that covert signaling co-evolves with generous receiving. This is due
to the fact that covert signalers are simply ignored by those with whom
they are different. If most of the individuals are churlish receivers, there is
no benefit to being unknown since most individuals dislike unknown others. 
We also use our model to predict differences in covert signaling prevalence
among minority and majority populations, where the minority and majority all
share the same in-group traits along a number of trait dimensions, but exactly
the opposite traits. If homophily is weak and disliking costs are high, the
minority will tend to become covert signalers. However, if homophily is
sufficiently high it is better for the minority to overtly signal so they can
efficiently identify similar interaction partners. We close by finding the
conditions that promote either signaling or receiving strategies to ``invade'',
i.e.\ become prevalent after starting as just a small fraction of the population.
We find here that sometimes no signaling is better than overt signaling: 
covert signaling can evolve even when the efficiency of covert signaling is
zero, i.e.\ covert signals are not understood by any model individuals (agents).

\section{Model}

The model includes parameters to represent homophily, the penalty for 
individuals who dislike one another, the efficiency of covert signaling, and the
number of traits assumed to be important in social interaction for a model system.
These are summarized in Table~\ref{tab:params} below.

\vspace{1em}
\begin{table}[H]
  \centering
  \begin{tabular}{cl}
    Variable/parameter & Definition \\
    \toprule 
    $a_{ij}$   & Attitude of agent $i$ towards agent $j$; $a_i$ is the $N$-dimensional 
      attitude vector of agent $i$ \\
    $\tau_{ij}$ & Trait $j$ of agent $i$; $\tau_i$ is the $K$-dimensional trait vector of agent $i$ \\
    $K$      & Number of relevant traits determining similarity, liking, disliking, etc. \\
    $w$      & Homophily \\
    $d$      & Interaction penalty when one agent dislikes the other \\
    $\delta$ & Additional interaction penalty when both agents dislike each other \\
    $s$      & Added interaction benefit when agents are similar, as defined by their traits \\
    $S$      & Number of traits two agents must have in common to be considered similar \\
    $M$      & Number of traits used (if any) to define majority/minority populations \\
  \end{tabular}
  \caption{Model parameters.}
  \label{tab:params}
\end{table}

\subsection{Agents}

Model individuals are agents who 
\begin{enumerate}
  \item have static ``in-born'' traits that determine pairwise similarity or dissimilarity
  \item hold attitudes about all other agents in the system
  \item have adopted a signaling and receiving strategy
\end{enumerate}Signaling strategies
may be either \emph{covert} or \emph{overt}, and receiving strategies may be
either \emph{generous} or \emph{churlish}. Unless otherwise noted, agents are
randomly initialized to be covert or overt with equal probability. The 
proportion of agents with specific signaling or receiving strategies will be
set to different values in the invasion experiments, explained in more detail below.

Each trait is represented arbitrarily by $\tau_{ij} \in \{-1, 1\}$ 
(MAYBE USE 'A' and 'B' INSTEAD SINCE THEY REALLY ARE CATEGORICAL?). 
Attitudes are $a_{ij} \in \{-1, 0, 1\}$ with meanings of 
disliking, neutral, or liking.

\subsection{Signaling and receiving}

\subsection{Interaction and payoff}

\subsection{Social learning}

\subsection{Computational experiment design}

Homophily not only determines

% The model is

% \begin{figure}[htpb]
% \begin{center}
% \caption{Model flow chart with relevant equations.}
% \label{fig:yo}
% \begin{tikzpicture}[]
%   \node[draw] at (0, 0) {}; 
% \end{tikzpicture}
% \end{center}
% \end{figure}

\section{Results}

\subsection{Evolution of covert signaling...}

\subsubsection{...under various homophily and disliking scenarios}

\subsubsection{...as a function of covert signaling efficiency}

\subsubsection{Co-evolution of covert signaling and generous receiving}

\subsection{Minority-majority dynamics}

\subsection{Covert signaling invasion}

\subsection{Non-signaling as an adaptive strategy}

% \bibliographystyle{apacite}

% \setlength{\bibleftmargin}{.125in}
% \setlength{\bibindent}{-\bibleftmargin}

% \bibliography{/Users/mt/workspace/papers/library.bib}

\appendix

\section{Additional analyses}

\subsection{Temporal dynamics}

\subsection{Correlations between churlish receiving and covert signaling}

\subsection{$d \neq \delta$}

Vary $\delta$ from 0 to $2d$.

\subsection{Minority dynamics}

\subsubsection{More traits ($K=9$ and $M=4$) and different similarity threshold}

\subsubsection{Varying minority group size}

\subsection{Invasion of other strategies}

\end{document}

### 2020-05-22 id_signaling/model.py

@@ -48,6 +48,9 @@ class Model:
                 what fraction of agents should be ``minority'' agents with
                 first trait +1, and set first trait of majority to -1. If
                 None, do not set minority agents.
+            n_minmaj_traits (int): number of traits to use in assigning
+                minority and majority agents; short name is M in paper and
+                CLI.
             evo_logistic_loc (float): location where logistic function = 0.5
                 probability of switching strategies depending on relative
                 payoff. I.e. default is set so that 50% chance of switching

### 2020-05-22 test/test_model.py

@@ -1,9 +1,48 @@
 import numpy as np
-import pytest
 
 from numpy.testing import assert_array_equal, assert_approx_equal
 
 from id_signaling.model import Agent, Model
+
+
+def test_minorities():
+    'Check that minorities experiment is properly initialized and payoffs are as expected.'
+
+    _test_minorities(3, 1, 0.1)
+    _test_minorities(3, 1, 0.25)
+    _test_minorities(3, 1, 0.75)
+
+    _test_minorities(9, 4, 0.1)
+    _test_minorities(9, 4, 0.25)
+    _test_minorities(9, 4, 0.75)
+
+    assert False
+
+
+def _test_minorities(K, M, minority_trait_frac):
+
+    # Set up new model with given settings.
+    model = Model(N=100, K=K, n_minmaj_traits=M, minority_trait_frac=minority_trait_frac)
+
+    # assert False
+
+    # Test #0: do we really have the distribution of minority/majority we
+    # expect?
+
+    # Test #1: are payoffs as expected for minorities and majorities?
+    # Think I can follow my test_expected_payoff method below.
+
+    # Test #2 ???
+
+
+def test_similarity_threshold():
+    'Check that payoffs and matching probabilities are as expected for different similarity thresholds.'
+    assert False
+
+
+def test_invasion_setup():
+    'Check that there are correct number of invading and established populations.'
+    assert False
 
 
 ##
@@ -119,6 +158,7 @@ def test_calculate_payoff():
     a1.attitudes = np.array([-1, -1])
     assert model._calculate_payoff(a0, a1) == 1 - 0.25 - 0.15
 
+
 ##
 # Signaling and receiving. Need to ensure generous/churlish receivers act as
 # we expect them to depending on covert/overt signaling from either similar
@@ -180,6 +220,7 @@ def test_expected_payoffs():
     assert_approx_equal(model.agents[2].gross_payoff, pi2, 2)
     assert_approx_equal(model.agents[3].gross_payoff, pi3, 2)
 
+
 def _setup_model_agents(**model_kwargs):
 
     model = Model(N=4, **model_kwargs)
@@ -220,7 +261,6 @@ def _setup_model_agents(**model_kwargs):
 # Calculating dyadic interaction probabilities.
 #
 def test_dyadic_interaction_probs():
-# def test_dyadic_interaction_probs():
     '''
     Dyadic interaction probabilities should match expected values calculated
 

### 2020-05-22 paper/ms.tex
working through model description.

@@
 
+\begin{table}[H]
+  \begin{tabular}{ccp{5in}}
+    Agent property & 
+  \end{tabular}
+\end{table}
+
 Model individuals are agents who 
@@
 
-\subsection{Signaling and receiving}
+\subsection{Dynamics}
 
-\subsection{Interaction and payoff}
+Each model iteration consist of three stages. First, agents signal their identities
+to some fraction of all other agents. It is at this step that agent attitudes
+$a_{ij}$ are set. Whether or not an agent receives a signal depends on the
+efficiency of overt and covert signaling, $E_{ov}$ and $E_{cov}$, respectively.
+\emph{Efficiency} is the proportion of agents in the population that receive
+a given agent's signal depending on whether the agent is an overt or covert
+signaler.  Signals are sent and received once every model iteration. 
+If and agent does receive a signal
 
-\subsection{Social learning}
+Then agents then
+interact at most $N_I$ times with other agents. In each of the possible 
+$N_I$ interactions, agents first match with one agent selected randomly from
+the population. The probability these agents interact after matching depends
+on the homophily, $w$, and the attitudes each agent has for the other. 
+If a pair interacts, their payoff is determined by whether the agents are
+similar, whether one dislikes the other, and the penalty for disliking,
+$d$\footnote{(WILL INTRODUCE $\delta$ WITH A REFERENCE TO THE SI IN SUBSUBSEC
+BELOW)}. The distinction between similarity and disliking is subtle, 
+but necessary to include, as we explain in more detail below. After all
+$N_I$ interaction rounds, each agent chooses a teacher to potentially learn
+from. ``Learning'' is simply the adoption of either the signaling or
+receiving strategy of the teacher by the learner---which strategy type is 
+learned is chosen at random.
+
+After several hundred iterations the prevalence of each signaling and
+receiving strategy reaches an equilibrium (see SI dynamics plots).
+
+\subsubsection{Signaling and receiving}
+
+At the signaling and receiving step, agents form attitudes about one another if
+they receive a signal from
+
+\subsubsection{Interaction}
+
+The two agents interact with different probabilities
+depending on their attitudes about one another, and depending on the 
+assumed homophily level. If  Note that as $w \rightarrow 0.5$,
+agents never interact with agents they dislike and always interact with 
+agents they like.
+
+\begin{equation}
+  \Pr(\text{$i$ interacts with $j$}) = \frac{1 + a_{ij} + a_{ji}}{2}
+\end{equation}
+\noindent
+
+\subsubsection{Payoff}
+
+Payoffs are determined based on the similarity bonus, $s$, and the disliking
+penalty $d$\footnote{In the SI we consider the case where the disliking penalty 
+when both agents dislike each other is different from $d$. We call this $\delta$
+and let it vary from 0 to $2d$}.
+
+\begin{table}[h]
+  \centering
+  \begin{tabular}{cccc}
+    $a_{ij}$ & $a_{ji}$ & Similar? & Payoff $\pi_i = \pi_j$ \\
+    \toprule
+    1 & 1 & Yes & $1 + s$ \\
+    1 & 0 & Yes & $1 + s$ \\
+    1 & -1 & Yes & $1 + s - d$ \\
+    1 & -1 & No & $1 + s - d$ \\
+    0 & 0 & Yes & $1 + s$ \\
+    0 & 0 & No & $1$ \\
+    -1 & 0 & Yes & $1 + s - d$ \\
+    -1 & 0 & No  & $1 - d$ \\
+    -1 & -1 & Yes & $1 + s - 2d$ \\
+    -1 & -1 & No  & $1 - 2d$ \\
+  \end{tabular}
+  \caption{Interaction payoff matrix. Certain conditions are impossible, and so are not
+  shown. For instance, it is necessary for two agents to be similar for 
+  one agent to like another agent (i.e.\ have $a_{ij} = 1$). Note that
+  due to churlish receiving, two agents may be similar, but one dislikes the
+  other while the other likes the one. There could be agents who dislike one
+  another due to churlish receiving if they have never signaled each other.}
+\end{table}
+
+\subsubsection{Social learning}
+
+All agents select another agent in the population to be a teacher. The 
+learner agent probabilistically adopts its teacher's signaling or receiving 
+strategy---which type of strategy might be learned is determined by a coin flip. 
+The probability that the learner adopts the teacher's strategy is set 
+calculated by the logistic sigmoid function applied to the quotient of 
+teacher and learner payoffs accumulated in one signaling/receiving-interaction/payoff round.
+Let $\pi_{i}$ be the accumulated payoff of agent $i$, and assume $i$ learns
+from $j$. Set $p_{ij} = \pi_{j} / \pi_i$. 
+The probability the learner will adopt the teacher's strategy is
+
+\begin{equation}
+  \Pr(\text{$i$ learns from $j$}) = \frac{1}{1 + e^{-\beta(p_{ij} - \alpha)}}.
+\end{equation}
+\noindent
+$\alpha$ and $\beta$ are parameters shift and scale the sigmoid curve, respectively. 
+$\alpha$ is the size of $p_{ij}$ such that $\Pr(\text{$i$ learns from $j$}) = 0.5$. % $P(\text{$i$ learns from $j$}) = 0.5$.
+For example, if we set $\alpha = 2$, then the teacher's accumulated payoff
+must be twice that of the learner's for a 50\% chance that the learner 
+adopts the teacher's strategy. 
+For the main results we set $\alpha=1.25$. $\beta$ sets how quickly 
+$\Pr(\text{$i$ learns from $j$})$ increases overall. Larger $\beta$ means that
+if $p_{ij} < 0.5$ then $\Pr(\text{$i$ learns from $j$})$ is closer to 0 than smaller $\beta$. 
+$\Pr(\text{$i$ learns from $j$})$ is closer to 1 for larger than for smaller $\beta$. For the main
+results we set $\beta = 12$. These settings are rather arbitrary, (SO WE NEED
+TO PROVIDE SENSITIVITY CHECKS IN THE SUPPLEMENT).
 
@@
 
-Homophily not only determines
+\subsection{Outcome measures}
 
-% The model is
+We are primarily interested in the prevalence of covert signaling at time
+$t$. Usually, $t=T$, where $T$ is the number of iterations chosen for our 
+computational experiments. The prevalence of overt signalers is the complement 
+of the prevalence of covert signalers. One important result shows that the
+prevalence of covert signalers at $t=T$ is positively correlated with the
+prevalence of generous receivers at $t=T$.
 
-% \begin{figure}[htpb]
-% \begin{center}
-% \caption{Model flow chart with relevant equations.}
-% \label{fig:yo}
-% \begin{tikzpicture}[]
-%   \node[draw] at (0, 0) {}; 
-% \end{tikzpicture}
-% \end{center}
-% \end{figure}
+\begin{table}[H]
+  \centering
+  \begin{tabular}{rp{3in}} %p{5in}}
+    Symbol & Measure \\ %& Description \\
+    \toprule
+      $\rho_{cov}$ & Prevalence of covert signalers\\
+    $1 - \rho_{cov} = \rho_{ov}$ & Prevalence of overt signalers  \\
+     $\rho_{gen}$ & Prevalence of generous receivers \\
+    $1 - \rho_{gen} = \rho_{ch}$ & Prevalence of churlish receivers \\
+    $\rho_i^{minor}$, $\rho_i^{maj}$ & Prevalence of strategy $i \in \{cov, ov, gen, ch\}$ amongst minority/majority \\
+    $\Pr(\text{$i$ invades})$ & Probability strategy $i$ invades 
+  \end{tabular}
+  \caption{Summary of outcome measures. To indicate any of these values at
+  a particular time, we add an additional subscript. For example, $\rho_{cov,t}^{maj}$
+  is the prevalence of covert signalers among the majority at time $t$.}
+  \label{tab:outcomeMeasures}
+\end{table}
 
@@
 \subsubsection{Co-evolution of covert signaling and generous receiving}
+
+Theoretically, conditions favorable for covert
+signalers should also be favorable for generous receivers (TRUE??). Furthermore, 
+an increase in covert signalers increases the pressure towards generous receiving.
+With many covert signalers it is likely an agent will get no signal on a 
+turn because they were receiving a signal from a covert signaler. Disliking
+incurs a penalty, so it is better to remain neutral.
+
+Our computational results support this theoretical claim. As the heatmaps
+below reveal... In the SI we show regressions of $\rho_{cov,T} \sim \rho_{gen,T}$.
 
@@
 
+\section{Model implementation}
+
+In order to aid evaluation of our model code, we provide notes below on 
+our model implementation. The code is freely available on GitHub at
+\url{https://github.com/mt-digital/identity-signaling}.
+
 \end{document}

### 2020-05-22 id_signaling/model.py

@@ -380,7 +380,6 @@ class Model:
 
         # Neutral/neutral and like/dislike.
         elif att_sum == 0:
-            # Neutral/neutral.
             if similar:
                 # Like/dislike
                 if a1.attitudes[a2.index] > 0 or a2.attitudes[a1.index] > 0:
@@ -389,7 +388,7 @@ class Model:
                 elif a1.attitudes[a2.index] == 0 and a2.attitudes[a1.index] == 0:
                     return 1 + self.similarity_benefit
             else:
-                # Like/dislike
+                # Like/dislike XXX IS THIS EVEN POSSIBLE? smelly....
                 if a1.attitudes[a2.index] > 0 or a2.attitudes[a1.index] > 0:
                     return 1 - self.one_dislike_penalty
                 # Neutrals

### 2020-05-23 paper/ms.tex
outline and some sections drafted for Model section

@@
   \begin{tabular}{cl}
-    Variable/parameter & Definition \\
+    Global parameter & Description \\
     \toprule 
-    $a_{ij}$   & Attitude of agent $i$ towards agent $j$; $a_i$ is the $N$-dimensional 
-      attitude vector of agent $i$ \\
-    $\tau_{ij}$ & Trait $j$ of agent $i$; $\tau_i$ is the $K$-dimensional trait vector of agent $i$ \\
     $K$      & Number of relevant traits determining similarity, liking, disliking, etc. \\
@@
   \end{tabular}
-  \caption{Model parameters.}
+  \caption{Global model parameters.}
   \label{tab:params}
@@
 
-\begin{table}[H]
-  \begin{tabular}{ccp{5in}}
-    Agent property & 
-  \end{tabular}
-\end{table}
-
-Model individuals are agents who 
+Model individuals are \emph{agents} who 
 \begin{enumerate}
@@
 
-Each trait is represented arbitrarily by $\tau_{ij} \in \{-1, 1\}$ 
-(MAYBE USE 'A' and 'B' INSTEAD SINCE THEY REALLY ARE CATEGORICAL?). 
+Agents have $K$ traits, where $K$ is a parameter representing the cultural 
+complexity of the system. In the real world, different systems may have 
+different cultural complexities. For instance, in United States politics, there
+is increasingly little subtlety and increasing partisanship, so $K \approx1 $.
+However, if we were trying to understand scholarly positions on some research
+question, we may have $K$ be very large, or $K$ could be large if we consider
+agents to be, e.g., nations instead of people (as in Axelrod 1997).
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{cp{4.5in}}
+    Agent property & Description \\
+    \toprule
+    $a_{ij}$   & Attitude of agent $i$ towards agent $j$; $a_i$ is the $N$-dimensional 
+      attitude vector of agent $i$. \\
+    $\tau_{ik}$ & Trait $k$ of agent $i$; $\tau_i$ is the $K$-dimensional trait vector of agent $i$. \\
+    Signaling strategy & Either \emph{overt} or \emph{covert}. Overt signaling always
+                         results in the communication of the signaler's traits,
+                         while covert signalers only reveal their traits to 
+                         ``similar'' others; dissimilar others do not receive a covert signal. \\
+    Receiving strategy & Either \emph{churlish} or \emph{generous}. Churlish
+                         receivers default to dislike other agents from whom they have
+                         not received a signal. Generous receivers default to
+                         a neutral attitude towards others from whom they have
+                         not received a signal.
+  \end{tabular}
+  \caption{Agent attributes.}
+  \label{tab:agentAttributes}
+\end{table}
+
+\subsubsection{Determining inter-agent similarity}
+
+Each trait $j$ of agent $i$ takes a value $\tau_{ik} \in \{-1, 1\}$. $-1$ and 1
+are used only to emphasize that there are two opposing traits.
 Attitudes are $a_{ij} \in \{-1, 0, 1\}$ with meanings of 
-disliking, neutral, or liking.
+disliking, neutral, or liking. Attitudes are set at the signaling and receiving
+rounds, explained in more detail below. Briefly, if agent $i$ recieves a
+trait signal from agent $j$, $a_{ij}$ will be 1 if the two agents have
+similar traits, and $-1$ if $i$ and $j$ are sufficiently different. Similarity
+is $s_{ij} = 1 - d(\tau_i, \tau_j)$ where $d(\tau_i, \tau_j)$ is the
+Hamming distance between trait vectors. The Hamming distance is the fraction
+of vector elements that are different. So, if $\tau_i = (1,~-1,~1)$ and
+$\tau_j = (1,~-1,~-1)$, then $d(\tau_i, \tau_j) = 1/3$ and $s_{ij}=2/3$.
+Two agents are ``similar'' if their similarity $s_{ij} \geq S$, where
+$S$ is the similarity threshold parameter. Otherwise they are considered
+dissimilar.
+
+If two agents are similar, this enables agents to like one another. On the
+other hand, dissimilar agents may come to dislike one another if they signal
+their traits to one another. As explained further in the following section on
+model dynamics, inter-agent attitudes determine the probability agents will
+interact; the payoff received when a particular dyad interacts; and the
+probability that one agent chooses another as a teacher.
 
@@
 signaler.  Signals are sent and received once every model iteration. 
-If and agent does receive a signal
+If agent $i$ does receive a signal that agent updates its attitudes about
+signaler $j$, then $i$ updates its attitudes about $j$ ($a_{ij}$), according to
+the process outlined above.
 
@@
 \begin{equation}
-  \Pr(\text{$i$ interacts with $j$}) = \frac{1 + a_{ij} + a_{ji}}{2}
+  \Pr(\text{$i$ interacts with $j$}) = \frac{1 + w(a_{ij} + a_{ji})}{2}
 \end{equation}
@@
   \begin{tabular}{cccc}
-    $a_{ij}$ & $a_{ji}$ & Similar? & Payoff $\pi_i = \pi_j$ \\
+    Similar? & $a_{ij}$ & $a_{ji}$ & Payoff $\pi_i = \pi_j$ \\
     \toprule
-    1 & 1 & Yes & $1 + s$ \\
-    1 & 0 & Yes & $1 + s$ \\
-    1 & -1 & Yes & $1 + s - d$ \\
-    1 & -1 & No & $1 + s - d$ \\
-    0 & 0 & Yes & $1 + s$ \\
-    0 & 0 & No & $1$ \\
-    -1 & 0 & Yes & $1 + s - d$ \\
-    -1 & 0 & No  & $1 - d$ \\
-    -1 & -1 & Yes & $1 + s - 2d$ \\
-    -1 & -1 & No  & $1 - 2d$ \\
+    Yes   & 1 & 1   & $1 + s$ \\
+    Yes   & 1 & 0   & $1 + s$ \\
+    Yes   & 1 & -1  & $1 + s - d$ \\
+    Yes   & 0 & 0   & $1 + s$ \\
+    Yes   & -1 & 0  & $1 + s - d$ \\
+    Yes   & -1 & -1 & $1 + s - 2d$ \\
+    \midrule
+    No    & 1 & -1  & $1 + s - d$ \\
+    No    & 0 & 0   & $1$ \\
+    No    & -1 & 0  & $1 - d$ \\
+    No    & -1 & -1 & $1 - 2d$ \\
   \end{tabular}
@@
 
-All agents select another agent in the population to be a teacher. The 
+All agents select another agent in the population to be a teacher.
+Teacher selection is random, where the probability an agent selects another
+agent is proportional to the probability of interaction given in 
+Equation~\ref{eq:interactionProb}, normalized by the sum of all interaction
+probabilities,
+
+\begin{equation}
+  \Pr(\text{$i$ chooses teacher $j$}) = 
+    \frac{1 + w(a_{ij} + a_{ji})}{\sum_{j \neq i}(1 + w(a_{ij} + a_{ji}))}
+\end{equation}
+% \noindent
+
+The 
 learner agent probabilistically adopts its teacher's signaling or receiving 
@@
 calculated by the logistic sigmoid function applied to the quotient of 
-teacher and learner payoffs accumulated in one signaling/receiving-interaction/payoff round.
+teacher and learner payoffs accumulated in one
+signaling/receiving-interaction/payoff round.
 Let $\pi_{i}$ be the accumulated payoff of agent $i$, and assume $i$ learns

### 2020-05-23 id_signaling/model.py
similarity threshold direct test green

@@ -355,6 +355,9 @@ class Model:
             else:
                 self.attitudes = -1 * np.ones((self.N,), dtype=int)
 
+    def _are_similar(self, a1, a2):
+        similarity = 1 - hamming(a1.traits, a2.traits)
+        return similarity >= self.similarity_threshold
 
     def _calculate_payoff(self, a1, a2):
         '''
@@ -366,9 +369,7 @@ class Model:
 
         # XXX OLD
         # similar = (np.sum(a1.traits * a2.traits) >= self.similarity_threshold)
-
-        similarity = 1 - hamming(a1.traits, a2.traits)
-        similar = similarity >= self.similarity_threshold
+        similar = self._are_similar(a1, a2)
 
         # Like/like.
         if att_sum == 2:
@@ -391,6 +392,7 @@ class Model:
                 # Like/dislike XXX IS THIS EVEN POSSIBLE? smelly....
                 if a1.attitudes[a2.index] > 0 or a2.attitudes[a1.index] > 0:
                     return 1 - self.one_dislike_penalty
+
                 # Neutrals
                 elif a1.attitudes[a2.index] == 0 and a2.attitudes[a1.index] == 0:
                     return 1

### 2020-05-23 test/test_model.py

@@ -37,7 +37,48 @@ def _test_minorities(K, M, minority_trait_frac):
 
 def test_similarity_threshold():
     'Check that payoffs and matching probabilities are as expected for different similarity thresholds.'
-    assert False
+
+    # Initialize model.
+    m = Model(similarity_threshold=0.5)
+
+    # Set up some agents to be similar or dissimlar.
+    a1 = Agent(K=3)
+    a2 = Agent(K=3)
+    a3 = Agent(K=3)
+
+    a1.traits = np.array([1, 1, -1])
+    a2.traits = np.array([1, 1, 1])
+    a3.traits = np.array([1, -1, 1])
+
+    assert m._are_similar(a1, a2)
+    assert not m._are_similar(a1, a3)
+    assert m._are_similar(a2, a3)
+
+    m = Model(similarity_threshold=0.1)
+    assert m._are_similar(a1, a2)
+    assert m._are_similar(a1, a3)
+    assert m._are_similar(a2, a3)
+
+    m = Model(similarity_threshold=0.9)
+    assert not m._are_similar(a1, a2)
+    assert not m._are_similar(a1, a3)
+    assert not m._are_similar(a2, a3)
+    assert m._are_similar(a1, a1)
+    assert m._are_similar(a2, a2)
+    assert m._are_similar(a3, a3)
+
+    m = Model(similarity_threshold=0.5)
+    # Set up some agents to be similar or dissimlar.
+    a1 = Agent(K=10)
+    a2 = Agent(K=10)
+    a3 = Agent(K=10)
+    a1.traits = np.array([1]*5 + [-1]*5)
+    a2.traits = np.array([1]*10)
+    a3.traits = np.array([-1]*4 + [1]*6)
+
+    assert m._are_similar(a1, a2)
+    assert m._are_similar(a2, a3)
+    assert not m._are_similar(a1, a3)
 
 
 def test_invasion_setup():

### 2020-05-23 id_signaling/model.py
fixes #3, new unit tests for similarity threshold, minority experiments, and invasion setup

@@ -11,8 +11,8 @@ from scipy.special import expit
 from scipy.spatial.distance import hamming
 
 
-RECEIVING_STRATEGIES = ["Generous", "Churlish"]
-SIGNALING_STRATEGIES = ["Overt", "Covert"]
+RECEIVING_STRATEGIES = ['Generous', 'Churlish']
+SIGNALING_STRATEGIES = ['Overt', 'Covert']
 
 
 class Model:

### 2020-05-23 test/test_model.py

@@ -16,23 +16,23 @@ def test_minorities():
     _test_minorities(9, 4, 0.25)
     _test_minorities(9, 4, 0.75)
 
-    assert False
 
-
-def _test_minorities(K, M, minority_trait_frac):
+def _test_minorities(K, M, minority_trait_frac, N=100):
 
     # Set up new model with given settings.
-    model = Model(N=100, K=K, n_minmaj_traits=M, minority_trait_frac=minority_trait_frac)
+    model = Model(N=N, K=K, n_minmaj_traits=M,
+                  minority_trait_frac=minority_trait_frac)
 
-    # assert False
+    # Simplest thing to test is the setup. Do we really have a minority and
+    # majority where the number of agents with the minority/majority trait
+    # are as expected?
 
-    # Test #0: do we really have the distribution of minority/majority we
-    # expect?
+    agents = model.agents
 
-    # Test #1: are payoffs as expected for minorities and majorities?
-    # Think I can follow my test_expected_payoff method below.
-
-    # Test #2 ???
+    minority = [a for a in agents if (a.traits[0:M] == [1]*M).all()]
+    majority = [a for a in agents if (a.traits[0:M] == [-1]*M).all()]
+    assert len(minority) == np.floor(minority_trait_frac * N)
+    assert len(majority) == np.floor((1 - minority_trait_frac) * N)
 
 
 def test_similarity_threshold():
@@ -83,8 +83,23 @@ def test_similarity_threshold():
 
 def test_invasion_setup():
     'Check that there are correct number of invading and established populations.'
-    assert False
 
+    _test_invasion_setup()
+    _test_invasion_setup(0.1, 0.9)
+    _test_invasion_setup(0.9, 0.1)
+    _test_invasion_setup(0.1, 0.5)
+    _test_invasion_setup(0.5, 0.1)
+
+
+def _test_invasion_setup(init_cov=0.5, init_ch=0.5, N=100):
+
+    m = Model(N=N, initial_prop_covert=init_cov, initial_prop_churlish=init_ch)
+
+    cov = [a for a in m.agents if a.signaling_strategy == 'Covert']
+    chur = [a for a in m.agents if a.receiving_strategy == 'Churlish']
+
+    assert len(cov) == np.floor(init_cov * N)
+    assert len(chur) == np.floor(init_ch * N)
 
 ##
 # Expected payoffs on interaction. Using results from test above we know the

### 2020-05-24 paper/ms.tex
wrote paragraphs on computational experiments

@@
 \begin{equation}
-  \Pr(\text{$i$ learns from $j$}) = \frac{1}{1 + e^{-\beta(p_{ij} - \alpha)}}.
+  \Pr(\text{$i$ adopts $j$'s strategy}) = \frac{1}{1 + e^{-\beta(p_{ij} - \alpha)}}.
 \end{equation}
 \noindent
-$\alpha$ and $\beta$ are parameters shift and scale the sigmoid curve, respectively. 
+$\alpha$ and $\beta$ are parameters that shift and scale the sigmoid curve, respectively. 
 $\alpha$ is the size of $p_{ij}$ such that $\Pr(\text{$i$ learns from $j$}) = 0.5$. % $P(\text{$i$ learns from $j$}) = 0.5$.
@@
 TO PROVIDE SENSITIVITY CHECKS IN THE SUPPLEMENT).
-
-\subsection{Computational experiment design}
 
@@
     $1 - \rho_{gen} = \rho_{ch}$ & Prevalence of churlish receivers \\
-    $\rho_i^{minor}$, $\rho_i^{maj}$ & Prevalence of strategy $i \in \{cov, ov, gen, ch\}$ amongst minority/majority \\
-    $\Pr(\text{$i$ invades})$ & Probability strategy $i$ invades 
+    $\rho_s^{minor}$, $\rho_s^{maj}$ & Prevalence of strategy $s \in \{cov, ov, gen, ch\}$ amongst minority/majority \\
+    $\Pr(\text{$s$ invades})$ & Probability strategy $s \in \{cov, ov, gen, ch\}$ invades 
   \end{tabular}
@@
 \end{table}
+
+\subsection{Computational experiments}
+
+\subsubsection{Design}
+
+All computational experiments we implemented share a core design. The only 
+difference between experiments is how we initialize agents and which
+outcome measures we analyze. This basic design initializes $N$ agents with
+a trait vector, an attitude vector, and a signaling and receiving strategy.
+Agent attributes can be set fully randomly, as we do for the basic experiments focusing
+on the role of key parameters of homophily ($w$), disliking penalty ($d$), and 
+covert signaling efficiency ($r$). Randomly setting agent attributes means
+choosing $\pm 1$ for each element of agent trait vectors with equal 
+probabilities, and choosing a signaling and receiving strategy at random
+with equal probabilities for each strategy type. Attributes are initialized
+according to the agent's receiving strategy. Generous agents have all 
+attitudes about other agents set to 0, indicating neutrality. Churlish agents
+have all attitudes set to -1, since these agents dislike others by default.
+This and all experiments iterate the model $T$ times, which
+means $T$ signaling rounds, with $I$ interactions between signaling rounds,
+and social learning after the signaling rounds. In this basic experiment,
+we analyze the global prevalence of covert signalers at time $T$ ($\rho_{cov,T}$)
+and the global prevalence of generous receivers at time $T$ ($\rho_{gen,T}$),
+including calculating correlation between the two.
+
+The first variation on this basic model is intended to test our 
+hypothesis that covert signaling prevalence in 
+minority populations ($\rho_{cov}^{minor}$) is inversely correlated with
+homophily. For this, we initialize the first $M$ traits out of $K$ to mark the 
+minority and majority populations. The minority population has its first
+$M$ trait vector elements set to $+1$ and the majority population has its
+first $M$ trait vector elements set to $-1$. For example, if $K=5$, $M=2$,
+and agent $i$ is in the minority, then its trait vector would be
+$\tau_i = (-1, -1, -1, \pm 1, \pm 1)$; if $i$ is in the majority, its 
+trait vector would be $\tau_i = (1, 1, 1, \pm 1, \pm 1)$, where in the last
+two positions the value is chosen randomly with equal probabilities.
+In this experiment we analyze the prevalence of covert signalers and 
+generous receivers in the minority and majority populations at time T: 
+$\rho_{cov,T}^{minor}$, $\rho_{cov,T}^{major}$,
+$\rho_{gen,T}^{minor}$, and $\rho_{gen,T}^{major}$.
+
+(NEXT WRITE INVASION PAR)
+
+\subsubsection{Implementation}
 

### 2020-06-16 paper/ms.tex
updated paper pushing towards fresh draft with current results

@@
   \centering
-  \begin{tabular}{cl}
-    Global parameter & Description \\
+  \begin{tabular}{cp{3.5in}c}
+    Symbol & Definition & Values tested (default in bold)  \\
     \toprule 
-    $K$      & Number of relevant traits determining similarity, liking, disliking, etc. \\
-    $w$      & Homophily \\
-    $d$      & Interaction penalty when one agent dislikes the other \\
-    $\delta$ & Additional interaction penalty when both agents dislike each other \\
-    $s$      & Added interaction benefit when agents are similar, as defined by their traits \\
-    $S$      & Number of traits two agents must have in common to be considered similar \\
-    $M$      & Number of traits used (if any) to define majority/minority populations \\
+    $w$      & \emph{Homophily}, the ability of agents to preferentially interact with similar others & $\{0.0, 0.05, 0.10, \ldots, 0.5\}$ \\
+    $d$      & \emph{Disliking penalty} imposed when one agent dislikes the other & $\{0.0, 0.05, 0.1,\ldots \mathbf{0.25}, \ldots, 0.5\}$ \\
+    $\delta$ & Additional penalty when pair dislike one another & \textbf{0.25} \\
+    $E_{cov}$ & \emph{Efficiency of covert signaling} & $\{0.0, 0.05, 0.1,\ldots \mathbf{0.25}, \ldots, 0.5\}$ \\
+    $E_{ov}$ & \emph{Efficiency of overt signaling} & \textbf{0.5} \\
+    $s$      & \emph{Similarity benefit} received by similar interacting pair & \textbf{??} \\
+    $K$      & Number of agent identity traits & $\{\mathbf{3}, 9\}$ \\
+    $S$      & Minimum fraction of traits in common for a pair to be considered similar & 
+      $\{0.1, 0.2, \ldots, \mathbf{0.5}, \ldots, 1.0\}$\\
+    $M$      & Number of traits used to define majority/minority populations & $\{\mathbf{2}, 4\}$\\
   \end{tabular}
-  \caption{Global model parameters.}
+  \caption{Global, as opposed to agent-specific, model parameters. 
+  Explanatory model parameters are used to answer
+  our guiding questions about identity communication strategies. In the final
+  column the default value is in bold, if there is one. Homophily never has a
+  default value because it is varied in every computational experiment
+  condition we test.}
   \label{tab:params}
@@
   \item have adopted a signaling and receiving strategy
-\end{enumerate}Signaling strategies
+\end{enumerate}
+Signaling strategies
 may be either \emph{covert} or \emph{overt}, and receiving strategies may be
@@
 
-\subsubsection{Design}
+Using the basic components of Agents with attributes and communication, interaction,
+and learning processes, we simulated the time course of prevalence of 
+covert/overt signalers ($\rho_{cov/ov,t}$) and churlish/generous receivers 
+($\rho_{ch/gen,t}$) among the simulated
+population as a whole or among agents specified as minorities or majorities.
+To understand when and why different communication strategies become prevalent
+over others, we varied a number of parameters with important real-world
+interpretations that answer this question. Specifically, we want to know
+the effects of varying \emph{explanatory parameters} 
+homophily ($w$), covert signaling efficiency ($r$), and the
+payoff penalty when one interaction partner dislikes the other ($d$). 
+(EXPLAIN HOW THESE ANSWER OUR RESEARCH QUESTIONS). We analyze these questions
+in three different framings.
 
-All computational experiments we implemented share a core design. The only 
-difference between experiments is how we initialize agents and which
-outcome measures we analyze. This basic design initializes $N$ agents with
-a trait vector, an attitude vector, and a signaling and receiving strategy.
-Agent attributes can be set fully randomly, as we do for the basic experiments focusing
-on the role of key parameters of homophily ($w$), disliking penalty ($d$), and 
-covert signaling efficiency ($r$). Randomly setting agent attributes means
+Our experiments are divided into three main parts: (1) a basic experiment
+to understand the role of the explanatory parameters in the evolution of
+communication strategies; (2) an experiment where
+we assign all agents to be in the
+minority or majority to understand how minorities utilize covert signaling;
+and (3) ``invasion'' (BETTER WORD?) experiments to understand how different
+communication strategies spread. In our first experiment, we assume nothing 
+about the distribution of agent traits, $\tau_{ik}$, other than each is 
+drawn randomly from $\{-1, 1\}$. Similarly, all communication strategies
+are randomly initialized with each strategy given equal probability of
+being chosen. In our second experiment we create majorities and minorities
+by setting $M$ of $K$ $\tau_{ik}$ to be
+$-1$ for some majority of agents and $+1$ for some minority of agents, where
+the fraction of agents in the minority is denoted $\rho^{minor}$. 
+In our third and final experiment, we examine what conditions allow for the
+spread of different communication strategies when they are initially rare,
+which is called an invasion analysis, borrowing from evolutionary theory.
+For one example of four, to see if covert signaling can spread when initially rare, we
+set the initial prevalence of covert signalers to be $\rho_{cov,0}=0.05$ by
+initializing that fraction of agents to be covert signalers, and the rest
+initialize to be overt signalers. Our outcome measure in this last case is
+the number of times the prevalence of covert signaling, e.g., reaches a 
+stable value above its initial value of 0.05. To ensure none of the results
+from these computational experiments are not due to arbitrary settings of
+what we have identified as non-explanatory parameters, we also
+perform sensitivity analyses.
+
+\subsubsection{Evolution of signaling strategies}
+
+This basic design initializes $N$ agents with a arndomized trait vector, 
+an attitude vector, and a signaling and receiving strategy.
+Randomly setting agent attributes means
 choosing $\pm 1$ for each element of agent trait vectors with equal 
@@
 
+\subsubsection{Covert signaling in minority/majority populations}
 The first variation on this basic model is intended to test our 
@@
 
-(NEXT WRITE INVASION PAR)
+\subsubsection{Communication strategy invasion}
 
-\subsubsection{Implementation}
+To understand when a rare communication strategy can become stably established
+in a population, we perform invasion analyses by setting a small fraction of
+the population to have one of the four strategies, and see if that strategy
+reaches a stable, increased prevalence. Whichever strategy, call it $s$,  of the invading
+population, the prevalence of that strategy is set to 0.05, $\rho_{s,t=0}=\rho_{s,0}=0.05$.
+When we consider strategy $s$ is invading, it is either a signaling or receiving strategy. 
+Whether signaling or recieving, the non-invading part of the population has
+their strategy set to the alternative for that communication process, e.g.\
+if $s=cov$, then $\rho_{cov,0}=0.05$ and $\rho_{ov,0}=0.95$.
+
+\subsubsection{Sensitivity analyses}
+
+The main text is dedicated to demonstrating the adaptiveness of covert signaling
+and churlish receiving, compared to their alternatives overt signaling and
+generous receiving. There are a number of parameters that may have an outsize impact on our results
+that we do not report in the main text. While we report the results of these
+experiments in the Appendix, we specify which parameters we set constant for
+our main results, and describe our experiments for testing model sensitivity
+to these parameters
+
+\begin{enumerate}
+  \item Correlation between churlish receiving and covert signaling prevalences
+  \item Introduction of $\delta \neq d$, additional penalty for both interacting
+    agents disliking one another.
+  \item Minority and similarity dynamics with more traits.
+\end{enumerate}
 
@@
 
+Here I co-vary the disliking penalties, which I set equal ($d=\delta$), and
+homophily, $w$. Here, $r=0.25$ and $R=0.5$.
+
+Specifically, I vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$
+As in the above experiment, I set $w \in \{0.0, 0.5, \ldots, 0.45\}$.
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/basic_disliking_signaling.pdf}
+    \caption{Density of covert signalers.}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/basic_disliking_receiving.pdf}
+    \caption{Density of churlish receivers.}
+  \end{subfigure}
+
+  \caption{Density of covert signalers and churlish receivers at $t=500$, 
+    the final timestep.}
+  \label{fig:dislikingHomophilyHeatmap}
+\end{figure}
+
 \subsubsection{...as a function of covert signaling efficiency}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/basic_receptivity_signaling.pdf}
+    \caption{Density of covert signalers.}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/basic_receptivity_receiving.pdf}
+    \caption{Density of churlish receivers.}
+  \end{subfigure}
+
+  \caption{Density of covert signalers and churlish receivers at $t=200$, 
+    final timestep recorded in this preliminary experiment. Receptivity of
+    overt signals is $R=0.5$.}
+  \label{fig:receptivityHomophilyHeatmap}
+\end{figure}
 
@@
 
-Our computational results support this theoretical claim. As the heatmaps
-below reveal... In the SI we show regressions of $\rho_{cov,T} \sim \rho_{gen,T}$.
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/receptivity_allcombos_reg.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/disliking_allcombos_reg.pdf}
+    \caption{}
+    \label{fig:}
+  \end{subfigure}
+  \caption{Correlation between proportion of covert signalers and proportion of
+    churlish receivers for all tested parameter combinations in both 
+    receptivity (a) and disliking (b) experiments. (NEED TO CHECK HOW I'M AVERAGING
+    HERE AND POSSIBLY AGGREGATE FURTHER AS A SMOOTHING FILTER. ALSO NEED TO
+    )}
+  \label{fig:regressions}
+\end{figure}
 
@@
 
+Here we analyze the evolution of covert signaling in populations where there
+are minority and majority sub-populations, as specified by agents' trait
+vectors, $\tau_i$. In these experiments, the first $M$ of each agent's $K$ traits
+are set to 1 or -1: fraction $\rho^{minor}$ of the
+population is in the minority, and have the first $M$ of their traits set to
+1, and the rest of the population is the majority, with the first $M$ of their
+traits set to -1.
+
+We primarily vary the minority prevalence, $\rho^{minor}$, and set $M=1$ and
+$K=3$, except for one heatmap in 
+Figure~\ref{fig:covert-signaling-minority-heatmap}.
+
+\subsubsection{Covert minority signaling over minority prevalence}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.31\textwidth}
+    \includegraphics[width=\textwidth]{Figures/minority-homophily=0p05.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.31\textwidth}
+    \includegraphics[width=\textwidth]{Figures/minority-homophily=0p25.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.31\textwidth}
+    \includegraphics[width=\textwidth]{Figures/minority-homophily=0p45.pdf}
+    \caption{}
+  \end{subfigure}
+  \caption{}
+\end{figure}
+
+\subsubsection{Minority covert signaling over homophily and disliking}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/covert_signalers_diff_0p05.pdf}
+    % \caption{Prevalence of minority covert receivers; $\rho^{minor} = 0.10$.}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/covert_signalers_diff_0p10.pdf}
+    % \caption{Prevalence of minority covert receivers; $\rho^{minor} = 0.25$.}
+  \end{subfigure} \\[.25in]
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/covert_signalers_diff_0p25.pdf}
+    % \caption{Prevalence of minority churilsh receivers; $\rho^{minor} = 0.10$.}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/covert_signalers_diff_0p10_K=10_M=4.pdf}
+    \caption{(NEED TO UPDATE WITH K=9 AND M=4. Ran these, just need to pull from
+    MERCED and analyze.)}
+  \end{subfigure}
+  \caption{Difference in covert signaling prevalence between minority and
+  majority populations for different parameters settings.}
+  \label{fig:covert-signaling-minority-heatmap}
+\end{figure}
+
+\subsubsection{Minority churlish receiving over homophily and disliking}
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/churlish_receivers_diff_0p05.pdf}
+    % \caption{Prevalence of minority covert receivers; $\rho^{minor} = 0.10$.}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/churlish_receivers_diff_0p10.pdf}
+    % \caption{Prevalence of minority covert receivers; $\rho^{minor} = 0.25$.}
+  \end{subfigure} \\[.25in]
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/churlish_receivers_diff_0p25.pdf}
+    % \caption{Prevalence of minority churilsh receivers; $\rho^{minor} = 0.10$.}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/churlish_receivers_diff_0p10_K=10_M=4.pdf}
+    % \caption{Prevalence of minority churilsh receivers; $\rho^{minor} = 0.25$.}
+  \end{subfigure}
+  \caption{Difference in churlish receiving prevalence between minority and majority
+  populations for different parameter settings.}
+\end{figure}
+
 \subsection{Covert signaling invasion}
 
-\subsection{Non-signaling as an adaptive strategy}
+In this experiment we begin with initial proportions, $\rho$ of one of the strategies
+at 0.05 and consider this the ``invading'' strategy. $\rho_{cov,0}$ represents
+the initial covert proportion, $\rho_{ov,0}$ the initial overt proportion,
+$\rho_{ch,0}$ the initial churlish proportion, and $\rho_{gen,0}$ the 
+initial generous proportion. We measure how often
+a non-zero proportion of agents with the invading strategy manage to 
+establish a permanent population, which we call invasion success. We calculated
+invasion success for a number of experimental parameter settings, covarying
+over disliking penalty ($d=\delta$) and homophily ($w$) in the first case,
+and over relative covert receptivity ($r/R$) and homophily ($w$) 
+in the second case (Figures~\ref{fig:cov-ov-invade} and~\ref{fig:ch-gen-invade}).
+
+\begin{figure}[H]
+  \centering
+    \begin{subfigure}{0.49\textwidth}
+      \includegraphics[width=\textwidth]{Figures/covert_invades.pdf}
+      \caption{Covert invades, $\rho_{cov,0}=0.05$}
+    \end{subfigure}
+    \begin{subfigure}{0.49\textwidth}
+      \includegraphics[width=\textwidth]{Figures/overt_invades.pdf}
+      \caption{Overt invades, $\rho_{cov,0}=0.95$}
+    \end{subfigure}
+  \caption{Covert and overt sending strategy invasion success rates. 
+    Lower homophily is more favorable for successful covert signaling invasion.
+    This is due to lower homophily meaning agents cannot assort well into
+    similar pairs prior to interaction.
+    Similarly, greater homophily is more favorable for successful overt
+    signaling invasion, where agents can better assort if they know each other's
+    true traits. Unexpectedly, as covert receptivity increases, overt signaling
+    is is more successful at invading and covert signaling is less successful
+    at invading when the initial churlishness is high. When initial
+    churlishness is small to moderate, the pattern is reversed.
+  }
+  \label{fig:cov-ov-invade}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    \begin{subfigure}{0.49\textwidth}
+      \includegraphics[width=\textwidth]{Figures/churlish_invades.pdf}
+      \caption{Churlish invades, $\rho_{ch,0}=0.05$}
+    \end{subfigure}
+    \begin{subfigure}{0.49\textwidth}
+      \includegraphics[width=\textwidth]{Figures/generous_invades.pdf}
+      \caption{Generous invades, $\rho_{ch,0}=0.95$}
+    \end{subfigure}
+  \caption{Churlish and generous receiving strategy invasion success rates.
+    For low to moderate rates of initial covert signaling there is not much
+    of a pattern to invasion success. High values of homophily do seem to lead
+    to more successful churlish invasion for moderate values of initial
+    covert signalers. For large initial proportions of covert
+    signalers, lower homophily favors generous invasion, which is more pronounced
+    for larger disliking penalties.
+  }
+  \label{fig:ch-gen-invade}
+\end{figure}
+
+\subsubsection{Non-signaling as an adaptive strategy}
+
+One of the most striking patterns in the invasion results is the evolution
+of a third de facto strategy of non-signaling. This strategy emerges when
+we consider both the invasion dynamics of either the covert or overt 
+signaling strategy. When simulating the invasion of covert signaling
+($\rho_{cov,0}=0.05$), the non-signaling strategy emerges when the covert
+signaling efficiency, $r$, is 0, but covert signaling still successfully
+invades as the chosen agent strategy. When $r=0$, no agents receive
+covert signals, making this more accurately a \emph{non-signaling} strategy.  
+For covert signaling invasion, this only happens when the initial churlishness
+is low ($\rho_{ch,0}=0.05$) and homophily is also low ($w \lessapprox 0.2$). 
+Non-signaling wins out evolutionarily 
+in some cases when considering of invading overt signalers when overt signalers
+fail to invade but $r=0$, again meaning agents in this society prefer not
+to signal at all. This occurs some of the time for all tested homophily
+values and low initial churlishness ($\rho_{ch,0}=0.05$) (Figure~\ref{fig:cov-ov-invade}b, bottom left plot).  
+Overt signaling continues to fail to evolve at least some of the time
+for $r=0$ for moderate initial churlishness ($\rho_{ch,0}=0.5$) up up to perfect 
+assortment homophily, $w=0.5$.
 

### 2020-06-24 paper/ms.tex

@@
 \usepackage{tabularx}
+\usepackage{multirow}
 \usepackage{float}
@@
     $E_{ov}$ & \emph{Efficiency of overt signaling} & \textbf{0.5} \\
-    $s$      & \emph{Similarity benefit} received by similar interacting pair & \textbf{??} \\
+    $s$      & \emph{Similarity benefit} received by similar interacting pair & \textbf{0.25} \\
     $K$      & Number of agent identity traits & $\{\mathbf{3}, 9\}$ \\
@@
       $\{0.1, 0.2, \ldots, \mathbf{0.5}, \ldots, 1.0\}$\\
-    $M$      & Number of traits used to define majority/minority populations & $\{\mathbf{2}, 4\}$\\
+    $M$      & \emph{Number of minority/majority traits} used to define majority/minority populations & $\{\mathbf{2}, 4\}$\\
+    $R$      & \emph{Number of interaction rounds} following a signaling round \\
+    $\alpha$ & Threshold payoff multiplier to give learner 50\% chance of 
+               adopting teacher's strategy \\
+    $\beta$  & Factor that, as it increases, both lowers chance of learner 
+               adopting strategy when $\pi_{teach}/\pi_{learn} < \alpha$ and
+               raises chance of learner adopting teacher strategy when 
+               $\pi_{teach}/\pi_{learn} > \alpha$.
   \end{tabular}
@@
     $\tau_{ik}$ & Trait $k$ of agent $i$; $\tau_i$ is the $K$-dimensional trait vector of agent $i$. \\
+    $s_{ij}$   & \emph{Similarity} between agents $i$ and $j$. Equal to $1-h(\tau_i,\tau_j)$ 
+                 where $h(\tau_i, \tau_j)$ is the Hamming distance between 
+                 $i$ and $j$'s trait vectors. \\ 
     Signaling strategy & Either \emph{overt} or \emph{covert}. Overt signaling always
@@
   \end{tabular}
-  \caption{Agent attributes.}
+  \caption{Agent and inter-agent attributes.}
   \label{tab:agentAttributes}
@@
 similar traits, and $-1$ if $i$ and $j$ are sufficiently different. Similarity
-is $s_{ij} = 1 - d(\tau_i, \tau_j)$ where $d(\tau_i, \tau_j)$ is the
+is
+
+\begin{equation}
+  s_{ij} = 1 - h(\tau_i, \tau_j)
+  \label{eq:similarity}
+\end{equation}
+\noindent
+where $h(\tau_i, \tau_j)$ is the
 Hamming distance between trait vectors. The Hamming distance is the fraction
@@
 interact; the payoff received when a particular dyad interacts; and the
-probability that one agent chooses another as a teacher.
+probability that one agent chooses another as a teacher. Dyad similarity 
+also determines whether or not a covert signal is ``understood'' by a 
+receiver who is not sufficiently similar to the sender. In this case, the
+receiver's attitude about the sender will remain unchanged from its
+initialization: $-1$ if the receiver is churlish and $0$ if the receiver is
+generous.
 
@@
 
-At the signaling and receiving step, agents form attitudes about one another if
-they receive a signal from
+At the signaling and receiving step, an agent updates its attitude about another
+agent if they receive a signal from that agent. How many agents receive a
+single agent's signal depends on whether the signaling agent is an overt or
+covert signaler, and the global parameters \emph{efficiency of overt signaling}, $E_{ov}$,
+and \emph{efficiency of covert signaling}, $E_{cov}$. An overt signal reaches
+$E_{ov} \times N$ agents and a covert signal reaches $E_{cov} \times N$ 
+agents---which agents receive either signal type are chosen at random.
+Overt signaling efficiency is set to $E_{ov}=0.5$ for all experiments presented
+in the main text; (WE NEED TO RUN SENSITIVITY CHECKS ON THIS FOR THE SI). Covert
+signaling efficiency is varied for one of our primary experimental variations
+taking values from 0.1 to 0.5 in steps of 0.05.
+
+\begin{itemize}
+  \item The difference between overt and covert signals is the conditions
+    under which the signal has an effect on the recieving agent's attitudes
+    towards the sender.
+    \begin{itemize}
+      \item Overt signals, when recieved, always noticed and can change the
+        receivers attitude about the signaler.
+      \item Covert signals, when received, are not ``noticed'' by receivers
+        if signaler and receiver are not sufficiently similar. 
+      \item Recall agents are similar in our model if their inter-agent
+    \end{itemize}
+\end{itemize}
 
@@
 
-The two agents interact with different probabilities
-depending on their attitudes about one another, and depending on the 
-assumed homophily level. If  Note that as $w \rightarrow 0.5$,
-agents never interact with agents they dislike and always interact with 
-agents they like.
-
+Interaction occurs in two stages between two randomly-selected agents.
+In the first stage, agents are matched in dyads at random. All agents
+are matched with a partner. In the second stage, agents \emph{collaborate} with
+one another depending on their attitudes towards one another and the homophily
+level, $w$, in the experimental condition.
+Recall that increased homophily means an increased 
+preference for agents to only collaborate with similar others. 
+This is operationalized in as
 \begin{equation}
-  \Pr(\text{$i$ interacts with $j$}) = \frac{1 + w(a_{ij} + a_{ji})}{2}
+  \Pr(\text{$i$ collaborates with $j$}) = \frac{1 + w(a_{ij} + a_{ji})}{2}
+  \label{eq:homophily}
 \end{equation}
 \noindent
+where $w$ is the homophily value, constrained between 0 and 0.5, and $a_{ij}$
+is agent $i$'s attitude towards agent $j$.
+Note that as $w \rightarrow 0.5$, agents never collaborate with agents they 
+dislike. Agents will only collaborate with agents they are neutral towards
+or like. Furthermore, as $w \rightarrow 0.5$, agents more rarely are 
+penalized for disliking their collaboration partner since they will never
+interact with others whom they dislike.
 
@@
 
-Payoffs are determined based on the similarity bonus, $s$, and the disliking
-penalty $d$\footnote{In the SI we consider the case where the disliking penalty 
+Agents gain payoffs when a dyad collaborates. Payoffs
+are determined based on the similarity bonus, $s$, and the disliking
+penalty $d$. The base payoff is 1, which is awarded if agents have neutral
+attitudes towards one another, i.e., $a_{ij}=a_{ji}=1$. 
+If the agents are similar, i.e.\ $s_{ij} > S$, then 
+the payoff is supplemented by the similarity bonus, $s$. Note that the
+collaboration penalty is not determined by \emph{dissimilarity}, but by
+\emph{disliking}. Specifically, if just one agent dislikes the other, a penalty
+of $d$ is subtracted from the base payoff. If both agents dislike one another,
+a penalty of $2d$ is subtracted from the base payoff. 
+In the SI we consider the case where the disliking penalty 
 when both agents dislike each other is different from $d$. We call this $\delta$
-and let it vary from 0 to $2d$}.
+and let it vary from 0 to $2d$. Note that, due to the orthogonality of 
+similarity and attitude, it is possible for agents to be similar and 
+to dislike one another. All possible payoffs are given in 
+Table~\ref{tab:payoffs}.
 
 \begin{table}[h]
+  \vspace{1em}
   \centering
   \begin{tabular}{cccc}
-    Similar? & $a_{ij}$ & $a_{ji}$ & Payoff $\pi_i = \pi_j$ \\
+    Similar? & $a_{ij}$ & $a_{ji}$ & Payoff \\
     \toprule
-    Yes   & 1 & 1   & $1 + s$ \\
-    Yes   & 1 & 0   & $1 + s$ \\
-    Yes   & 1 & -1  & $1 + s - d$ \\
-    Yes   & 0 & 0   & $1 + s$ \\
-    Yes   & -1 & 0  & $1 + s - d$ \\
-    Yes   & -1 & -1 & $1 + s - 2d$ \\
+    \multirow{6}{*}{Yes}   & 1 & 1   & $1 + s$ \\
+       & 1 & 0   & $1 + s$ \\
+       & 1 & -1  & $1 + s - d$ \\
+       & 0 & 0   & $1 + s$ \\
+       & -1 & 0  & $1 + s - d$ \\
+       & -1 & -1 & $1 + s - 2d$ \\
+
+    % Yes   & 1 & 1   & $1 + s$ \\
+    % Yes   & 1 & 0   & $1 + s$ \\
+    % Yes   & 1 & -1  & $1 + s - d$ \\
+    % Yes   & 0 & 0   & $1 + s$ \\
+    % Yes   & -1 & 0  & $1 + s - d$ \\
+    % Yes   & -1 & -1 & $1 + s - 2d$ \\
     \midrule
-    No    & 1 & -1  & $1 + s - d$ \\
-    No    & 0 & 0   & $1$ \\
-    No    & -1 & 0  & $1 - d$ \\
-    No    & -1 & -1 & $1 - 2d$ \\
+    % No    & 1 & -1  & $1 - d$ \\  <-- on further review, this seems impossible...
+    %                                   since a_{ij}=1 is only possible if
+    %                                   agents are similar.
+    \multirow{3}{*}{No}    & 0 & 0   & $1$ \\
+        & -1 & 0  & $1 - d$ \\
+        & -1 & -1 & $1 - 2d$ \\
   \end{tabular}
@@
   another due to churlish receiving if they have never signaled each other.}
+  \label{tab:payoffs}
 \end{table}
@@
 
-The 
-learner agent probabilistically adopts its teacher's signaling or receiving 
+The learner agent probabilistically adopts its teacher's signaling or receiving 
 strategy---which type of strategy might be learned is determined by a coin flip. 
@@
 
-We are primarily interested in the prevalence of covert signaling at time
-$t$. Usually, $t=T$, where $T$ is the number of iterations chosen for our 
+First, we are interested in the prevalence of covert signaling in the
+whole population at time
+$t$, denoted $\rho_{cov,t}$. For a complete understanding of model dynamics,
+we also track the prevalence of overt signaling and each receiving strategy,
+denoted similarly (see Table~\ref{tab:outcomeMeasures}).
+Usually, $t=T$, where $T$ is the number of iterations chosen for our 
 computational experiments. The prevalence of overt signalers is the complement 
@@
 prevalence of covert signalers at $t=T$ is positively correlated with the
-prevalence of generous receivers at $t=T$.
+prevalence of generous receivers at $t=T$. When considering $t=T$ we (SHOULD?)
+drop the subscript and write $\rho_{cov}$, for example.
 
 \begin{table}[H]
+  \vspace{1em}
   \centering
@@
 \end{table}
+
+In addition to the prevalence of signaling and receiving strategies in the whole
+population, we need to track the prevalence of strategies within  
+minority and majority populations, where the prevalence of siganling or
+receiving strategy $s$ in the minority (majority) population at time $t$ is written
+$\rho_{s,t}^{minor}$ ($\rho_{s,t}^{major}$). Again, we may drop $t$ when 
+consider the long-time equilibrium ($t=T$) of these prevalence values.
+
+Our final computational experiment analyzes whether strategy $s$ can ``invade''
+the population and establish a stable, sizable population of agents adopting
+that strategy. Here our outcome measure is the calculated probability (i.e.\
+frequency) of invasion success, where a stable sizable population adopting
+that strategy emerges. We write this $\Pr(\text{$s$ invades})$ where $s$
+is covert, overt, generous, or churlish.
 
@@
 and social learning after the signaling rounds. In this basic experiment,
-we analyze the global prevalence of covert signalers at time $T$ ($\rho_{cov,T}$)
-and the global prevalence of generous receivers at time $T$ ($\rho_{gen,T}$),
-including calculating correlation between the two.
+we analyze the global prevalence of covert signalers at time $T$, denoted
+$\rho_{cov,T}$, and the global prevalence of generous receivers at time $T$,
+denoted $\rho_{gen,T}$, including calculating correlation between the two.
 
@@
 hypothesis that covert signaling prevalence in 
-minority populations ($\rho_{cov}^{minor}$) is inversely correlated with
-homophily. For this, we initialize the first $M$ traits out of $K$ to mark the 
+minority populations, denoted $\rho_{cov}^{minor}$, is inversely correlated with
+homophily, $w$. For this, we initialize the first $M$ traits out of $K$ to mark the 
 minority and majority populations. The minority population has its first
@@
 
-\subsection{Evolution of covert signaling...}
+\subsection{Basic covert signaling prevalence dynamics}
 
-\subsubsection{...under various homophily and disliking scenarios}
+% Here I co-vary the disliking penalties, which I set equal ($d=\delta$), and
+% homophily, $w$. Here, $=0.25$ and $R=0.5$.
 
-Here I co-vary the disliking penalties, which I set equal ($d=\delta$), and
-homophily, $w$. Here, $r=0.25$ and $R=0.5$.
-
-Specifically, I vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$
-As in the above experiment, I set $w \in \{0.0, 0.5, \ldots, 0.45\}$.
+Our first task is to support our basic hypotheses that, other
+things being equal, (1) covert signaling will
+be the preferred strategy when penalties for disliking and 
+being disliked is high and homophily is relatively weak; (2) increased homophily reduces the utility of
+covert signaling since one rarely interacts when agents dislike one another;
+and, finally, (3) if homophily is moderate or weak, increased covert signaling
+efficiency leads to greater covert signaling prevalence.
+To support these hypotheses, we present computational experiments below where
+three explanatory parameters are varied systematically: homophily, $w$; 
+disliking penalty, $d$; and covert signaling efficiency $E_{cov}$. 
+Specifically, we co-vary homophily, disliking penalty, and covert signaling
+efficiencies all in the same range $w,d,E_{cov} \in \{0.0, 0.05, 0.1, \ldots, 0.5\}$.
+We co-vary these parameters in two separaete experiments. Both experiments
+vary $w$ over those values. One experiment varies $d$ and one varies $E_{cov}$.
 
@@
     \includegraphics[width=\textwidth]{Figures/basic_disliking_signaling.pdf}
-    \caption{Density of covert signalers.}
+    \caption{Covert signaling prevalence under a variety of homophily and
+    disliking penalty parameter values. }
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=\textwidth]{Figures/basic_disliking_receiving.pdf}
-    \caption{Density of churlish receivers.}
+    \includegraphics[width=\textwidth]{Figures/basic_receptivity_signaling.pdf}
+    \caption{Covert signaling prevalence under a variety of homophily and
+    covert signaling efficiency values. $d=0.25$; all other parameters set to
+  defaults listed in Table~}
   \end{subfigure}
 
-  \caption{Density of covert signalers and churlish receivers at $t=500$, 
-    the final timestep.}
+  \caption{Covert signaling prevalence is sensitive to changes in all 
+  three explanatory parameters for our basic experiment, homophily ($w$),
+disliking penalty ($d$), and covert signaling efficiency ($E_{cov}$). 
+In (a) $E_{cov}=0.25$; in (b) $d=0.25$. All other parameters in both sets of 
+    results (a) and (b) are set to defaults listed in Table~\ref{tab:params}.}
   \label{fig:dislikingHomophilyHeatmap}
@@
 
-\subsubsection{...as a function of covert signaling efficiency}
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{Figures/basic_receptivity_signaling.pdf}
-    \caption{Density of covert signalers.}
-  \end{subfigure}
-  \begin{subfigure}{0.49\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{Figures/basic_receptivity_receiving.pdf}
-    \caption{Density of churlish receivers.}
-  \end{subfigure}
-
-  \caption{Density of covert signalers and churlish receivers at $t=200$, 
-    final timestep recorded in this preliminary experiment. Receptivity of
-    overt signals is $R=0.5$.}
-  \label{fig:receptivityHomophilyHeatmap}
-\end{figure}
+% \subsubsection{...as a function of covert signaling efficiency}
 
@@
     HERE AND POSSIBLY AGGREGATE FURTHER AS A SMOOTHING FILTER. ALSO NEED TO
-    )}
+). (THINK ABOUT HOW WE COULD USE PAIR PLOT GRIDS TO COMMUNICATE SOME OF
+These, such as in https://jakevdp.github.io/PythonDataScienceHandbook/04.14-visualization-with-seaborn.html
+I'm already going towards that with the invasion plots, but this would be
+plotting correlations between outcome variables and maybe do a 2x2 with
+signaling and receiving prevalences on x and y axes, respectively. Each plot
+with be one of $s \in {cov, ov} \times {ch, gen}$.)}
+
   \label{fig:regressions}
@@
 
-\subsection{Minority-majority dynamics}
+\subsubsection{Covert signaling is favored in less tolerant and more diverse societies}
+
+(THIS PART REQUIRES NEW EXPERIMENTS. These need to be explained in Model 
+  section. Below I am just writing a paragraph for myself to guide the 
+experiment.)
+
+Now we evaluate two related hypotheses, that (1) more tolerant societies
+foster greater overt signaling prevalence and less covert signaling, i.e., more
+tolerant societies promote honest communication; 
+and (2) increased cultural diversity fosters increased 
+covert signaling prevalence---that is, one must be more cautious since more
+diversity means more social norms and taboos to navigate.
+
+To test the first hypothesis that less tolerant societies foster greater
+covert signaling prevalence, we
+systematically varied the similarity threshold $S \in \{0.1, 0.2, \ldots, 0.9\}$.
+Recall this threshold determines whether
+two agents are deemed ``similar''. Two agents are similar if their similarity
+$s_{ij} \geq S$ (see Equation~\ref{eq:similarity}; Table~\ref{tab:params}). 
+We can think of the ``tolerance'' of agents to be $1-S$; then
+high levels of tolerance mean a lower threshold for similarity.
+
+\subsubsection{Covert signaling is favored among minority groups}
 
@@
 
-We primarily vary the minority prevalence, $\rho^{minor}$, and set $M=1$ and
-$K=3$, except for one heatmap in 
+We primarily vary the minority prevalence, $\rho^{minor} \in \{0.1, 0.15, \ldots, 0.45\}$. 
+We vary $\rho^{minor}$ for two parameter pairs of $(K, M)$, where $K$ is the cultural 
+complexity, and $M$ is the integer number of traits used to define 
+majority/minority populations. The similarity threshold is set to $S=0.5$. 
+We test the settings $K=3$, $M=1$, and $K=9$, $M=4$. We also test three
+values of homophily and disliking penalty, representing low, medium, and high
+levels for each: $w,d \in \{0.05, 0.25, 0.45\}$.
+
+By setting $K$ and $M$ to these two values we test two different social
+situations: in the first, $K=3$ and $M=1$, it is relatively easier for two binary traits
+to match (1/4 probability) than the second case, 
+with $K=9$ and $M=4$ where five binary traits must match (1/32 probability).
+Our current results show \dots
 Figure~\ref{fig:covert-signaling-minority-heatmap}.
@@
 \subsubsection{Covert minority signaling over minority prevalence}
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.31\textwidth}
-    \includegraphics[width=\textwidth]{Figures/minority-homophily=0p05.pdf}
-    \caption{}
-  \end{subfigure}
-  \begin{subfigure}{0.31\textwidth}
-    \includegraphics[width=\textwidth]{Figures/minority-homophily=0p25.pdf}
-    \caption{}
-  \end{subfigure}
-  \begin{subfigure}{0.31\textwidth}
-    \includegraphics[width=\textwidth]{Figures/minority-homophily=0p45.pdf}
-    \caption{}
-  \end{subfigure}
-  \caption{}
-\end{figure}
-
-\subsubsection{Minority covert signaling over homophily and disliking}
 
@@
 
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.31\textwidth}
+    \includegraphics[width=\textwidth]{Figures/minority-homophily=0p05.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.31\textwidth}
+    \includegraphics[width=\textwidth]{Figures/minority-homophily=0p25.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.31\textwidth}
+    \includegraphics[width=\textwidth]{Figures/minority-homophily=0p45.pdf}
+    \caption{}
+  \end{subfigure}
+  \caption{}
+\end{figure}
+
+\subsection{Covert signaling invasion}
+
+In this experiment we begin with initial proportions, $\rho$ of one of the strategies
+at 0.05 and consider this the ``invading'' strategy. $\rho_{cov,0}$ represents
+the initial covert proportion, $\rho_{ov,0}$ the initial overt proportion,
+$\rho_{ch,0}$ the initial churlish proportion, and $\rho_{gen,0}$ the 
+initial generous proportion. We measure how often
+a non-zero proportion of agents with the invading strategy manage to 
+establish a permanent population, which we call invasion success. We calculated
+invasion success for a number of experimental parameter settings, covarying
+over disliking penalty ($d=\delta$) and homophily ($w$) in the first case,
+and over relative covert receptivity ($r/R$) and homophily ($w$) 
+in the second case (Figure~\ref{fig:cov-invades} below; Figures~\ref{fig:ov-invades} and~\ref{fig:ch-gen-invades} in the supplement).
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{Figures/covert_invades.pdf}
+  % \caption{Covert invades, $\rho_{cov,0}=0.05$}
+  \caption{Covert and overt sending strategy invasion success rates. 
+    Lower homophily is more favorable for successful covert signaling invasion.
+    This is due to lower homophily meaning agents cannot assort well into
+    similar pairs prior to interaction.
+    Similarly, greater homophily is more favorable for successful overt
+    signaling invasion, where agents can better assort if they know each other's
+    true traits. Unexpectedly, as covert receptivity increases, overt signaling
+    is is more successful at invading and covert signaling is less successful
+    at invading when the initial churlishness is high. When initial
+    churlishness is small to moderate, the pattern is reversed.
+  }
+  \label{fig:cov-invades}
+\end{figure}
+
+\subsubsection{Non-signaling as an adaptive strategy}
+
+One of the most striking patterns in the invasion results is the evolution
+of a third de facto strategy of non-signaling. This strategy emerges when
+we consider both the invasion dynamics of either the covert or overt 
+signaling strategy. When simulating the invasion of covert signaling
+($\rho_{cov,0}=0.05$), the non-signaling strategy emerges when the covert
+signaling efficiency, $r$, is 0, but covert signaling still successfully
+invades as the chosen agent strategy. When $r=0$, no agents receive
+covert signals, making this more accurately a \emph{non-signaling} strategy.  
+For covert signaling invasion, this only happens when the initial churlishness
+is low ($\rho_{ch,0}=0.05$) and homophily is also low ($w \lessapprox 0.2$). 
+Non-signaling wins out evolutionarily 
+in some cases when considering of invading overt signalers when overt signalers
+fail to invade but $r=0$, again meaning agents in this society prefer not
+to signal at all. This occurs some of the time for all tested homophily
+values and low initial churlishness ($\rho_{ch,0}=0.05$) (Figure~\ref{fig:cov-invades}, bottom left plot).  
+Overt signaling continues to fail to evolve at least some of the time
+for $r=0$ for moderate initial churlishness ($\rho_{ch,0}=0.5$) up up to perfect 
+assortment homophily, $w=0.5$.
+
+\subsection{Further analyses and robustness checks}
+
+There are a number of analyses that could be done to extend or check the 
+robustness of the results presented here. In this section we present some
+we deem most important and straightforward, and present more of these extensions
+and checks in the supplement.
+
+In this main text we present
+\begin{itemize}
+  \item Correlation between churlish receiving and covert signaling.
+  \item Case where $\delta \neq d$---that is, the penalty from collaboration
+    payoff is not $2d$ when both agents dislike one another, it is $d + \delta$.
+  \item We check the robustness of our conclusions regarding covert signaling
+    in minority populations by running our minority/majority
+    experiments with $K=9$ instead of $K=3$ as we had above.
+\end{itemize}
+
+% \bibliographystyle{apacite}
+
+% \setlength{\bibleftmargin}{.125in}
+% \setlength{\bibindent}{-\bibleftmargin}
+
+% \bibliography{/Users/mt/workspace/papers/library.bib}
+
+\appendix
+
+\section{Additional analyses}
+
+\subsection{Receiving strategy prevalence dynamics}
+
+Recall that in our experiments, when agents learn they may adopt a new signaling 
+strategy or receiving strategy.  In the main text we focused on covert 
+signaling prevalence as a function of homophily, disliking penalty, and 
+covert signaling efficiency. Here we support supplemental hypotheses about
+the churlish recieving prevalence dynamics: (1) increased homophily tends
+to increase the prevalence of churlish receivers; (2) churlish receiving
+will be selected against when the disliking penalty is higher; and,
+finally, (3) the prevalence of churlish receivers increases with 
+covert signaling efficiency.
+
+(EXPLAIN IN MORE DETAIL)
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/basic_disliking_receiving.pdf}
+    \caption{Density of covert signalers.}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/basic_receptivity_receiving.pdf}
+    \caption{Density of churlish receivers.}
+  \end{subfigure}
+
+  \caption{Density of covert signalers and churlish receivers at $t=200$, 
+    final timestep recorded in this preliminary experiment. Receptivity of
+    overt signals is $R=0.5$.}
+  \label{fig:receptivityHomophilyHeatmap}
+\end{figure}
+
 \subsubsection{Minority churlish receiving over homophily and disliking}
+
+In the main text we showed covert signaling is more prevalent in minority 
+populations than the majority for most, but not all, parameter settings. 
+Here we supplement this analysis by analyzing what conditions lead to
+churlish receiving in the minority. (Reason out how it would benefit minority
+agents to adopt churlish receiving).
 
@@
 
-\subsection{Covert signaling invasion}
+\subsection{Temporal dynamics and distribution of outcomes}
 
-In this experiment we begin with initial proportions, $\rho$ of one of the strategies
-at 0.05 and consider this the ``invading'' strategy. $\rho_{cov,0}$ represents
-the initial covert proportion, $\rho_{ov,0}$ the initial overt proportion,
-$\rho_{ch,0}$ the initial churlish proportion, and $\rho_{gen,0}$ the 
-initial generous proportion. We measure how often
-a non-zero proportion of agents with the invading strategy manage to 
-establish a permanent population, which we call invasion success. We calculated
-invasion success for a number of experimental parameter settings, covarying
-over disliking penalty ($d=\delta$) and homophily ($w$) in the first case,
-and over relative covert receptivity ($r/R$) and homophily ($w$) 
-in the second case (Figures~\ref{fig:cov-ov-invade} and~\ref{fig:ch-gen-invade}).
+To understand how the model works it is important to examine ensembles and
+means of time series for different parameter settings. In the results presented
+in the main text, all reported values were calculated using the final
+time step, where the time series had approximately reached equilibrium.
+We want to be sure that the model actually reaches equilibrium.
+
+We also want to know whether the mean of the outcomes is close to the
+median value of the outcomes. That is, if the mean
+final covert signaling prevalence is some value we want to be sure that
+this is more an estimate of a typical prevalence value, not a measure of 
+how often prevalence is either 0 or 1 at equilibrium.
+
+\subsubsection{Temporal dynamics}
 
@@
   \begin{subfigure}{0.49\textwidth}
-      \includegraphics[width=\textwidth]{Figures/covert_invades.pdf}
-      \caption{Covert invades, $\rho_{cov,0}=0.05$}
+    \includegraphics[width=\textwidth]{Figures/disliking_evo_d=0p1.pdf}
+  \caption{}
   \end{subfigure}
   \begin{subfigure}{0.49\textwidth}
-      \includegraphics[width=\textwidth]{Figures/overt_invades.pdf}
-      \caption{Overt invades, $\rho_{cov,0}=0.95$}
+    \includegraphics[width=\textwidth]{Figures/disliking_evo_d=0p4.pdf}
+  \caption{}
+  \end{subfigure} \\
+  \begin{subfigure}{0.49\textwidth}
+    \includegraphics[width=\textwidth]{Figures/disliking_evo_w=0p1.pdf}
+  \caption{}
   \end{subfigure}
-  \caption{Covert and overt sending strategy invasion success rates. 
-    Lower homophily is more favorable for successful covert signaling invasion.
-    This is due to lower homophily meaning agents cannot assort well into
-    similar pairs prior to interaction.
-    Similarly, greater homophily is more favorable for successful overt
-    signaling invasion, where agents can better assort if they know each other's
-    true traits. Unexpectedly, as covert receptivity increases, overt signaling
-    is is more successful at invading and covert signaling is less successful
-    at invading when the initial churlishness is high. When initial
-    churlishness is small to moderate, the pattern is reversed.
-  }
-  \label{fig:cov-ov-invade}
+  \begin{subfigure}{0.49\textwidth}
+    \includegraphics[width=\textwidth]{Figures/disliking_evo_w=0p4.pdf}
+  \caption{}
+  \end{subfigure}
+  \caption{Time series of communication strategy prevalences under different parameter settings
+  for homophily, $w$, and disliking penalty, $d$.}
+  \label{fig:}
 \end{figure}
@@
   \begin{subfigure}{0.49\textwidth}
+    \includegraphics[width=\textwidth]{Figures/receptivity_evo_r=0p1.pdf}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \includegraphics[width=\textwidth]{Figures/receptivity_evo_r=0p4.pdf}
+  \caption{}
+  \end{subfigure} \\
+  \begin{subfigure}{0.49\textwidth}
+    \includegraphics[width=\textwidth]{Figures/receptivity_evo_w=0p1.pdf}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+    \includegraphics[width=\textwidth]{Figures/receptivity_evo_w=0p4.pdf}
+  \caption{}
+  \end{subfigure}
+  \caption{Time series of communication strategy prevalences under different parameter settings
+  for homophily, $w$, and covert signaling efficiency, $E_{cov}$.}
+  \label{fig:}
+\end{figure}
+
+\subsubsection{Mean versus median outcomes}
+
+Here I want to examine
+\begin{enumerate}
+  \item Histograms of the final distribution of prevalences for a number of
+    parameter settings.
+  \item Show time series of a selection (e.g. 10 or 20) of trials for a number
+    of parameter settings to know that our averaged timeseries are showing
+  typical behavior, not probabilities of an extreme outcome, i.e. $\rho_s=0,1$.
+
+\end{enumerate}
+
+\subsection{$d \neq \delta$}
+
+Vary $\delta$ from 0 to $2d$.
+
+\subsection{Invasion of other strategies}
+
+In the main text we examined what conditions led to successful invasion of
+the covert signaling strategy. Here in the supplement we analyze what
+allows the other three strategies to invade: overt signaling, and churlish
+and generous receiving.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{Figures/overt_invades.pdf}
+  \caption{Overt invades, $\rho_{cov,0}=0.95$}
+  \label{fig:ov-invades}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    \begin{subfigure}{\textwidth}
       \includegraphics[width=\textwidth]{Figures/churlish_invades.pdf}
       \caption{Churlish invades, $\rho_{ch,0}=0.05$}
-    \end{subfigure}
-    \begin{subfigure}{0.49\textwidth}
+    \end{subfigure} \\
+    \begin{subfigure}{\textwidth}
       \includegraphics[width=\textwidth]{Figures/generous_invades.pdf}
@@
   }
-  \label{fig:ch-gen-invade}
+  \label{fig:ch-gen-invades}
 \end{figure}
 
-\subsubsection{Non-signaling as an adaptive strategy}
+\subsection{Different learning parameters}
 
-One of the most striking patterns in the invasion results is the evolution
-of a third de facto strategy of non-signaling. This strategy emerges when
-we consider both the invasion dynamics of either the covert or overt 
-signaling strategy. When simulating the invasion of covert signaling
-($\rho_{cov,0}=0.05$), the non-signaling strategy emerges when the covert
-signaling efficiency, $r$, is 0, but covert signaling still successfully
-invades as the chosen agent strategy. When $r=0$, no agents receive
-covert signals, making this more accurately a \emph{non-signaling} strategy.  
-For covert signaling invasion, this only happens when the initial churlishness
-is low ($\rho_{ch,0}=0.05$) and homophily is also low ($w \lessapprox 0.2$). 
-Non-signaling wins out evolutionarily 
-in some cases when considering of invading overt signalers when overt signalers
-fail to invade but $r=0$, again meaning agents in this society prefer not
-to signal at all. This occurs some of the time for all tested homophily
-values and low initial churlishness ($\rho_{ch,0}=0.05$) (Figure~\ref{fig:cov-ov-invade}b, bottom left plot).  
-Overt signaling continues to fail to evolve at least some of the time
-for $r=0$ for moderate initial churlishness ($\rho_{ch,0}=0.5$) up up to perfect 
-assortment homophily, $w=0.5$.
+In the main text we have set the learning parameters to be $\alpha=1.25$ and
+$\beta=12.0$. Setting $\alpha=1.25$ means that for there to be a 50\% chance
+of the learner to match its strategy with its teachers, the teacher's 
+accumulated payoff for that round must be 1.25 that of the learner's. This
+seems somewhat severe, and we imagine that a different adoption threshold values
+$\alpha$ could lead to different patterns in the spread of the covert signaling
+strategy. In this section we test $\alpha=1.0$ (TO BEGIN WITH THEN WE WILL TEST
+OTHER VALUES IF IT SEEMS VALUABLE TO DO SO).
 
-% \bibliographystyle{apacite}
+\subsection{Different number of interaction rounds per model iteration}
 
-% \setlength{\bibleftmargin}{.125in}
-% \setlength{\bibindent}{-\bibleftmargin}
-
-% \bibliography{/Users/mt/workspace/papers/library.bib}
-
-\appendix
-
-\section{Additional analyses}
-
-\subsection{Temporal dynamics}
-
-\subsection{Correlations between churlish receiving and covert signaling}
-
-\subsection{$d \neq \delta$}
-
-Vary $\delta$ from 0 to $2d$.
-
-\subsection{Minority dynamics}
-
-\subsubsection{More traits ($K=9$ and $M=4$) and different similarity threshold}
-
-\subsubsection{Varying minority group size}
-
-\subsection{Invasion of other strategies}
+One model iteration consists of a signalling round followed by $N_I$ interaction
+rounds in which agents are matched randomly into dyads then collaborate 
+with probability proportional to the attitudes each agent in the dyad has towards
+the other (Equation~\ref{eq:homophily}). In the main text, $N_I = 10$ for
+all experiments that generated the results we presented.
 

### 2020-06-24 id_signaling/model.py
implemented improved similarity calculation added to signal_and_receive and now used in calculate_payoff

@@ -107,6 +107,13 @@ class Model:
             for idx in range(N)
         ]
 
+        # Initialize similarity matrix of shape NxN to hold boolean
+        # indicating whether or not two agents are similar.
+        self.similar_matrix = np.zeros((N, N), dtype=bool)
+
+        # It is repetetive but convenient to create the full symmetric matrix.
+        self._init_similar_matrix()
+
         # Have a marker for the run() method if it should track majority/
         # minority agents over time so we can later recover their
         # proportional strategies.
@@ -152,6 +159,14 @@ class Model:
         self.prop_covert_series = np.array([_proportion_covert(self)])
         self.prop_churlish_series = np.array([_proportion_churlish(self)])
 
+    def _init_similar_matrix(self):
+        for a1 in self.agents:
+            for a2 in self.agents:
+
+                similarity = 1 - hamming(a1.traits, a2.traits)
+                similar = similarity >= self.similarity_threshold
+
+                self.similar_matrix[a1.index, a2.index] = similar
 
     def run(self, n_iter):
         '''
@@ -203,19 +218,19 @@ class Model:
 
     def _signal_and_receive(self):
 
-        for signaller_idx, signaller in enumerate(self.agents):
+        for signaler_idx, signaler in enumerate(self.agents):
 
             # Determine which of the two receiver proportions should be used.
             receive_prob = (
                 self.prob_overt_receiving
-                if signaller.signaling_strategy == "Overt" else
+                if signaler.signaling_strategy == "Overt" else
                 self.prob_covert_receiving
             )
 
             # Build a list of receivers who will observe the signal.
             receivers = (
                 other for other in self.agents
-                if (other != signaller) and (uniform() < receive_prob)
+                if (other != signaler) and (uniform() < receive_prob)
             )
 
             # TODO: implement signaling by focal `agent` and receiving by
@@ -229,29 +244,31 @@ class Model:
                 # and equal number of similar and dissimilar traits.
                 # XXX This can be calculated just once at init after
                 # traits have been set since traits don't change.
-                similarity = np.sum(receiver.traits * signaller.traits)
+                # similarity = np.sum(receiver.traits * signaler.traits)
+                similar = self._are_similar(signaler, receiver)
 
                 # If similarity is positive, attitude independent of signaling
                 # strategy...
-                if similarity > 0:
-                    receiver.attitudes[signaller_idx] = 1
+                # if similarity > 0:
+                if similar:
[…]

### 2020-06-24 test/test_model.py

@@ -42,24 +42,31 @@ def test_similarity_threshold():
     m = Model(similarity_threshold=0.5)
 
     # Set up some agents to be similar or dissimlar.
-    a1 = Agent(K=3)
-    a2 = Agent(K=3)
-    a3 = Agent(K=3)
+    a1 = Agent(K=3, agent_idx=0)
+    a2 = Agent(K=3, agent_idx=1)
+    a3 = Agent(K=3, agent_idx=2)
 
     a1.traits = np.array([1, 1, -1])
     a2.traits = np.array([1, 1, 1])
     a3.traits = np.array([1, -1, 1])
+
+    m.agents = [a1, a2, a3]
+    m._init_similar_matrix()
 
     assert m._are_similar(a1, a2)
     assert not m._are_similar(a1, a3)
     assert m._are_similar(a2, a3)
 
     m = Model(similarity_threshold=0.1)
+    m.agents = [a1, a2, a3]
+    m._init_similar_matrix()
     assert m._are_similar(a1, a2)
     assert m._are_similar(a1, a3)
     assert m._are_similar(a2, a3)
 
     m = Model(similarity_threshold=0.9)
+    m.agents = [a1, a2, a3]
+    m._init_similar_matrix()
     assert not m._are_similar(a1, a2)
     assert not m._are_similar(a1, a3)
     assert not m._are_similar(a2, a3)
@@ -69,12 +76,14 @@ def test_similarity_threshold():
 
     m = Model(similarity_threshold=0.5)
     # Set up some agents to be similar or dissimlar.
-    a1 = Agent(K=10)
-    a2 = Agent(K=10)
-    a3 = Agent(K=10)
+    a1 = Agent(K=10, agent_idx=0)
+    a2 = Agent(K=10, agent_idx=1)
+    a3 = Agent(K=10, agent_idx=2)
     a1.traits = np.array([1]*5 + [-1]*5)
     a2.traits = np.array([1]*10)
     a3.traits = np.array([-1]*4 + [1]*6)
+    m.agents = [a1, a2, a3]
+    m._init_similar_matrix()
 
     assert m._are_similar(a1, a2)
     assert m._are_similar(a2, a3)
@@ -120,6 +129,8 @@ def test_calculate_payoff():
     # Like/like. Only similar possible. Only one possible configuration.
     a0.traits = np.array([1, 1, -1])
     a1.traits = np.array([1, -1, -1])
+    model.agents = [a0, a1]
[…]

### 2020-06-24 sub_minority_experiments.sh
added to README note about directories for experiments; tolerance/diversity experiment sub script

@@ -1,25 +1,25 @@
 # NOTE r = 0.25 and R = 0.5 by default.
 
 
-# printf "\nSubmitting minority experiment with minority frac 0.05 experiment part 1\n"
-# fname=output_data/minority/0.05/part-`uuidgen`
-# subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
-#     -qfast.q -j$fname -n24 -t"04:00:00" -m0.05
+printf "\nSubmitting minority experiment with minority frac 0.05 experiment part 1\n"
+fname=output_data/minority/0.05/part-`uuidgen`
+subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+    -qfast.q -j$fname -n24 -t"04:00:00" -m0.05
 
-# printf "\nSubmitting minority experiment with minority frac 0.05 experiment part 2\n"
-# fname=output_data/minority/0.05/part-`uuidgen`
-# subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
-#     -qfast.q -j$fname -n24 -t"04:00:00" -m0.05
+printf "\nSubmitting minority experiment with minority frac 0.05 experiment part 2\n"
+fname=output_data/minority/0.05/part-`uuidgen`
+subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+    -qfast.q -j$fname -n24 -t"04:00:00" -m0.05
 
-# printf "\nSubmitting minority experiment with minority frac 0.10 experiment part 1\n"
-# fname=output_data/minority/0.10/part-`uuidgen`
-# subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
-#     -qfast.q -j$fname -n24 -t"04:00:00" -m0.10
+printf "\nSubmitting minority experiment with minority frac 0.10 experiment part 1\n"
+fname=output_data/minority/0.10/part-`uuidgen`
+subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+    -qfast.q -j$fname -n24 -t"04:00:00" -m0.10
 
-# printf "\nSubmitting minority experiment with minority frac 0.10 experiment part 2\n"
[…]

### 2020-06-24 sub_similarity_experiments.sh

@@ -1,33 +1,0 @@
-# * Set up simulations where agents are characterized by 10 
-#     binary traits (instead of 3). 
-# * Run simulations where "similarity" is defined as having at least X traits 
-#     in common, where X = {1, 2, 3, 4, ..., 10}. We should find here 
-#     that when X increases, we get more covert signaling. 
-# * Run new majority-minority dynamics using a threshold of 50% similar. Set 
-#     minority to be 10% of the population, where the first 4 traits are set to 
-#     zero, and one for the majority (so that minority individuals really need 
-#     to find each other). This will be a good confirmation of the trend we see 
-#     with 3 traits. 
-# * You can run all these with just one value of r/R and maybe 3 values of d.
-
-
-# Experiment 1: 
-
-# for similarity_threshold in 0.{1..9} 1.0; do
-
-#     fname=output_data/minority-similarity/$similarity_threshold/part-`uuidgen`
-#     subexp disliking 0.05:0.46:0.2 0.0:0.51:0.1 500 100 $fname.csv -R0.5  \
-#         -qfast.q -j$fname -n24 -t"04:00:00" -S$similarity_threshold -K10
-#         # -qstd.q -j$fname -n20 -t"04:00:00" -S$similarity_threshold -K10
-
-# done
-
-
-
-for i in {1..10}; do
-    fname=output_data/minority-similarity/minority/part-`uuidgen`
-    subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 10 $fname.csv -R0.5  \
-        --n_minmaj_traits=4 -K10 -m0.10 \
-        -qfast.q -j$fname -n24 -t"04:00:00" 
-        # -qstd.q -j$fname -n20 -t"04:00:00" --n_minmaj_traits=4 -K10
-done

### 2020-06-24 sub_tolerance_diversity_experiments.sh

@@ -1,0 +1,27 @@
+# Testing three values of K (cultural diversity) and ten similarity
+# thresholds. This requires thirty directories be created in total,
+# which can be done with commands
+# mkdir -p output_data/tolerance_diversity/0.{1..9}/"K="{10,15,20}/
+# mkdir -p output_data/tolerance_diversity/1.0/"K="{10,15,20}/
+
+for similarity_threshold in 0.{1..9} 1.0; do
+
+    fname=output_data/tolerance_diversity/$similarity_threshold/"K=10"/part-`uuidgen`
+    subexp disliking 0.05:0.46:0.2 0.0:0.51:0.1 500 100 $fname.csv -R0.5  \
+        -qfast.q -j$fname -n24 -t"04:00:00" -S$similarity_threshold -K10
+done
+
+
+for similarity_threshold in 0.{1..9} 1.0; do
+
+    fname=output_data/tolerance_diversity/$similarity_threshold/"K=15"/part-`uuidgen`
+    subexp disliking 0.05:0.46:0.2 0.0:0.51:0.1 500 100 $fname.csv -R0.5  \
+        -qfast.q -j$fname -n24 -t"04:00:00" -S$similarity_threshold -K15
+done
+
+for similarity_threshold in 0.{1..9} 1.0; do
+
+    fname=output_data/tolerance_diversity/$similarity_threshold/"K=20"/part-`uuidgen`
+    subexp disliking 0.05:0.46:0.2 0.0:0.51:0.1 500 100 $fname.csv -R0.5  \
+        -qfast.q -j$fname -n24 -t"04:00:00" -S$similarity_threshold -K20
+done

### 2020-06-27 id_signaling/experiment.py
success running tolerance/diversity and minority experiments with tolerance/diversity

@@ -86,7 +86,10 @@ def _one_trial(trial_tup, experiment, n_iter, **model_kwargs):
         initial_prop_churlish=[model.initial_prop_churlish]*n_tstep,
         prop_covert=model.prop_covert_series,
         prop_churlish=model.prop_churlish_series,
-        homophily=[homophily] * n_tstep
+        homophily=[homophily] * n_tstep,
+        K=[model.K] * n_tstep,
+        S=[model.similarity_threshold] * n_tstep,
+        M=[model.n_minmaj_traits] * n_tstep
     )
 
     minority_trait_frac = model_kwargs['minority_trait_frac']

### 2020-06-27 id_signaling/model.py

@@ -23,7 +23,7 @@ class Model:
                  homophily=0.25, random_seed=None, similarity_threshold=0.5,
                  minority_trait_frac=None,
                  initial_prop_covert=0.5, initial_prop_churlish=0.5,
-                 n_minmaj_traits=1,  # only used if minority_trait_frac ! None
+                 n_minmaj_traits=None,  # only used if minority_trait_frac ! None
                  evo_logistic_loc=1.25, evo_logistic_scale=12):
         '''
         Arguments:
@@ -73,6 +73,10 @@ class Model:
         self.evo_logistic_loc = evo_logistic_loc
         self.evo_logistic_scale = evo_logistic_scale
 
+        if n_minmaj_traits is None:
+            n_minmaj_traits = K - ((K+1) // 2)
+        self.n_minmaj_traits = n_minmaj_traits
+
         self.initial_prop_covert = initial_prop_covert
         self.initial_prop_churlish = initial_prop_churlish
 
@@ -86,12 +90,16 @@ class Model:
         n_initial_covert = int(N * initial_prop_covert)
         n_initial_overt = N - n_initial_covert
 
+        # Create array of receiving strategies and randomize to vector-assign
+        # to agents for initialization.
         rec_strategies = (
             ['Churlish'] * n_initial_churlish +
             ['Generous'] * n_initial_generous
         )
         np.random.shuffle(rec_strategies)
 
+        # Create array of signaling strategies and randomize to vector-assign
+        # to agents for initialization.
         sig_strategies = (
             ['Covert'] * n_initial_covert +
             ['Overt'] * n_initial_overt

### 2020-06-27 id_signaling/scripts/runner.py

@@ -33,8 +33,7 @@ def basic_decorator():
             click.option('--initial_prop_churlish', type=float, default=0.5),
             click.option('--num_traits', '-K', type=int, default=3),
             click.option('--similarity_threshold', '-S', type=float,
-                         default=0.5),
-            click.option('--n_minmaj_traits', type=int, default=1)
+                         default=0.5)
        )
 
 
@@ -43,7 +42,7 @@ def basic_decorator():
 def run(experiment, param_vals, homophily_vals, n_iter, n_trials,
         output_file, prob_overt_receiving, minority_trait_frac,
         initial_prop_covert, initial_prop_churlish, num_traits,
-        similarity_threshold, n_minmaj_traits):
+        similarity_threshold):
 
     # XXX Hack to deal with subexp throwing error I don't understand that
     # minority_trait_frac can't be None (the default) because it's not a
@@ -63,7 +62,6 @@ def run(experiment, param_vals, homophily_vals, n_iter, n_trials,
                              initial_prop_covert=initial_prop_covert,
                              initial_prop_churlish=initial_prop_churlish,
                              K=num_traits, similarity_threshold=similarity_threshold,
-                             n_minmaj_traits=n_minmaj_traits
                              )
 
     out_df.to_csv(output_file, index=False)
@@ -80,7 +78,7 @@ def sub(
             experiment, param_vals, homophily_vals, n_iter, n_trials,
             output_file, prob_overt_receiving, minority_trait_frac,
             initial_prop_covert, initial_prop_churlish, num_traits,
-            similarity_threshold, n_minmaj_traits,
+            similarity_threshold,
             queue, ncpu, wall_time, dry_run, job_name  # SLURM OPTS
         ):
     """

### 2020-06-27 sub_basic_experiments.sh

@@ -1,21 +1,21 @@
 
 printf "\nSubmitting basic disliking experiment part 1\n"
 fname=output_data/basic/disliking/part-`uuidgen`
-subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 1000 50 $fname.csv -R0.5  \
     -qfast.q -j$fname -n24 -t"04:00:00"
 
 printf "\nSubmitting basic disliking experiment part 2\n"
 fname=output_data/basic/disliking/part-`uuidgen`
-subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 1000 50 $fname.csv -R0.5  \
     -qfast.q -j$fname -n24 -t"04:00:00"
 
 
 printf "\nSubmitting basic receptivity experiment part 1\n"
 fname=output_data/basic/receptivity/part-`uuidgen`
-subexp receptivity 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+subexp receptivity 0.0:0.51:0.05 0.0:0.51:0.05 1000 50 $fname.csv -R0.5  \
     -qfast.q -j$fname -n24 -t"04:00:00"
 
 printf "\nSubmitting basic receptivity experiment part 2\n"
 fname=output_data/basic/receptivity/part-`uuidgen`
-subexp receptivity 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+subexp receptivity 0.0:0.51:0.05 0.0:0.51:0.05 1000 50 $fname.csv -R0.5  \
     -qfast.q -j$fname -n24 -t"04:00:00"

### 2020-06-27 sub_minority_experiments.sh

@@ -1,92 +1,20 @@
 # NOTE r = 0.25 and R = 0.5 by default.
 
+for K in 3 9; do #5 9 15; do # 21; do
+    for similarity_threshold in 0.{1..9} 1.0; do 
+        # for minority_trait_frac in 0.05 0.10 0.15 0.20 0.25 0.30 0.35 0.40 0.45; do
+        for minority_trait_frac in 0.10 0.20; do  # 0.25 0.30 0.35 0.40 0.45; do
 
-printf "\nSubmitting minority experiment with minority frac 0.05 experiment part 1\n"
-fname=output_data/minority/0.05/part-`uuidgen`
-subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
-    -qfast.q -j$fname -n24 -t"04:00:00" -m0.05
+            fname=output_data/minority_supp/$minority_trait_frac/part-`uuidgen`
+            subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+                -qfast.q -j$fname -n24 -t"04:00:00" -m$minority_trait_frac \
+                -K$K -S$similarity_threshold 
 
-printf "\nSubmitting minority experiment with minority frac 0.05 experiment part 2\n"
-fname=output_data/minority/0.05/part-`uuidgen`
-subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
-    -qfast.q -j$fname -n24 -t"04:00:00" -m0.05
+            fname=output_data/minority_supp/$minority_trait_frac/part-`uuidgen`
+            subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+                -qfast.q -j$fname -n24 -t"04:00:00" -m$minority_trait_frac \
+                -K$K -S$similarity_threshold 
 
-printf "\nSubmitting minority experiment with minority frac 0.10 experiment part 1\n"
-fname=output_data/minority/0.10/part-`uuidgen`
-subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
-    -qfast.q -j$fname -n24 -t"04:00:00" -m0.10
-
[…]

### 2020-06-27 sub_tolerance_diversity_experiments.sh

@@ -4,24 +4,12 @@
 # mkdir -p output_data/tolerance_diversity/0.{1..9}/"K="{10,15,20}/
 # mkdir -p output_data/tolerance_diversity/1.0/"K="{10,15,20}/
 
-for similarity_threshold in 0.{1..9} 1.0; do
 
-    fname=output_data/tolerance_diversity/$similarity_threshold/"K=10"/part-`uuidgen`
-    subexp disliking 0.05:0.46:0.2 0.0:0.51:0.1 500 100 $fname.csv -R0.5  \
-        -qfast.q -j$fname -n24 -t"04:00:00" -S$similarity_threshold -K10
-done
+for K in 3 5 9 15 21; do
+    for similarity_threshold in 0.{1..9} 1.0; do
 
-
-for similarity_threshold in 0.{1..9} 1.0; do
-
-    fname=output_data/tolerance_diversity/$similarity_threshold/"K=15"/part-`uuidgen`
-    subexp disliking 0.05:0.46:0.2 0.0:0.51:0.1 500 100 $fname.csv -R0.5  \
-        -qfast.q -j$fname -n24 -t"04:00:00" -S$similarity_threshold -K15
-done
-
-for similarity_threshold in 0.{1..9} 1.0; do
-
-    fname=output_data/tolerance_diversity/$similarity_threshold/"K=20"/part-`uuidgen`
-    subexp disliking 0.05:0.46:0.2 0.0:0.51:0.1 500 100 $fname.csv -R0.5  \
-        -qfast.q -j$fname -n24 -t"04:00:00" -S$similarity_threshold -K20
+        fname=output_data/tolerance_diversity/$similarity_threshold/"K=$K"/part-`uuidgen`
+        subexp disliking 0.05:0.46:0.2 0.0:0.51:0.1 500 100 $fname.csv -R0.5  \
+            -qfast.q -j$fname -n24 -t"04:00:00" -S$similarity_threshold -K$K
+    done
 done

### 2020-06-27 sub_minority_missing.sh
updates to README and script to sub missing minority trials

@@ -1,0 +1,34 @@
+##
+# Script to run missing parameter settings for previous minority experiment.
+# Date: 6/27/20
+#
+
+# Submit missing trials for K=3, rho_minor=0.1.
+for similarity_threshold in 0.3 0.4 0.5; do
+    K=3
+    minority_trait_frac=0.1
+    fname=output_data/minority_supp/$minority_trait_frac/part-`uuidgen`
+    subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+        -qfast.q -j$fname -n24 -t"04:00:00" -m$minority_trait_frac \
+        -K$K -S$similarity_threshold 
+done
+
+# Submit missing trials for K=3, rho_minor=0.2.
+for similarity_threshold in 0.3 0.5 0.7; do
+    K=3
+    minority_trait_frac=0.2
+    fname=output_data/minority_supp/$minority_trait_frac/part-`uuidgen`
+    subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+        -qfast.q -j$fname -n24 -t"04:00:00" -m$minority_trait_frac \
+        -K$K -S$similarity_threshold 
+done
+
+# Only one failed for K=9 across both similarity thresholds; no need to loop.
+K=9
+similarity_threshold=0.4
+minority_trait_frac=0.2
+
+fname=output_data/minority_supp/$minority_trait_frac/part-`uuidgen`
+subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+    -qfast.q -j$fname -n24 -t"04:00:00" -m$minority_trait_frac \
+    -K$K -S$similarity_threshold 

### 2020-06-28 id_signaling/figures.py
first analysis of minority/tolerance exposed a bug; fixed, now to re-run

@@ -450,7 +450,14 @@ def covert_vs_minority_frac(minority_dfs, dislikings, homophily,
 def similarity_threshold(dfs, thresholds=np.arange(0.1, 1.1, 0.1),
                          dislikings=[0.05, 0.25, 0.45], homophily=0.2,
                          ax=None, savefig_path=None, ylow=0.2, yhigh=1.0,
-                         legend=False, xlabel=True, ylabel=True):
+                         legend=False, xlabel=True, ylabel=True,
+                         minority_majority=None):
+    '''
+
+    Arguments:
+        minority_majority (str): Either 'minority' or 'majority', or None by
+            default if this is not a majority/minority test.
+    '''
 
     if ax is None:
         fig, ax = plt.subplots(figsize=(5, 4))

### 2020-06-28 id_signaling/model.py

@@ -115,13 +115,6 @@ class Model:
             for idx in range(N)
         ]
 
-        # Initialize similarity matrix of shape NxN to hold boolean
-        # indicating whether or not two agents are similar.
-        self.similar_matrix = np.zeros((N, N), dtype=bool)
-
-        # It is repetetive but convenient to create the full symmetric matrix.
-        self._init_similar_matrix()
-
         # Have a marker for the run() method if it should track majority/
         # minority agents over time so we can later recover their
         # proportional strategies.
@@ -167,6 +160,14 @@ class Model:
         self.prop_covert_series = np.array([_proportion_covert(self)])
         self.prop_churlish_series = np.array([_proportion_churlish(self)])
 
+        # Initialize similarity matrix of shape NxN to hold boolean
+        # indicating whether or not two agents are similar.
+        self.similar_matrix = np.zeros((N, N), dtype=bool)
+
+        # It is repetetive but convenient to create the full symmetric matrix.
+        self._init_similar_matrix()
+
+
     def _init_similar_matrix(self):
         for a1 in self.agents:
             for a2 in self.agents:
@@ -194,10 +195,10 @@ class Model:
 
             self._evolve()
 
-            self.prop_covert_series= np.append(
+            self.prop_covert_series = np.append(
                 self.prop_covert_series, _proportion_covert(self)
             )
-            self.prop_churlish_series= np.append(
+            self.prop_churlish_series = np.append(
                 self.prop_churlish_series, _proportion_churlish(self)
             )
 

### 2020-06-29 paper/ms.tex
finished minority/'tolerance' (similarity thresh) experiments and draft writeup

@@
 \usepackage[bookmarks]{hyperref}
+\hypersetup{
+    colorlinks=true,
+    allcolors=cyan
+}
 \usepackage{amssymb,amsmath}
@@
 
-\section{Introduction}
-
-When we interact with others it is often to mutually benefit from the
-exchange. For instance, we shop at a store to buy things we want from one or
-a group of people who want to do the hard work of shopkeeping. When we are
-dissimilar from those with whom we interact, the benefit can be lessened.
-For instance, you might be wearing a shirt with a political slogan and 
-the shopkeeper has posted signs boasting their political affiliation. Perhaps
-the shopkeeper decides to charge you more, or perhaps you feel a sense of 
-resentment for giving money to someone with whom you disagree politically;
-maybe the shopkeeper's signage distracted you from making all the purchases 
-you needed to make. Shopping is rather inconsequential, but illustrates the issue. 
-A much more critical situation is the interaction of political partisans, who
-must mutually benefit one another for democracy to work.
-
-In response to the fact that
-interpersonal disliking often lowers payoffs from interaction, humans have
-developed \emph{covert signaling} strategies so that, e.g.,
-customer and shopkeeper can signal their political affiliations so that like-minded
-people will know they are similar, but dissimilar others will be unaware
-of political or identity signaling at all. Different social settings present
-different signaling pressures. Sometimes it is possible to choose who we assort
-with for interaction, which means the practice of homophily---selectively
-interacting with similar others---is widespread. In that case, there is little
-reason to signal covertly because we can preferentially 
-interact with similar others, avoiding penalties for interaction with 
-dissimilar others. Sometimes the penalties for
-disliking one another are very high, which pressures individuals to choose
-covert signaling more often in order to not be disliked. While there are
-interaction costs for dislike there are benefits for the case where two, which are
-also included in the model.
-
-Here we present a model of identity signaling, social interaction,
-and social learning to identify mechanisms for the evolution of the covert 
-signaling strategy, as opposed to an overt signaling strategy. The precise 
-definitions of overt and covert signaling are given in the Model section.
-Our results are thus predictions of when covert signaling will or
-will not evolve. This depends on a number of model parameters and the 
-co-evolution of the \emph{receiving} strategy, which may be either \emph{generous}
-or \emph{churlish}. Generous individuals do not dislike
-others with whom they have not previously interacted. Churlish individuals 
-dislike others with whom they have not previously interacted.
-
-The model predicts that covert signaling evolves when homophily is low (agents
-do not efficiently assort) and the costs of disliking are high. The model also 
-predicts that covert signaling co-evolves with generous receiving. This is due
-to the fact that covert signalers are simply ignored by those with whom
-they are different. If most of the individuals are churlish receivers, there is
-no benefit to being unknown since most individuals dislike unknown others. 
-We also use our model to predict differences in covert signaling prevalence
-among minority and majority populations, where the minority and majority all
-share the same in-group traits along a number of trait dimensions, but exactly
-the opposite traits. If homophily is weak and disliking costs are high, the
-minority will tend to become covert signalers. However, if homophily is
-sufficiently high it is better for the minority to overtly signal so they can
-efficiently identify similar interaction partners. We close by finding the
-conditions that promote either signaling or receiving strategies to ``invade'',
-i.e.\ become prevalent after starting as just a small fraction of the population.
-We find here that sometimes no signaling is better than overt signaling: 
-covert signaling can evolve even when the efficiency of covert signaling is
-zero, i.e.\ covert signals are not understood by any model individuals (agents).
+\begin{abstract}
+    This document is a snapshot of the Model and Results sections outline.
+    It is very much a work in progress. I believe there is enough information 
+    for it to be valuable to share, and there are two important new results
+    I try to explain in the Results section. The Appendix is just basically
+    an outline. In many cases there are old results in there serving as
+    placeholders. I tried to note where old data was being presented and
+    make notes on where supplemental analyses need to go. I will be taking
+    care of this in the coming days.
+
+    The Model section is a first
+    draft just past outline stage. I think it has all the model elements, but 
+    needs a lot of work. Note that I split the ``interaction'' stage into
+    the random ``matching'' stage and then 
+    a dyad reaches the ``collaboration'' stage with probability
+    given in Equation~\ref{eq:collaborationProbability}. 
+    If you see any big problems please let me know. 
+    Otherwise I will hopefully catch more issues on revision and expansion.
+
+    \textbf{The most important new results are} 
+    \begin{enumerate}
+        \item Complex dependence of covert signaling prevalence $\rho_{cov}$ on
+            the similarity threshold ($S$), homophily ($w$),
+            and the disliking penalty ($d$)
+            (Figures~\ref{fig:covertAndSimilarity} and~\ref{fig:overtAndSimilarity}).
+            In some cases where $w$ and $S$ are large, increased $S$ 
+            favors \emph{overt}, not covert, signaling. For small $K$ this
+            relationhsip is monotonic. For larger $K$, $\rho_{cov}$ decreases
+            for a while with $S$, but then shoots up to $\rho_{cov}=1$ at
+            some critical value of $S$. Full results from these ``similarity 
+            experiments'' are given across three pages in the
+            Appendix/Supplement, Figure~\ref{fig:similarity_supp}.
+        \item Covert signaling in minority/majority populations also showed a
+            complex relationship with $S$, $K$, $w$, and $d$. The latest results
+            show the primary thing we want to show in many cases: that 
+            increased disliking cost leads to increased covert signaling, and
+            that covert signaling is further preferred when $K=9$ and $M=4$.
+            Furthermore,
+            \begin{itemize}
+                \item When homophily is large enough, the \emph{majority}
+                    covert signals more than the minority.
+                \item Increasing minority prevalence $\rho^{minor}$ decreases
+                    the prevalence of covert signaling in the minority 
+                    population overall.
+                \item When similarity is high ($S=0.8$), covert signaling
+                    dominates in the minority population for high enough
+                    levels of homophily. This is so that they have a better
+                    chance of collaborating with a majority member to at least
+                    get \emph{some} payoff---when homophily is high, an overt
+                    signaling minority agent may have a harder time successfully
+                    collaborating with a majority partner.
+                \item When similarity threshold is small ($S=0.3$), 
+                    there is little difference between minority and majority 
+                    strategy prevalence, as expected (WILL GO IN SUPPLEMENT,
+                    NOT THERE YET).
+            \end{itemize}
+
+    \end{enumerate}
+
+    The Results section is in rough shape, basically an outline. I tried to
+    clear out some garbage, but there is still a bit left that I will
+    expand on and shape up.
+
+    Please see the Model section tables for default parameter values. If I 
+    failed to list the value of a parameter in the main text I will likely 
+    catch it in a future iteration. If something is very confusing please
+    just contact me and we can have a look together. Hopefully we can clear 
+    things up over a video call/screen share Tuesday.
+
+    If there are no results or text in a given section that means I have not
+    done that analysis/experiment yet. Notably, I have not yet done the case
+    where $d \neq \delta$ and I have not performed improved 
+    correlational analyses between signaling and receiving strategies.
+
+    We are currently getting underwhelming results for the invasion experiments.
+    I think one thing that might improve this is to lower $\alpha$ in the
+    learning rule from $\alpha=1.25$ to $\alpha=1.0$. This would encourage more
+    ``exploration'' of strategies that are as good as an agents current one
+    and boost the chances that an agent will adopt a better-performing alternative
+    strategy. I could imagine that with the current setting a better-performing
+    alternative is not catching on due to our cautious updating assumption
+    with $\alpha=1.25$. This could have a big effect on other results, and
+    I think this is one of the primary further analyses we should pursue.
+
+    Another sensitivity analysis would be to see what happens in minority 
+    experiments (and others) when the population is increased from 100, 
+    perhaps $N=200,500,1000$.
+\end{abstract}
+
+\tableofcontents
+\listoffigures
+\listoftables
+
+% \section{Introduction}
+
+% When we interact with others it is often to mutually benefit from the
+% exchange. For instance, we shop at a store to buy things we want from one or
+% a group of people who want to do the hard work of shopkeeping. When we are
+% dissimilar from those with whom we interact, the benefit can be lessened.
+% For instance, you might be wearing a shirt with a political slogan and 
+% the shopkeeper has posted signs boasting their political affiliation. Perhaps
+% the shopkeeper decides to charge you more, or perhaps you feel a sense of 
+% resentment for giving money to someone with whom you disagree politically;
+% maybe the shopkeeper's signage distracted you from making all the purchases 
+% you needed to make. Shopping is rather inconsequential, but illustrates the issue. 
+% A much more critical situation is the interaction of political partisans, who
+% must mutually benefit one another for democracy to work.
+
+% In response to the fact that
+% interpersonal disliking often lowers payoffs from interaction, humans have
+% developed \emph{covert signaling} strategies so that, e.g.,
+% customer and shopkeeper can signal their political affiliations so that like-minded
+% people will know they are similar, but dissimilar others will be unaware
+% of political or identity signaling at all. Different social settings present
+% different signaling pressures. Sometimes it is possible to choose who we assort
+% with for interaction, which means the practice of homophily---selectively
+% interacting with similar others---is widespread. In that case, there is little
+% reason to signal covertly because we can preferentially 
+% interact with similar others, avoiding penalties for interaction with 
+% dissimilar others. Sometimes the penalties for
+% disliking one another are very high, which pressures individuals to choose
+% covert signaling more often in order to not be disliked. While there are
+% interaction costs for dislike there are benefits for the case where two, which are
+% also included in the model.
+
+% Here we present a model of identity signaling, social interaction,
+% and social learning to identify mechanisms for the evolution of the covert 
+% signaling strategy, as opposed to an overt signaling strategy. The precise 
+% definitions of overt and covert signaling are given in the Model section.
+% Our results are thus predictions of when covert signaling will or
+% will not evolve. This depends on a number of model parameters and the 
+% co-evolution of the \emph{receiving} strategy, which may be either \emph{generous}
+% or \emph{churlish}. Generous individuals do not dislike
+% others with whom they have not previously interacted. Churlish individuals 
+% dislike others with whom they have not previously interacted.
+
+% The model predicts that covert signaling evolves when homophily is low (agents
+% do not efficiently assort) and the costs of disliking are high. The model also 
+% predicts that covert signaling co-evolves with generous receiving. This is due
+% to the fact that covert signalers are simply ignored by those with whom
+% they are different. If most of the individuals are churlish receivers, there is
+% no benefit to being unknown since most individuals dislike unknown others. 
+% We also use our model to predict differences in covert signaling prevalence
+% among minority and majority populations, where the minority and majority all
+% share the same in-group traits along a number of trait dimensions, but exactly
+% the opposite traits. If homophily is weak and disliking costs are high, the
+% minority will tend to become covert signalers. However, if homophily is
+% sufficiently high it is better for the minority to overtly signal so they can
+% efficiently identify similar interaction partners. We close by finding the
+% conditions that promote either signaling or receiving strategies to ``invade'',
+% i.e.\ become prevalent after starting as just a small fraction of the population.
+% We find here that sometimes no signaling is better than overt signaling: 
+% covert signaling can evolve even when the efficiency of covert signaling is
+% zero, i.e.\ covert signals are not understood by any model individuals (agents).
 
@@
     \toprule 
-    $w$      & \emph{Homophily}, the ability of agents to preferentially interact with similar others & $\{0.0, 0.05, 0.10, \ldots, 0.5\}$ \\
+    $w$      & \emph{Homophily}, the ability of agents to preferentially interact with similar others & $\{0.0, 0.05, 0.1,\ldots \mathbf{0.25}, \ldots, 0.5\}$\\
     $d$      & \emph{Disliking penalty} imposed when one agent dislikes the other & $\{0.0, 0.05, 0.1,\ldots \mathbf{0.25}, \ldots, 0.5\}$ \\
@@
     $s$      & \emph{Similarity benefit} received by similar interacting pair & \textbf{0.25} \\
-    $K$      & Number of agent identity traits & $\{\mathbf{3}, 9\}$ \\
+    $K$      & Number of agent identity traits & $\{\mathbf{3}, 5, 9, 15, 21\}$ \\
     $S$      & Minimum fraction of traits in common for a pair to be considered similar & 
       $\{0.1, 0.2, \ldots, \mathbf{0.5}, \ldots, 1.0\}$\\
-    $M$      & \emph{Number of minority/majority traits} used to define majority/minority populations & $\{\mathbf{2}, 4\}$\\
-    $R$      & \emph{Number of interaction rounds} following a signaling round \\
+    $M$      & \emph{Number of minority/majority traits} used to define majority/minority populations & $\{\mathbf{1}, 4\}$\\
+    $N_I$      & \emph{Number of interaction rounds} following a signaling round & \textbf{10} \\
     $\alpha$ & Threshold payoff multiplier to give learner 50\% chance of 
-               adopting teacher's strategy \\
+        adopting teacher's strategy & \textbf{1.25}\\
     $\beta$  & Factor that, as it increases, both lowers chance of learner 
@@
                raises chance of learner adopting teacher strategy when 
-               $\pi_{teach}/\pi_{learn} > \alpha$.
+               $\pi_{teach}/\pi_{learn} > \alpha$. & \textbf{12.0}
   \end{tabular}
@@
         if signaler and receiver are not sufficiently similar. 
-      \item Recall agents are similar in our model if their inter-agent
+      \item Recall agents are similar in our model if their similarity measure
+          (Equation~\ref{eq:similarity}) is greater than the similarity
+          threshold $S$, set to 0.5 in the default case.
     \end{itemize}
@@
 
+(FIGURES ARE CURRENT, BUT TEXT IS OLD OUTLINE TEXT; NEED TO UPDATE)
+
 Our first task is to support our basic hypotheses that, other
@@
 
-Theoretically, conditions favorable for covert
-signalers should also be favorable for generous receivers (TRUE??). Furthermore, 
-an increase in covert signalers increases the pressure towards generous receiving.
-With many covert signalers it is likely an agent will get no signal on a 
-turn because they were receiving a signal from a covert signaler. Disliking
-incurs a penalty, so it is better to remain neutral.
+(DID NOT YET GET TO RE-DO CORRELATIONS AND WRITE THIS SECTION)
+
+% Theoretically, conditions favorable for covert
+% signalers should also be favorable for generous receivers (TRUE??). Furthermore, 
+% an increase in covert signalers increases the pressure towards generous receiving.
+% With many covert signalers it is likely an agent will get no signal on a 
+% turn because they were receiving a signal from a covert signaler. Disliking
+% incurs a penalty, so it is better to remain neutral.
 
@@
 
-\subsubsection{Covert signaling is favored in less tolerant and more diverse societies}
-
-(THIS PART REQUIRES NEW EXPERIMENTS. These need to be explained in Model 
-  section. Below I am just writing a paragraph for myself to guide the 
-experiment.)
+\subsubsection{Complex relationship between similarity threshold, homophily, and covert signaling}
+
+(BELOW IS PRELIMINARY/OUTLINE TEXT TO UPDATE)
 
@@
 
-\subsubsection{Covert signaling is favored among minority groups}
+We found that covert signaling is indeed sensitive to the similarity threshold, 
+$S$. In most cases, increased $S$ leads to increased covert signaling
+prevalence. However, when homophily is high, increased $S$ leads to increased
+\emph{overt}, not covert, signaling prevalence. This is understandable by
+considering the interaction process composed of two phases, matching and
+collaboration. Matching is totally random---all 100 agents are paired into
+50 random dyads. Collaboration occurs probabilistically with the chance of
+collaboration increasing with the attitudes each agent has towards the other.
+
+To understand why overt signaling is sometimes favored over covert signaling,
+consider the default situation, which we used in our
+computational experiments. Covert signaling is
+half as efficient than overt signaling, which is set to $E_{ov} = 2E_{cov} = 0.5$. 
+Recall this means that when an agent signals, half of all other agents receive
+an overt signal and one quarter receive a covert signal. Say a dyad is formed
+where the agents are similar, but covert signalers and generous receivers
+so they each have an attitude of 0 about the other, $a_{ij} = a_{ji} = 0$. 
+There is a high probability that both agents do not get a signal about the other
+in a given round of communication: $\frac{1}{4} \cdot \frac{1}{4} = \frac{1}{16}$.
+The probability of collaboration is $\frac{1}{2}$ in this situation 
+(Equation~\ref{eq:homophily}). If instead both agents were 
+overt signalers the chance they like one another is $\frac{1}{4}$ and if
+$w=0.5$ they are guaranteed to collaborate and reap a payoff of $1 + s$. 
+If just one likes the other, the chance they collaborate is $\frac{3}{4}$
+instead of $\frac{1}{2}$. There is a much higher chance of payoff if agents
+know they like one another. We will see that this same pattern is inverted for
+minority group agents when homophily is high so that they have a fighting chance to
+get a payoff with a majority group agent they would likely be matched with.
+
+What to show with figures
+\begin{itemize}
+  \item In most all cases, when the similarity threshold reaches a large enough 
+    value, covert signaling dominates. Exception is $K=3$ and $K=5$ with 
+    $w=0.5$. When homophily is not maximal ($w \leq 0.4$) an increased 
+    similarity threshold tends to increase covert signaling prevalence. 
+    We consider $w=0.5$ and other select exceptions to this pattern later; 
+    for now, we focus on showing this general trend of increased covert signaling
+    with increased similarity (Figure~\ref{fig:covertAndSimilarity}).
+  \item Unexpectedly, for moderately high levels of $S$ and high $w$, overt signaling is
+    favored. As showed in previous result this goes away when $S$ gets to
+    maximal values. However, for maximal $S=1.0$ and $w=0.5$ covert signaling
+    does not come to dominate. When $K=3$, overt signaling becomes more
+    preferred when $S$ goes from $0.5$\footnote{For $K=3$, $S=0.5$ is equivalent
+        to $S=0.4$ and $S=0.6$---all refer to the situation where a pair matches
+    two of three traits. For $K=5$, $S=0.5$ is only equivalent to $S=0.6$.}
+    to $0.8$. For $K=5$, covert signaling prevalence recovers somewhat going
+    from $S=0.7,0.8$ to $S=0.9,1.0$ (Figure~\ref{fig:overtAndSimilarity}).
+  \item Worthwhile to note that when the disliking penalty is high and $S$ is low, 
+      overt signaling is weakly favored for $w=0.3$. There also seems to be a
+      weak effect at $w=0.4$ that is like dominance of overt signaling for
+      moderate-high $S$ with maximal $w=0.5$.
+      (GIVE DETAILS IN SUPPLEMENT \ref{fig:similarity_supp}) 
+\end{itemize}
+
+\begin{figure}
+  \centering
+  \large{Low to moderate homophily, $w=0.2$}
+  \includegraphics[width=0.8\textwidth]{Figures/similarity/similarity_low_medium_S_homophily.pdf}
+  \caption{When homophily is low to moderate ($0.0 \leq w \leq 0.3$), covert signaling
+  prevalence increases monotonically with similarity threshold, $S$.}
+  \label{fig:covertAndSimilarity}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \large{High homophily, $w=0.5$}
+  \includegraphics[width=0.8\textwidth]{Figures/similarity/similarity_high_S_homophily.pdf}
+  \caption{
+      When homophily is maximal ($w=0.5$) and $K$ is small (top row,
+      $K=3$ and $K=5$), covert signaling
+      prevalence is \emph{negatively} correlated with increased similarity 
+      threshold, meaning larger $S$ favors \emph{overt}, not covert signaling. 
+      This also occurs for maximal homophily and larger values of $K$, but 
+      only to a point (bottom row). For larger values of $K$, $\rho_{cov}$
+      decreases at first with $S$, but then undergoes a sudden transition to
+      $\rho_{cov} \approx 1.0$.
+  }
+  \label{fig:overtAndSimilarity}
+\end{figure}
+
+\subsubsection{Evolution of signaling strategy in minority and majority groups}
 
@@
 
-By setting $K$ and $M$ to these two values we test two different social
-situations: in the first, $K=3$ and $M=1$, it is relatively easier for two binary traits
-to match (1/4 probability) than the second case, 
-with $K=9$ and $M=4$ where five binary traits must match (1/32 probability).
-Our current results show \dots
-Figure~\ref{fig:covert-signaling-minority-heatmap}.
-
-\subsubsection{Covert minority signaling over minority prevalence}
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.48\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{Figures/covert_signalers_diff_0p05.pdf}
-    % \caption{Prevalence of minority covert receivers; $\rho^{minor} = 0.10$.}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{0.48\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{Figures/covert_signalers_diff_0p10.pdf}
-    % \caption{Prevalence of minority covert receivers; $\rho^{minor} = 0.25$.}
-  \end{subfigure} \\[.25in]
-  \begin{subfigure}{0.48\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{Figures/covert_signalers_diff_0p25.pdf}
-    % \caption{Prevalence of minority churilsh receivers; $\rho^{minor} = 0.10$.}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{0.48\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{Figures/covert_signalers_diff_0p10_K=10_M=4.pdf}
-    \caption{(NEED TO UPDATE WITH K=9 AND M=4. Ran these, just need to pull from
-    MERCED and analyze.)}
-  \end{subfigure}
-  \caption{Difference in covert signaling prevalence between minority and
-  majority populations for different parameters settings.}
-  \label{fig:covert-signaling-minority-heatmap}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.31\textwidth}
-    \includegraphics[width=\textwidth]{Figures/minority-homophily=0p05.pdf}
-    \caption{}
-  \end{subfigure}
-  \begin{subfigure}{0.31\textwidth}
-    \includegraphics[width=\textwidth]{Figures/minority-homophily=0p25.pdf}
-    \caption{}
-  \end{subfigure}
-  \begin{subfigure}{0.31\textwidth}
-    \includegraphics[width=\textwidth]{Figures/minority-homophily=0p45.pdf}
-    \caption{}
-  \end{subfigure}
-  \caption{}
-\end{figure}
+We found (SUPPORTED BY FIGURES)\dots
+\begin{itemize}
+    \item Basic results (FIRST FIGURE)
+        \begin{itemize}
+          \item High levels of homophily and low costs for disliking favor 
+              decreased covert signaling prevalence among minority for 
+              $S=0.5$ (Figures: all conditions
+              with $S=0.5$)
+          \item Larger minority population size decreases covert 
+              signaling prevalence among the minority,
+            but weakly if at all---would want to integrate over $d$, $w$ values.
+            (Compare, e.g., K=9, S=0.5, and $\rho^{minor}=0.1,0.2$).
+          \item Increased overall diversity (increased $K$) increases prevalence of 
+            covert signaling among minority for low to moderate 
+            similarity thresholds (Figures: compare $K=3,9$ over 
+            $S=0.3, 0.5$---Four plots---TWO ALREADY THERE,
+            PUT S=0.3 IN SUPPLEMENT).
+        \end{itemize}
+  \item High levels of homophily and similarity threshold favor covert signaling.
+    (Figures: selection of two figures where $S=0.8$ SECOND FIGURE IN MAIN TEXT)
+\end{itemize}
+
+(ALL FIGURES BELOW WERE RUN PRELIMINARY WITH 20 TRIALS. I HAVE DATA FOR 100
+TRIALS BUT HAVE NOT YET ANALYZED IT)
+
+\begin{figure}
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+      \includegraphics[width=\textwidth]{Figures/minority_tolerance/3_0p10_0p5.pdf}
+      \caption{}
+    \end{subfigure}
+    \begin{subfigure}{0.49\textwidth}
+      \includegraphics[width=\textwidth]{Figures/minority_tolerance/9_0p10_0p5.pdf}
+      \caption{}
+    \end{subfigure} \\[1em]
+    \begin{subfigure}{0.49\textwidth}
+      \includegraphics[width=\textwidth]{Figures/minority_tolerance/3_0p20_0p5.pdf}
+      \caption{}
+      \end{subfigure}
+    \begin{subfigure}{0.49\textwidth}
+      \includegraphics[width=\textwidth]{Figures/minority_tolerance/9_0p20_0p5.pdf}
+      \caption{}
+    \end{subfigure}
+    \caption{When homophily is high, disliking costs are low, and
+      similarity threshold is moderate ($S=0.5$ in these heatmaps), covert 
+    signaling is more common among the majority than the minority. When 
+  disliking costs are high and homophily is not, covert signaling is more
+prevalent among the minority than the majority. Results shown from condition
+where $\rho^{minor}=0.1$. We observe the same pattern with $\rho^{minor}=0.2$
+(Figure~\ref{fig:suppBasicMinorityResult}). All parameters not specified are set
+to their default values (Table~\ref{tab:params}).}
+  \label{fig:}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+      \includegraphics[width=\textwidth]{Figures/minority_tolerance/3_0p10_0p8.pdf}
+      \caption{}
+    \end{subfigure}
+    \begin{subfigure}{0.49\textwidth}
+      \includegraphics[width=\textwidth]{Figures/minority_tolerance/9_0p10_0p8.pdf}
+      \caption{}
+    \end{subfigure}
+    \caption{A high similarity threshold ($S=0.8$ here) promotes covert
+    signaling differentially among the minority when homophily is also high.
+    Here $\rho^{minor}=0.1$, but the same pattern is also observed for 
+  $\rho^{minor}=0.2$ (NEED TO PUT IN A SUPPLEMENT FIGURE~\ref{fig:highSimilarityHomophily_supp}).}
+  \label{fig:highSimilarityHomophily}
+\end{figure}
+
+% \begin{figure}
+%   \centering
+%   \begin{subfigure}{0.49\textwidth}
+%       \includegraphics[width=\textwidth]{Figures/minority_tolerance/3_0p10_0p5.pdf}
+%       \caption{}
+%     \end{subfigure}
+%     \begin{subfigure}{0.49\textwidth}
+%       \includegraphics[width=\textwidth]{Figures/minority_tolerance/9_0p10_0p5.pdf}
+%       \caption{}
+%     \end{subfigure}
+%     \caption{When homophily is high, disliking costs are low, and
+%       similarity threshold is moderate ($S=0.5$ in these heatmaps), covert 
+%     signaling is more common among the majority than the minority. When 
+%   disliking costs are high and homophily is not, covert signaling is more
+% prevalent among the minority than the majority. Results shown from condition
+% where $\rho^{minor}=0.1$. We observe the same pattern with $\rho^{minor}=0.2$
+% (Figure~\ref{fig:suppBasicMinorityResult}). All parameters not specified are set
+% to their default values (Table~\ref{tab:params}).}
+%   \label{fig:}
+% \end{figure}
+
+% % \subsubsection{Covert minority signaling over minority prevalence}
+
+% % \begin{figure}[H]
+% %   \centering
+% %   \begin{subfigure}{0.48\textwidth}
+% %     \centering
+% %     \includegraphics[width=\textwidth]{Figures/covert_signalers_diff_0p05.pdf}
+% %     % \caption{Prevalence of minority covert receivers; $\rho^{minor} = 0.10$.}
+% %   \end{subfigure}
+% %   \hfill
+% %   \begin{subfigure}{0.48\textwidth}
+% %     \centering
+% %     \includegraphics[width=\textwidth]{Figures/covert_signalers_diff_0p10.pdf}
+% %     % \caption{Prevalence of minority covert receivers; $\rho^{minor} = 0.25$.}
+% %   \end{subfigure} \\[.25in]
+% %   \begin{subfigure}{0.48\textwidth}
+% %     \centering
+% %     \includegraphics[width=\textwidth]{Figures/covert_signalers_diff_0p25.pdf}
+% %     % \caption{Prevalence of minority churilsh receivers; $\rho^{minor} = 0.10$.}
+% %   \end{subfigure}
+% %   \hfill
+% %   \begin{subfigure}{0.48\textwidth}
+% %     \centering
+% %     \includegraphics[width=\textwidth]{Figures/covert_signalers_diff_0p10_K=10_M=4.pdf}
+% %     \caption{(NEED TO UPDATE WITH K=9 AND M=4. Ran these, just need to pull from
+% %     MERCED and analyze.)}
+% %   \end{subfigure}
+% %   \caption{Difference in covert signaling prevalence between minority and
+% %   majority populations for different parameters settings.}
+% %   \label{fig:covert-signaling-minority-heatmap}
+% % \end{figure}
+
+% \begin{figure}[H]
+%   \centering
+%   \begin{subfigure}{0.31\textwidth}
+%     \includegraphics[width=\textwidth]{Figures/minority-homophily=0p05.pdf}
+%     \caption{}
+%   \end{subfigure}
+%   \begin{subfigure}{0.31\textwidth}
+%     \includegraphics[width=\textwidth]{Figures/minority-homophily=0p25.pdf}
+%     \caption{}
+%   \end{subfigure}
+%   \begin{subfigure}{0.31\textwidth}
+%     \includegraphics[width=\textwidth]{Figures/minority-homophily=0p45.pdf}
+%     \caption{}
+%   \end{subfigure}
+%   \caption{}
+% \end{figure}
 
@@
 
+\subsection{Similarity threshold experiment---further details}
+
+\begin{figure}[H]
+    \centering
+  \label{fig:}
+  \centering
+  \begin{subfigure}{\textwidth}
+    \centering
+      \includegraphics[width=0.8\textwidth]{Figures/similarity_threshold_matrix_K=3.pdf}
+      \caption{}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+    \centering
+      \includegraphics[width=0.8\textwidth]{Figures/similarity_threshold_matrix_K=5.pdf}
+      \caption{}
+  \end{subfigure}
+  \caption{}
+\end{figure}
+\begin{figure}[H]
+  \ContinuedFloat
+    \centering
+  \begin{subfigure}{\textwidth}
+    \centering
+      \includegraphics[width=0.8\textwidth]{Figures/similarity_threshold_matrix_K=9.pdf}
+      \caption{}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+    \centering
+      \includegraphics[width=0.8\textwidth]{Figures/similarity_threshold_matrix_K=15.pdf}
+      \caption{}
+  \end{subfigure}
+  \caption{}
+\end{figure}
+\begin{figure}[H]
+    \ContinuedFloat
+    \centering
+  \begin{subfigure}{\textwidth}
+    \centering
+      \includegraphics[width=0.8\textwidth]{Figures/similarity_threshold_matrix_K=21.pdf}
+      \caption{}
+  \end{subfigure}
+  \label{fig:similarity_supp}
+  \caption{All results for experiments varying the similarity threshold, which
+      could be thougth of as the additive inverse of tolerance. There are a
+      number of subtle patterns described in detail in the main text and here
+      in the supplement. Notably\dots (RECAP BRIEFLY HERE AND HIGHLIGHT 
+      STUFF NOT INCLUDED IN MAIN).
+}
+\end{figure}
+
 \subsection{Receiving strategy prevalence dynamics}
@@
     final timestep recorded in this preliminary experiment. Receptivity of
-    overt signals is $R=0.5$.}
+    overt signals is $R=0.5$. (THIS IS USING OLD DATA---NEED TO UPDATE WITH
+    LATEST DATA USED TO GENERATE PLOTS ABOVE).}
   \label{fig:receptivityHomophilyHeatmap}
@@
 agents to adopt churlish receiving).
+
+(THESE ARE OLD RESULTS, NOT TAKEN FROM DATASETS USED TO MAKE CURRENT MAIN
+TEXT SIGNALING STRATEGY RESULTS. NEED TO UPDATE THESE.)
 

### 2020-06-29 id_signaling/figures.py

@@ -221,6 +221,7 @@ def heatmap(df, experiment='disliking', strategy='signaling',
     if savefig_path is not None:
         plt.savefig(savefig_path)
 
+
 def minority_diff_heatmap(df, strategy='signaling', savefig_path=None,
                           figsize=(6.35, 4.75), vmin=None, vmax=None,
                           title=None):
@@ -253,7 +254,7 @@ def minority_diff_heatmap(df, strategy='signaling', savefig_path=None,
     plt.figure(figsize=figsize)
     ax = sns.heatmap(
         diff.stack(), square=True, vmin=vmin, vmax=vmax,
-        cmap=sns.diverging_palette(10, 220, sep=80, n=10), #, center='dark'),
+        cmap=sns.diverging_palette(10, 220, sep=30, n=26), #, center='dark'),
         cbar_kws={
             'label':
                 f'Difference in {strategy_inset.lower()}\n'

### 2020-06-29 id_signaling/model.py

@@ -167,7 +167,6 @@ class Model:
         # It is repetetive but convenient to create the full symmetric matrix.
         self._init_similar_matrix()
 
-
     def _init_similar_matrix(self):
         for a1 in self.agents:
             for a2 in self.agents:
@@ -247,13 +246,7 @@ class Model:
             for receiver in receivers:
 
                 # Calculate similarity and set whether receiver likes
-                # signaling agent. "Liking" is determined by how many traits
-                # they have in common---if they have a majority of their traits
-                # in common they like the signaling agent. Neutral if K even
-                # and equal number of similar and dissimilar traits.
-                # XXX This can be calculated just once at init after
-                # traits have been set since traits don't change.
-                # similarity = np.sum(receiver.traits * signaler.traits)
+                # signaling agent.
                 similar = self._are_similar(signaler, receiver)
 
                 # If similarity is positive, attitude independent of signaling

### 2020-06-30 id_signaling/model.py
added option to pass alpha learning rate; going to run basic and invasion on cluster

@@ -24,7 +24,7 @@ class Model:
                  minority_trait_frac=None,
                  initial_prop_covert=0.5, initial_prop_churlish=0.5,
                  n_minmaj_traits=None,  # only used if minority_trait_frac ! None
-                 evo_logistic_loc=1.25, evo_logistic_scale=12):
+                 learning_alpha=1.25, learning_beta=12):
         '''
         Arguments:
             N (int): Number of agents, i.e. population
@@ -51,11 +51,11 @@ class Model:
             n_minmaj_traits (int): number of traits to use in assigning
                 minority and majority agents; short name is M in paper and
                 CLI.
-            evo_logistic_loc (float): location where logistic function = 0.5
+            learning_alpha (float): location where logistic function = 0.5
                 probability of switching strategies depending on relative
                 payoff. I.e. default is set so that 50% chance of switching
                 when the teacher has accumulated 1.25x more than the learner.
-            evo_logistic_scale (float): scale defining the sharpness of the
+            learning_beta (float): scale defining the sharpness of the
                 transition from 0 to 1 in the logistic function. Default chosen
                 so that probability of switching is ~1/50 when
                 relative payoff is 0.9 and ~3/50 when relative payoff is 1.0.
@@ -70,8 +70,8 @@ class Model:
         self.two_dislike_penalty = two_dislike_penalty
         self.homophily = homophily
         self.similarity_threshold = similarity_threshold
-        self.evo_logistic_loc = evo_logistic_loc
-        self.evo_logistic_scale = evo_logistic_scale
+        self.learning_alpha = learning_alpha
+        self.learning_beta = learning_beta
 
         if n_minmaj_traits is None:
             n_minmaj_traits = K - ((K+1) // 2)
@@ -343,11 +343,11 @@ class Model:
                 payoff_proportion = teacher.payoff / learner.payoff
             # ... if it is, set chance to switch to be 0.5.
             else:
-                payoff_proportion = self.evo_logistic_loc
+                payoff_proportion = self.learning_alpha
 
             switch_prob = _logistic(payoff_proportion,
-                                    loc=self.evo_logistic_loc,
-                                    scale=self.evo_logistic_scale)
+                                    loc=self.learning_alpha,
+                                    scale=self.learning_beta)
 
             if uniform() < switch_prob:
                 # Coin flip to switch either signaling or receiving strategy.

### 2020-06-30 id_signaling/scripts/runner.py

@@ -33,7 +33,8 @@ def basic_decorator():
             click.option('--initial_prop_churlish', type=float, default=0.5),
             click.option('--num_traits', '-K', type=int, default=3),
             click.option('--similarity_threshold', '-S', type=float,
-                         default=0.5)
+                         default=0.5),
+            click.option('--learning_alpha', type=float, default=1.25)
        )
 
 
@@ -42,7 +43,7 @@ def basic_decorator():
 def run(experiment, param_vals, homophily_vals, n_iter, n_trials,
         output_file, prob_overt_receiving, minority_trait_frac,
         initial_prop_covert, initial_prop_churlish, num_traits,
-        similarity_threshold):
+        similarity_threshold, learning_alpha):
 
     # XXX Hack to deal with subexp throwing error I don't understand that
     # minority_trait_frac can't be None (the default) because it's not a
@@ -61,7 +62,9 @@ def run(experiment, param_vals, homophily_vals, n_iter, n_trials,
                              minority_trait_frac=minority_trait_frac,
                              initial_prop_covert=initial_prop_covert,
                              initial_prop_churlish=initial_prop_churlish,
-                             K=num_traits, similarity_threshold=similarity_threshold,
+                             K=num_traits,
+                             similarity_threshold=similarity_threshold,
+                             learning_alpha=learning_alpha
                              )
 
     out_df.to_csv(output_file, index=False)
@@ -78,7 +81,7 @@ def sub(
             experiment, param_vals, homophily_vals, n_iter, n_trials,
             output_file, prob_overt_receiving, minority_trait_frac,
             initial_prop_covert, initial_prop_churlish, num_traits,
-            similarity_threshold,
+            similarity_threshold, learning_alpha,
             queue, ncpu, wall_time, dry_run, job_name  # SLURM OPTS
         ):
     """
@@ -107,7 +110,8 @@ runexp {experiment} {param_vals} {homophily_vals} {n_iter} {n_trials} \\
     {output_file} -R{prob_overt_receiving} -m{minority_trait_frac} \\
     -K{num_traits} -S{similarity_threshold} \\
     --initial_prop_covert={initial_prop_covert} \\
-    --initial_prop_churlish={initial_prop_churlish}
+    --initial_prop_churlish={initial_prop_churlish} \\
+    --learning_alpha={learning_alpha}
 
 
 printf "******************\\nFinished at `uptime`"

### 2020-06-30 sub_basic_experiments.sh
rename sub_invasion_experiments and set n_iter back to 500 in basic

@@ -1,21 +1,21 @@
 
 printf "\nSubmitting basic disliking experiment part 1\n"
 fname=output_data/basic/disliking/part-`uuidgen`
-subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 1000 50 $fname.csv -R0.5  \
+subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
     -qfast.q -j$fname -n24 -t"04:00:00"
 
 printf "\nSubmitting basic disliking experiment part 2\n"
 fname=output_data/basic/disliking/part-`uuidgen`
-subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 1000 50 $fname.csv -R0.5  \
+subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
     -qfast.q -j$fname -n24 -t"04:00:00"
 
 
 printf "\nSubmitting basic receptivity experiment part 1\n"
 fname=output_data/basic/receptivity/part-`uuidgen`
-subexp receptivity 0.0:0.51:0.05 0.0:0.51:0.05 1000 50 $fname.csv -R0.5  \
+subexp receptivity 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
     -qfast.q -j$fname -n24 -t"04:00:00"
 
 printf "\nSubmitting basic receptivity experiment part 2\n"
 fname=output_data/basic/receptivity/part-`uuidgen`
-subexp receptivity 0.0:0.51:0.05 0.0:0.51:0.05 1000 50 $fname.csv -R0.5  \
+subexp receptivity 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
     -qfast.q -j$fname -n24 -t"04:00:00"

### 2020-06-30 sub_invasion_experiments.sh

@@ -1,67 +1,70 @@
 # An executable bit of documentation of how to run all the experiments used
 # for the computational modeling publication.
 
+# NOTE -- 6/29/20: Running with learning_alpha=1.0; comment out to
+# change back to default 1.25.
+
 printf "\nRunning .95, .95\n"
 fname=output_data/invasion/disliking/part-`uuidgen`
 subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
     --initial_prop_covert=0.95 --initial_prop_churlish=0.95 \
-    -qfast.q -j$fname -n24 -t"02:00:00"
+    -qfast.q -j$fname -n24 -t"04:00:00" --learning_alpha=1.0
 
 
 printf "\nRunning .5, .95\n"
 fname=output_data/invasion/disliking/part-`uuidgen`
 subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
     --initial_prop_covert=0.5 --initial_prop_churlish=0.95 \
-    -qfast.q -j$fname -n24 -t"02:00:00"
+    -qfast.q -j$fname -n24 -t"04:00:00" --learning_alpha=1.0
 
 
 printf "\nRunning .05, .95\n"
 fname=output_data/invasion/disliking/part-`uuidgen`
 subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
     --initial_prop_covert=0.05 --initial_prop_churlish=0.95 \
-    -qfast.q -j$fname -n24 -t"02:00:00"
+    -qfast.q -j$fname -n24 -t"04:00:00" --learning_alpha=1.0
 
 
 printf "\nRunning .95, .5\n"
 fname=output_data/invasion/disliking/part-`uuidgen`
 subexp disliking 0.0:0.51:0.1 0.0:0.51:0.1 500 50 $fname.csv -R0.5  \
     --initial_prop_covert=0.95 --initial_prop_churlish=0.5 \
-    -qfast.q -j$fname -n24 -t"02:00:00"
+    -qfast.q -j$fname -n24 -t"04:00:00" --learning_alpha=1.0
 
 
 printf "\nRunning .5, .5\n"
 fname=output_data/invasion/disliking/part-`uuidgen`
[…]

### 2020-06-30 id_signaling/scripts/runner.py
added option to set N

@@ -34,7 +34,8 @@ def basic_decorator():
             click.option('--num_traits', '-K', type=int, default=3),
             click.option('--similarity_threshold', '-S', type=float,
                          default=0.5),
-            click.option('--learning_alpha', type=float, default=1.25)
+            click.option('--learning_alpha', type=float, default=1.25),
+            click.option('--n_agents', '-N', type=int, default=100)
        )
 
 
@@ -43,7 +44,7 @@ def basic_decorator():
 def run(experiment, param_vals, homophily_vals, n_iter, n_trials,
         output_file, prob_overt_receiving, minority_trait_frac,
         initial_prop_covert, initial_prop_churlish, num_traits,
-        similarity_threshold, learning_alpha):
+        similarity_threshold, learning_alpha, n_agents):
 
     # XXX Hack to deal with subexp throwing error I don't understand that
     # minority_trait_frac can't be None (the default) because it's not a
@@ -64,7 +65,8 @@ def run(experiment, param_vals, homophily_vals, n_iter, n_trials,
                              initial_prop_churlish=initial_prop_churlish,
                              K=num_traits,
                              similarity_threshold=similarity_threshold,
-                             learning_alpha=learning_alpha
+                             learning_alpha=learning_alpha,
+                             N=n_agents
                              )
 
     out_df.to_csv(output_file, index=False)
@@ -81,7 +83,7 @@ def sub(
             experiment, param_vals, homophily_vals, n_iter, n_trials,
             output_file, prob_overt_receiving, minority_trait_frac,
             initial_prop_covert, initial_prop_churlish, num_traits,
-            similarity_threshold, learning_alpha,
+            similarity_threshold, learning_alpha, n_agents,
             queue, ncpu, wall_time, dry_run, job_name  # SLURM OPTS
         ):
     """
@@ -108,7 +110,7 @@ printf "******************\\nStarting {job_name} at `uptime`\\n"
 
 runexp {experiment} {param_vals} {homophily_vals} {n_iter} {n_trials} \\
     {output_file} -R{prob_overt_receiving} -m{minority_trait_frac} \\
-    -K{num_traits} -S{similarity_threshold} \\
+    -K{num_traits} -S{similarity_threshold} -N{n_agents} \\
     --initial_prop_covert={initial_prop_covert} \\
     --initial_prop_churlish={initial_prop_churlish} \\
     --learning_alpha={learning_alpha}

### 2020-06-30 sub_basic_experiments.sh
running minority and basic with N=200

@@ -1,21 +1,21 @@
 
 printf "\nSubmitting basic disliking experiment part 1\n"
-fname=output_data/basic/disliking/part-`uuidgen`
-subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
-    -qfast.q -j$fname -n24 -t"04:00:00"
+fname=output_data/"basic_alpha=1"/disliking/part-`uuidgen`
+subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 20 $fname.csv -R0.5  \
+    -qfast.q -j$fname -n24 -t"04:00:00" --learning_alpha=1.0
 
 printf "\nSubmitting basic disliking experiment part 2\n"
-fname=output_data/basic/disliking/part-`uuidgen`
-subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
-    -qfast.q -j$fname -n24 -t"04:00:00"
+fname=output_data/"basic_alpha=1"/disliking/part-`uuidgen`
+subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 20 $fname.csv -R0.5  \
+    -qfast.q -j$fname -n24 -t"04:00:00" --learning_alpha=1.0
 
 
 printf "\nSubmitting basic receptivity experiment part 1\n"
-fname=output_data/basic/receptivity/part-`uuidgen`
-subexp receptivity 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
-    -qfast.q -j$fname -n24 -t"04:00:00"
+fname=output_data/"basic_alpha=1"/receptivity/part-`uuidgen`
+subexp receptivity 0.0:0.51:0.05 0.0:0.51:0.05 500 20 $fname.csv -R0.5  \
+    -qfast.q -j$fname -n24 -t"04:00:00" --learning_alpha=1.0
 
 printf "\nSubmitting basic receptivity experiment part 2\n"
-fname=output_data/basic/receptivity/part-`uuidgen`
-subexp receptivity 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
-    -qfast.q -j$fname -n24 -t"04:00:00"
+fname=output_data/"basic_alpha=1"/receptivity/part-`uuidgen`
[…]

### 2020-06-30 sub_minority_experiments.sh

@@ -29,15 +29,15 @@ K=3
 for similarity_threshold in 0.3 0.5 0.8; do 
     for minority_trait_frac in 0.10 0.20; do 
 
-        fname=output_data/minority/$minority_trait_frac/part-`uuidgen`
-        subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+        fname=output_data/"minority_N=200"/$minority_trait_frac/part-`uuidgen`
+        subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 20 $fname.csv -R0.5  \
             -qfast.q -j$fname -n24 -t"04:00:00" -m$minority_trait_frac \
-            -K$K -S$similarity_threshold 
+            -K$K -S$similarity_threshold -N200
 
-        fname=output_data/minority/$minority_trait_frac/part-`uuidgen`
-        subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+        fname=output_data/"minority_N=200"/$minority_trait_frac/part-`uuidgen`
+        subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 20 $fname.csv -R0.5  \
             -qfast.q -j$fname -n24 -t"04:00:00" -m$minority_trait_frac \
-            -K$K -S$similarity_threshold 
+            -K$K -S$similarity_threshold -N200
     done
 done
 
@@ -46,15 +46,15 @@ K=9
 for similarity_threshold in 0.3 0.5 0.8; do 
     for minority_trait_frac in 0.10 0.20; do 
 
-        fname=output_data/minority/$minority_trait_frac/part-`uuidgen`
-        subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 50 $fname.csv -R0.5  \
+        fname=output_data/"minority_N=200"/$minority_trait_frac/part-`uuidgen`
+        subexp disliking 0.0:0.51:0.05 0.0:0.51:0.05 500 20 $fname.csv -R0.5  \
             -qfast.q -j$fname -n24 -t"04:00:00" -m$minority_trait_frac \
-            -K$K -S$similarity_threshold 
+            -K$K -S$similarity_threshold -N200
 
-        fname=output_data/minority/$minority_trait_frac/part-`uuidgen`
[…]
